### 2015-09-02 HarryPlotter/doc/harry_plotter.tex
new Artus/HarryPlotter illustrations

\begin{tikzpicture}[scale=1.0]
\node at (0cm,0cm) [draw, rectangle, minimum width=3.5cm, minimum height=5ex, node distance=5ex+0.3cm] (module1) {Input Module 1};
\node [rectangle, fill=white, minimum width=3.5cm, minimum height=5ex, node distance=5ex+0.3cm, below of=module1] (module2) {$\cdots$};
\node [draw, rectangle, fill=white, minimum width=3.5cm, minimum height=5ex, node distance=5ex+0.3cm, below of=module2] (module3) {Analysis Module 1};
\node [draw, rectangle, fill=white, minimum width=3.5cm, minimum height=5ex, node distance=5ex+0.3cm, below of=module3] (module4) {Analysis Module 2};
\node [draw, rectangle, fill=white, minimum width=3.5cm, minimum height=5ex, node distance=5ex+0.3cm, below of=module4] (module5) {Analysis Module 3};
\node [rectangle, fill=white, minimum width=3.5cm, minimum height=5ex, node distance=5ex+0.3cm, below of=module5] (module6) {$\cdots$};
\node [draw, rectangle, fill=white, minimum width=3.5cm, minimum height=5ex, node distance=5ex+0.3cm, below of=module6] (module7) {Plot Module 1};
\node [rectangle, fill=white, minimum width=3.5cm, minimum height=5ex, node distance=5ex+0.3cm, below of=module7] (module8) {$\cdots$};

\node [draw, rectangle, rounded corners, KIT_rot_1, fill=KIT_rot_5, minimum width=3.5cm, minimum height=7ex, node distance=7ex+0.5cm, above of=module1] (input) {Input};
\node [draw, rectangle, rounded corners, KIT_blau_1, fill=KIT_blau_5, minimum width=3.5cm, minimum height=7ex, node distance=7ex+0.5cm, below of=module8] (plot) {Plot};

\draw [->, thick] (input) -- (module1);
\draw [->, thick] (module1) -- (module2);
\draw [->, thick] (module2) -- (module3);
\draw [->, thick] (module3) -- (module4);
\draw [->, thick] (module4) -- (module5);
\draw [->, thick] (module5) -- (module6);
\draw [->, thick] (module6) -- (module7);
\draw [->, thick] (module7) -- (module8);
\draw [->, thick] (module8) -- (plot);

\draw [fill=white] ($ (module1) + (-1.75cm-0.5cm-5ex-0.5cm-5ex-1.5cm,2.5ex) $) rectangle node{\rotatebox{90}{Argument Parser}} ($ (module8) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm,-2.5ex) $);

\draw [->, thick] ($ (module1) + (-1.75cm,1ex) $) -- ($ (module1) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm,1ex) $);
\draw [->, thick] ($ (module3) + (-1.75cm,1ex) $) -- ($ (module3) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm,1ex) $);
\draw [->, thick] ($ (module4) + (-1.75cm,1ex) $) -- ($ (module4) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm,1ex) $);
\draw [->, thick] ($ (module5) + (-1.75cm,1ex) $) -- ($ (module5) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm,1ex) $);
\draw [->, thick] ($ (module7) + (-1.75cm,1ex) $) -- ($ (module7) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm,1ex) $);

\draw [<-, thick, KIT_gruen_1] ($ (module1) + (-1.75cm,-1ex) $) -- ($ (module1) + (-1.75cm-0.5cm,-1ex) $);
\draw [<-, thick, KIT_gruen_1] ($ (module3) + (-1.75cm,-1ex) $) -- ($ (module3) + (-1.75cm-0.5cm,-1ex) $);
\draw [<-, thick, KIT_gruen_1] ($ (module4) + (-1.75cm,-1ex) $) -- ($ (module4) + (-1.75cm-0.5cm,-1ex) $);
\draw [<-, thick, KIT_gruen_1] ($ (module5) + (-1.75cm,-1ex) $) -- ($ (module5) + (-1.75cm-0.5cm,-1ex) $);
\draw [<-, thick, KIT_gruen_1] ($ (module7) + (-1.75cm,-1ex) $) -- ($ (module7) + (-1.75cm-0.5cm,-1ex) $);

\node at ($ (module1) + (-1.75cm-0.5cm-5ex-0.5cm-0.5cm,1ex-1.75ex) $) {\textit{define}};
\node at ($ (module1) + (-1.75cm-0.5cm-5ex-0.5cm-0.5cm,1ex-1.75ex-2.25ex) $) {\textit{arguments}};

\draw [rounded corners, KIT_gruen_1, fill=white] ($ (module1) + (-1.75cm-0.5cm-5ex,2.5ex) $) rectangle node{\rotatebox{90}{Settings}} ($ (module8) + (-1.75cm-0.5cm,-2.5ex) $);

\draw [<-, thick, KIT_gruen_1] ($ (module1) + (-1.75cm-0.5cm-2.5ex,2.5ex) $) -- ($ (module1) + (-1.75cm-0.5cm-2.5ex,2.5ex+0.3cm) $) -- ($ (module1) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm-2.5ex,2.5ex+0.3cm) $) -- ($ (module1) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm-2.5ex,2.5ex) $);
\draw [<-, thick, KIT_gruen_1] ($ (module8) + (-1.75cm-0.5cm-2.5ex,-2.5ex) $) -- ($ (module8) + (-1.75cm-0.5cm-2.5ex,-2.5ex-0.3cm) $) -- ($ (module8) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm-2.5ex,-2.5ex-0.3cm) $) -- ($ (module8) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm-2.5ex,-2.5ex) $);

\node [KIT_gruen_1] at ($ (module1) + (-1.75cm-0.5cm-5ex-0.5cm-0.5cm,2.5ex+0.3cm+1.5ex) $) {\textit{1${}^\text{st}$ parsing}};
\node [KIT_gruen_1] at ($ (module8) + (-1.75cm-0.5cm-5ex-0.5cm-0.5cm,-2.5ex-0.3cm-1.5ex) $) {\textit{2${}^\text{nd}$ parsing}};

\draw [rounded corners, KIT_gruen_1, fill=KIT_gruen_5] ($ (module1) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm-5ex-0.5cm-5ex,2.5ex) $) rectangle node{\rotatebox{90}{Program Arguments, JSON Configuration}} ($ (module8) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm-5ex-0.5cm,-2.5ex) $);

\draw [->, thick, KIT_gruen_1] ($ (module4) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm-5ex-0.5cm,-2.5ex-0.15cm) $) -- ($ (module4) + (-1.75cm-0.5cm-5ex-0.5cm-1.5cm-5ex,-2.5ex-0.15cm) $);

\draw [rounded corners, KIT_rot_1, fill=white] ($ (module1) + (1.75cm+0.5cm+5ex,2.5ex) $) rectangle node{\rotatebox{90}{Plot Data}} ($ (module8) + (1.75cm+0.5cm,-2.5ex) $);

\draw [<->, thick, KIT_rot_1] (module1) -- ($ (module1) + (1.75cm+0.5cm,0cm) $);
\draw [<->, thick, KIT_rot_1] (module3) -- ($ (module3) + (1.75cm+0.5cm,0cm) $);
\draw [<->, thick, KIT_rot_1] (module4) -- ($ (module4) + (1.75cm+0.5cm,0cm) $);
\draw [<->, thick, KIT_rot_1] (module5) -- ($ (module5) + (1.75cm+0.5cm,0cm) $);
\draw [<->, thick, KIT_rot_1] (module7) -- ($ (module7) + (1.75cm+0.5cm,0cm) $);
\end{tikzpicture}

### 2015-09-02 KappaAnalysis/interface/Consumers/KappaLambdaNtupleConsumer.h
Tolerate cut as filter identifier.

@@ -89,7 +89,7 @@ public:
 					return SafeMap::GetWithDefault(product.m_weights, quantity, SafeMap::GetWithDefault(product.m_optionalWeights, quantity, 1.0));
 				} );
 			}
-			if (boost::algorithm::icontains(quantity, "filter") &&
+			if ((boost::algorithm::icontains(quantity, "filter") || boost::algorithm::icontains(quantity, "cut")) &&
 			   (LambdaNtupleConsumer<TTypes>::GetFloatQuantities().count(quantity) == 0))
 			{
 				LOG(DEBUG) << "\tQuantity \"" << quantity << "\" is tried to be taken from prduct.fres (FilterResult).";

### 2015-09-03 Configuration/scripts/artusMergeOutputs.py
python scripts: improved ROOT imports

@@ -10,13 +10,14 @@ import glob
 import os
 
 import ROOT
+ROOT.gROOT.SetBatch(True)
 ROOT.PyConfig.IgnoreCommandLineOptions = True
+ROOT.gErrorIgnoreLevel = ROOT.kError
 
 import Artus.Utility.progressiterator as pi
 
 
 def main():
-	ROOT.gROOT.SetBatch(True)
 	
 	parser = argparse.ArgumentParser(description="Merge Artus outputs per nick name.", parents=[logger.loggingParser])
 

### 2015-09-03 KappaAnalysis/scripts/availableKappaElectronMvaIds.py

@@ -9,12 +9,13 @@ import argparse
 import os
 
 import ROOT
+ROOT.gROOT.SetBatch(True)
 ROOT.PyConfig.IgnoreCommandLineOptions = True
 ROOT.gErrorIgnoreLevel = ROOT.kError
 
 
 def main():
-	ROOT.gROOT.SetBatch(True)
+	
 	ROOT.gSystem.Load(os.path.expandvars("$CMSSW_BASE/src/Kappa/lib/libKappa"))
 	
 	parser = argparse.ArgumentParser(description="Print out the available electron MVA IDs in a kappa skim.", parents=[logger.loggingParser])

### 2015-09-03 Utility/python/jsonTools.py

@@ -13,7 +13,9 @@ import pprint
 import sys
 
 import ROOT
+ROOT.gROOT.SetBatch(True)
 ROOT.PyConfig.IgnoreCommandLineOptions = True
+ROOT.gErrorIgnoreLevel = ROOT.kError
 
 import Artus.Utility.tools as tools
 

### 2015-09-03 Utility/scripts/compareRootFiles.py

@@ -8,6 +8,10 @@ log = logging.getLogger(__name__)
 import argparse
 
 import ROOT
+ROOT.gROOT.SetBatch(True)
+ROOT.PyConfig.IgnoreCommandLineOptions = True
+ROOT.gErrorIgnoreLevel = ROOT.kError
+
 import sys
 
 opt_all = False

### 2015-09-03 Utility/scripts/eventmatching.py

@@ -2,10 +2,14 @@
 # -*- coding: utf-8 -*-
 
 import sys
-import ROOT
 import time
 import os
 import argparse
+
+import ROOT
+ROOT.gROOT.SetBatch(True)
+ROOT.PyConfig.IgnoreCommandLineOptions = True
+ROOT.gErrorIgnoreLevel = ROOT.kError
 
 
 def main():

### 2015-09-03 Configuration/scripts/artusRepositoryDiff.py
artusRepositoryDiff.py: some improvements (e.g. print github link)

@@ -8,6 +8,7 @@ log = logging.getLogger(__name__)
 import argparse
 import os
 import shlex
+import subprocess
 
 import Artus.Utility.jsonTools as jsonTools
 import Artus.Utility.tools as tools
@@ -29,10 +30,18 @@ def main():
 	
 	repo_version1 = config1[repo_key1]
 	repo_version2 = config2[repo_key2]
+	diff_string = "%s...%s" % (repo_version1, repo_version2)
 	
 	command = "git diff %s..%s" % (repo_version1, repo_version2)
-	log.info(command)
-	logger.subprocessCall(shlex.split(command))
+	if log.isEnabledFor(logging.DEBUG):
+		log.info("")
+		logger.subprocessCall(shlex.split(command))
+	log.info("\n"+command)
+	
+	popen_cout, popen_cerr = subprocess.Popen("git config remote.origin.url".split(), stdout=subprocess.PIPE).communicate()
+	remote_url = popen_cout.replace("\n", "")
+	github_link = os.path.join(remote_url, "compare", diff_string)
+	log.info(github_link)
 	
 
 if __name__ == "__main__":

### 2015-09-03 Utility/python/tools.py
harry.py: move multiprocessing to tools.py

@@ -8,6 +8,7 @@ log = logging.getLogger(__name__)
 import array
 import copy
 import fcntl
+import multiprocessing
 import os
 import re
 import sys
@@ -142,4 +143,10 @@ def get_indented_text(prefix, message, width=None):
 				replace_whitespace=False
 			)
 	return '\n'.join(['\n'.join(tmp_wrapped_texts)])
+
+def parallelize(function, arguments_list, n_processes=1):
+	pool = multiprocessing.Pool(processes=n_processes)
+	results = pool.map_async(function, arguments_list)
+	# 9999999 is needed for KeyboardInterrupt to work: http://stackoverflow.com/questions/1408356/keyboard-interrupts-with-pythons-multiprocessing-pool
+	return results.get(9999999)
 

### 2015-09-03 artus_pipeline.tex
standalone version of pictures

\documentclass[tikz,border=10pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{shapes,calc,arrows,through,intersections}
\usepackage{calc}

\begin{tikzpicture}[scale=1.0]
\node at (0cm,0cm) [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=2.5cm+0.2cm] (processor1) {\rotatebox{90}{Producer A}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor1] (processor2) {\rotatebox{90}{Filter B}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor2] (processor3) {\rotatebox{90}{Producer C}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor3] (processor4) {\rotatebox{90}{Filter D}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor4] (processor5) {\rotatebox{90}{Filter E}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor5] (processor6) {\rotatebox{90}{Producer F}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor6] (processor7) {\rotatebox{90}{Producer G}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor7] (processor8) {\rotatebox{90}{Producer H}};
\node [rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor8] (processor9) {\textbf{$\cdots$}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor9] (processor10) {\rotatebox{90}{Consumer 1}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor10] (processor11) {\rotatebox{90}{Consumer 2}};
\node [draw, rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor11] (processor12) {\rotatebox{90}{Consumer 3}};
\node [rectangle, minimum height=2.5cm, minimum width=5ex, node distance=5ex+0.3cm, right of=processor12] (processor13) {\textbf{$\cdots$}};

\draw[->, thick] (processor1) -- (processor2);
\draw[->, thick] (processor2) -- (processor3);
\draw[->, thick] (processor3) -- (processor4);
\draw[->, thick] (processor4) -- (processor5);
\draw[->, thick] (processor5) -- (processor6);
\draw[->, thick] (processor6) -- (processor7);
\draw[->, thick] (processor7) -- (processor8);
\draw[->, thick] (processor8) -- (processor9);
\draw[->, thick] (processor9) -- (processor10);
\draw[->, thick] (processor10) -- (processor11);
\draw[->, thick] (processor11) -- (processor12);
\draw[->, thick] (processor12) -- (processor13);

\node [draw, rectangle, rounded corners, minimum width=3.5cm, minimum height=5ex, node distance=1.25cm+2.5ex+1cm, above of=processor5, KIT_gruen_1] (settings) {Settings};
\node [draw, rectangle, rounded corners, minimum width=3.5cm, minimum height=5ex, node distance=1.25cm+2.5ex+1cm+5ex+0.2cm, above of=processor9, KIT_rot_1] (event) {Event};
\node [draw, rectangle, rounded corners, minimum width=3.5cm, minimum height=5ex, node distance=1.25cm+2.5ex+1cm, below of=processor5, KIT_rot_1] (product) {Product};
\node [draw, rectangle, rounded corners, minimum width=3.5cm, minimum height=5ex, node distance=1.25cm+2.5ex+1cm+5ex-0.05cm, below of=processor11, KIT_blau_1] (output) {Output};

\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor1) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor1) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor2) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor2) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor3) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor3) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor4) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor4) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor5) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor5) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor6) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor6) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor7) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor7) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor8) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor8) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor10) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor10) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor11) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor11) + (-1ex,1.25cm) $);
\draw[->, thick, KIT_gruen_1] (settings) -- ($ (settings) + (0cm,-2.5ex-0.4cm) $) -- ($ (processor12) + (-1ex,1.25cm+0.6cm) $) -- ($ (processor12) + (-1ex,1.25cm) $);

\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor1) + (1ex,1.25cm+0.4cm) $) -- ($ (processor1) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor2) + (1ex,1.25cm+0.4cm) $) -- ($ (processor2) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor3) + (1ex,1.25cm+0.4cm) $) -- ($ (processor3) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor4) + (1ex,1.25cm+0.4cm) $) -- ($ (processor4) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor5) + (1ex,1.25cm+0.4cm) $) -- ($ (processor5) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor6) + (1ex,1.25cm+0.4cm) $) -- ($ (processor6) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor7) + (1ex,1.25cm+0.4cm) $) -- ($ (processor7) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor8) + (1ex,1.25cm+0.4cm) $) -- ($ (processor8) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor10) + (1ex,1.25cm+0.4cm) $) -- ($ (processor10) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor11) + (1ex,1.25cm+0.4cm) $) -- ($ (processor11) + (1ex,1.25cm) $);
\draw[->, thick, KIT_rot_1] (event) -- ($ (event) + (0cm,-5ex-0.2cm-2.5ex-0.6cm) $) -- ($ (processor12) + (1ex,1.25cm+0.4cm) $) -- ($ (processor12) + (1ex,1.25cm) $);

\draw[<->, very thick, dashed, KIT_rot_1] ($ (product) + (-1.3cm,2.5ex) $) -- ($ (product) + (-1.3cm,2.5ex+0.4cm) $) -- ($ (processor1) + (0cm,-1.25cm-0.6cm) $) -- (processor1);
\draw[<->, very thick, dashed, KIT_rot_1] ($ (product) + (-1.3cm,2.5ex) $) -- ($ (product) + (-1.3cm,2.5ex+0.4cm) $) -- ($ (processor3) + (0cm,-1.25cm-0.6cm) $) -- (processor3);
\draw[<->, very thick, dashed, KIT_rot_1] ($ (product) + (-1.3cm,2.5ex) $) -- ($ (product) + (-1.3cm,2.5ex+0.4cm) $) -- ($ (processor6) + (0cm,-1.25cm-0.6cm) $) -- (processor6);
\draw[<->, very thick, dashed, KIT_rot_1] ($ (product) + (-1.3cm,2.5ex) $) -- ($ (product) + (-1.3cm,2.5ex+0.4cm) $) -- ($ (processor7) + (0cm,-1.25cm-0.6cm) $) -- (processor7);
\draw[<->, very thick, dashed, KIT_rot_1] ($ (product) + (-1.3cm,2.5ex) $) -- ($ (product) + (-1.3cm,2.5ex+0.4cm) $) -- ($ (processor8) + (0cm,-1.25cm-0.6cm) $) -- (processor8);

\draw[->, thick, KIT_rot_1] ($ (product) + (1.3cm,2.5ex) $) -- ($ (product) + (1.3cm,2.5ex+0.6cm) $) -- ($ (processor2) + (0cm,-1.25cm-0.4cm) $) -- (processor2);
\draw[->, thick, KIT_rot_1] ($ (product) + (1.3cm,2.5ex) $) -- ($ (product) + (1.3cm,2.5ex+0.6cm) $) -- ($ (processor4) + (0cm,-1.25cm-0.4cm) $) -- (processor4);
\draw[->, thick, KIT_rot_1] ($ (product) + (1.3cm,2.5ex) $) -- ($ (product) + (1.3cm,2.5ex+0.6cm) $) -- ($ (processor5) + (0cm,-1.25cm-0.4cm) $) -- (processor5);
\draw[->, thick, KIT_rot_1] ($ (product) + (1.3cm,2.5ex) $) -- ($ (product) + (1.3cm,2.5ex+0.6cm) $) -- ($ (processor10) + (-1ex,-1.25cm-0.4cm) $) -- ($ (processor10) + (-1ex,-1.25cm) $);
\draw[->, thick, KIT_rot_1] ($ (product) + (1.3cm,2.5ex) $) -- ($ (product) + (1.3cm,2.5ex+0.6cm) $) -- ($ (processor11) + (-1ex,-1.25cm-0.4cm) $) -- ($ (processor11) + (-1ex,-1.25cm) $);
\draw[->, thick, KIT_rot_1] ($ (product) + (1.3cm,2.5ex) $) -- ($ (product) + (1.3cm,2.5ex+0.6cm) $) -- ($ (processor12) + (-1ex,-1.25cm-0.4cm) $) -- ($ (processor12) + (-1ex,-1.25cm) $);

\draw[<-, thick, KIT_blau_1] ($ (output) + (1ex,2.5ex) $) -- ($ (output) + (1ex,2.5ex+0.4cm+5ex-0.05cm) $) -- ($ (processor10) + (1ex,-1.25cm-0.6cm) $) -- ($ (processor10) + (1ex,-1.25cm) $);
\draw[<-, thick, KIT_blau_1] ($ (output) + (1ex,2.5ex) $) -- ($ (output) + (1ex,2.5ex+0.4cm+5ex-0.05cm) $) -- ($ (processor11) + (1ex,-1.25cm-0.6cm) $) -- ($ (processor11) + (1ex,-1.25cm) $);
\draw[<-, thick, KIT_blau_1] ($ (output) + (1ex,2.5ex) $) -- ($ (output) + (1ex,2.5ex+0.4cm+5ex-0.05cm) $) -- ($ (processor12) + (1ex,-1.25cm-0.6cm) $) -- ($ (processor12) + (1ex,-1.25cm) $);

\draw[dashed, thin] ($ (processor1) + (-2.5ex-0.2cm,1.25cm+1cm+5ex+0.1cm) $) rectangle ($ (processor13) + (2.5ex+0.2cm,-1.25cm-1cm-5ex-0.1cm) $);
\node at ($ (processor1) + (-2.5ex-0.2cm+2em,1.25cm+1cm+5ex+0.1cm+1.5ex) $) {\textit{Pipeline}};
\end{tikzpicture}

\end{document}

### 2015-09-03 artus_structure.tex
standalone version of pictures

\documentclass[tikz,border=10pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{shapes,calc,arrows,through,intersections}
\usepackage{calc}

\begin{document}

\begin{tikzpicture}[scale=1.0]
%\draw[step=1cm, very thin, red] (-8cm,-10cm) grid (5cm,3cm);

\node[draw, rectangle, rounded corners, minimum width=0.8cm, minimum height=5.3cm, KIT_rot_1] (event) at (0cm-2.5cm-0.5cm,0cm-1cm-2cm+0.75cm) {\rotatebox{90}{Event}};
\node[draw, rectangle, minimum width=0.8cm, minimum height=5.3cm] (eventprovider) at (0cm-2.5cm-0.5cm-1.5cm,0cm-1cm-2cm+0.75cm) {\rotatebox{90}{Event Provider}};
\node[draw, rectangle, rounded corners, minimum width=0.8cm, minimum height=5.3cm, KIT_rot_1, fill=KIT_rot_5] (input) at (0cm-2.5cm-0.5cm-1.5cm-1.5cm,0cm-1cm-2cm+0.75cm) {\rotatebox{90}{Input}};

\node[draw, rectangle, minimum width=3.8cm, minimum height=0.8cm] (globalpipeline) at (0cm,0cm) {Global Pipeline};

\draw[->, thick] ($ (input) + (0.4cm,2.2cm) $) -- ($ (eventprovider) + (-0.4cm,2.2cm) $);
\draw[->, thick] ($ (eventprovider) + (0.4cm,2.2cm) $) -- ($ (event) + (-0.4cm,2.2cm) $);
\draw[->, thick] ($ (event) + (0.4cm,2.2cm) $) -- (globalpipeline);

\draw[->, thick, KIT_rot_1] ($ (event) + (0.4cm,2.4cm) $) -- ($ (event) + (0.4cm+0.9cm,2.4cm) $);
\draw[->, thick, KIT_rot_1] ($ (event) + (0.4cm,0.5cm) $) -- ($ (event) + (0.4cm+0.9cm,0.5cm) $);
\draw[->, thick, KIT_rot_1] ($ (event) + (0.4cm,0.4cm) $) -- ($ (event) + (0.4cm+1.9cm,0.4cm) $);
\draw[->, thick, KIT_rot_1] ($ (event) + (0.4cm,0.3cm) $) -- ($ (event) + (0.4cm+2.9cm,0.3cm) $);

\node[draw, rectangle, minimum width=0.8cm, minimum height=3.3cm] (localpipeline1) at (0cm-1.5cm,0cm-1cm-2cm-0.25cm) {\rotatebox{90}{Local Pipeline 1}};
\node[draw, rectangle, minimum width=0.8cm, minimum height=3.3cm] (localpipeline2) at (0cm-0.5cm,0cm-1cm-2cm-0.25cm) {\rotatebox{90}{Local Pipeline 2}};
\node[draw, rectangle, minimum width=0.8cm, minimum height=3.3cm] (localpipeline3) at (0cm+0.5cm,0cm-1cm-2cm-0.25cm) {\rotatebox{90}{Local Pipeline 3}};
\node[rectangle, minimum width=0.8cm, minimum height=3.3cm] (localpipeline4) at (0cm+1.5cm,0cm-1cm-2cm-0.25cm) {\textbf{$\cdots$}};
\node[KIT_rot_1] at ($ (globalpipeline) + (-0.5cm+0.5cm,0cm-1cm-0.2cm+1.5ex) $) {\textit{duplicate product}};

\draw[->, thick] (globalpipeline) -- ($ (globalpipeline) + (2cm+0.2cm,0cm) $) -- ($ (globalpipeline) + (2cm+0.2cm,0cm-1cm-0.2cm) $) -- ($ (globalpipeline) + (-2cm+0.5cm,0cm-1cm-0.2cm) $) -- (localpipeline1);
\draw[->, thick] (globalpipeline) -- ($ (globalpipeline) + (2cm+0.2cm,0cm) $) -- ($ (globalpipeline) + (2cm+0.2cm,0cm-1cm-0.2cm) $) -- ($ (globalpipeline) + (-2cm+1.5cm,0cm-1cm-0.2cm) $) -- (localpipeline2);
\draw[->, thick] (globalpipeline) -- ($ (globalpipeline) + (2cm+0.2cm,0cm) $) -- ($ (globalpipeline) + (2cm+0.2cm,0cm-1cm-0.2cm) $) -- ($ (globalpipeline) + (-2cm+2.5cm,0cm-1cm-0.2cm) $) -- (localpipeline3);

\node[draw, rectangle, rounded corners, minimum width=3.8cm, minimum height=0.8cm, KIT_blau_1, fill=KIT_blau_5] (output) at (0cm,0cm-1cm-2cm-2cm-1cm) {Output};
\draw[dotted, thick, KIT_blau_1] ($ (output) + (-1cm,0.4cm) $) -- ($ (output) + (-1cm,-0.4cm) $);
\draw[dotted, thick, KIT_blau_1] ($ (output) + (0cm,0.4cm) $) -- ($ (output) + (0cm,-0.4cm) $);
\draw[dotted, thick, KIT_blau_1] ($ (output) + (1cm,0.4cm) $) -- ($ (output) + (1cm,-0.4cm) $);

\draw[->, thick] ($ (localpipeline1) + (0cm,-1.65cm) $) -- ($ (localpipeline1) + (0cm,-1.75cm-0.5cm-0.1cm) $);
\draw[->, thick] ($ (localpipeline2) + (0cm,-1.65cm) $) -- ($ (localpipeline2) + (0cm,-1.75cm-0.5cm-0.1cm) $);
\draw[->, thick] ($ (localpipeline3) + (0cm,-1.65cm) $) -- ($ (localpipeline3) + (0cm,-1.75cm-0.5cm-0.1cm) $);

\node[draw, rectangle, rounded corners, minimum width=0.8cm, minimum height=5.3cm, KIT_gruen_1, fill=KIT_gruen_5] (configuration) at (0cm+2.5cm+0.5cm,0cm-1cm-2cm+0.75cm) {\rotatebox{90}{Configuration}};

\draw[dotted, thick, KIT_gruen_1] ($ (configuration) + (-0.4cm,1.5cm) $) -- ($ (configuration) + (0.4cm,1.5cm) $);

\draw[->, thick, KIT_gruen_1] ($ (configuration) + (-0.4cm,2.4cm) $) -- ($ (configuration) + (-0.4cm-0.9cm,2.4cm) $);
\draw[->, thick, KIT_gruen_1] ($ (configuration) + (-0.4cm,0.5cm) $) -- ($ (configuration) + (-0.4cm-3.9cm,0.5cm) $);
\draw[->, thick, KIT_gruen_1] ($ (configuration) + (-0.4cm,0.4cm) $) -- ($ (configuration) + (-0.4cm-2.9cm,0.4cm) $);
\draw[->, thick, KIT_gruen_1] ($ (configuration) + (-0.4cm,0.3cm) $) -- ($ (configuration) + (-0.4cm-1.9cm,0.3cm) $);
\draw[->, thick, KIT_gruen_1] (configuration) -- ($ (configuration) + (0cm,2.65cm+0.4cm) $) -- ($ (eventprovider) + (-0.2cm,2.65cm+0.4cm) $) -- ($ (eventprovider) + (-0.2cm,2.65cm-0.2cm) $);

\draw[->, thick] (configuration) |- (output);

\draw[dashed, thin] ($ (eventprovider) + (0cm,2.65cm) $) -- ($ (eventprovider) + (0cm,2.65cm+0.2cm) $) -- ($ (configuration) + (-0.6cm,2.65cm+0.2cm) $) -- ($ (configuration) + (-0.6cm,-2.65cm-0.2cm) $) -- ($ (eventprovider) + (0cm,-2.65cm-0.2cm) $) -- ($ (eventprovider) + (0cm,-2.65cm) $);
\node at ($ (eventprovider) + (1cm,-2.65cm-0.2cm-1.5ex) $) {\textit{Event Loop}};
\end{tikzpicture}

\end{document}

### 2015-09-03 HarryPlotter/python/plotbase.py
web plotting: added --www-title and --www-text arguments to make gallery title and text configurable

@@ -155,6 +155,10 @@ class PlotBase(processor.Processor):
 		                                 help="""Push output plots directly to your public EKP webspace.
 		                                 Default location is http://www-ekp.physik.uni-karlsruhe.de/~<USER>/plots_archive/<DATE>
 		                                 Optional argument is the name of a subdirectory that will appended to the default location.""")
+		self.other_options.add_argument("--www-title", type=str, default="Plot overview",
+		                                 help="Title for the web gallery. [Default: %(default)s]")
+		self.other_options.add_argument("--www-text", type=str, default=None,
+		                                 help="Text for the web gallery. [Default: download-link]")
 	
 	def prepare_args(self, parser, plotData):
 		super(PlotBase, self).prepare_args(parser, plotData)

### 2015-09-03 HarryPlotter/python/plotdata.py

@@ -69,31 +69,38 @@ class PlotData(object):
 				html_content = ""
 
 				log.info("Copying plots to webspace...")
+
+				# get the html templates
+				html_texts = {}
+				for var in ['overview', 'description', 'plot']:
+					with open(os.path.expandvars("$ARTUSPATH/HarryPlotter/data/template_webplotting_{}.html".format(var))) as htmlfile:
+						html_texts[var] = string.Template(htmlfile.read())
+				html_texts['description'] = html_texts['description'].substitute(url=url)
+				if self.plotdict["www_text"]:
+					html_texts['description'] = self.plotdict["www_text"]
+
 				# loop over plots, make gallery
-				
-				html_template = None
-				with open(os.path.expandvars("$ARTUSPATH/HarryPlotter/data/template_webplotting_overview.html")) as html_template_file:
-					html_template = string.Template(html_template_file.read())
-				
-				html_template_plot = None
-				with open(os.path.expandvars("$ARTUSPATH/HarryPlotter/data/template_webplotting_plot.html")) as html_template_plot_file:
-					html_template_plot = string.Template(html_template_plot_file.read())
-				
 				for plot in [p for p in plots_for_gallery]:
 					# try to link to pdf file, if it exists
 					href = plot.replace('.png', '.pdf')
 					if href not in plots_for_gallery:
 						href = plot
 					filename = os.path.splitext(plot)[0]
-					html_content += html_template_plot.substitute(
+					html_content += html_texts['plot'].substitute(
 							title=filename,
 							href=href,
 							plot=plot,
 							json=filename+".json"
 					)
+				# put the html parts together and write
 				with open(os.path.join(self.plotdict["output_dir"], overview_filename), "w") as overview_file:
-					overview_file.write(html_template.substitute(url=url, html_content=html_content))
+					overview_file.write(html_texts['overview'].substitute(
+						html_content=html_content,
+						title=self.plotdict["www_title"],
+						text=html_texts['description']
+					))
 
+				# find out which files to copy
 				files_to_copy = (
 					self.plotdict["output_filenames"]
 					+ [os.path.join(self.plotdict["output_dir"], overview_filename)]

### 2015-09-03 Utility/python/tools.py
tools.py: added special case for n_processes=1 in parallelize function

@@ -145,8 +145,16 @@ def get_indented_text(prefix, message, width=None):
 	return '\n'.join(['\n'.join(tmp_wrapped_texts)])
 
 def parallelize(function, arguments_list, n_processes=1):
-	pool = multiprocessing.Pool(processes=n_processes)
-	results = pool.map_async(function, arguments_list)
-	# 9999999 is needed for KeyboardInterrupt to work: http://stackoverflow.com/questions/1408356/keyboard-interrupts-with-pythons-multiprocessing-pool
-	return results.get(9999999)
+	if n_processes <= 1:
+		results = []
+		for arguments in arguments_list:
+			if isinstance(arguments, basestring):
+				results.append(function(arguments))
+			else:
+				results.append(function(*arguments))
+		return results
+	else:
+		pool = multiprocessing.Pool(processes=n_processes)
+		results = pool.map_async(function, arguments_list)
+		return results.get(9999999) # 9999999 is needed for KeyboardInterrupt to work: http://stackoverflow.com/questions/1408356/keyboard-interrupts-with-pythons-multiprocessing-pool
 

### 2015-09-03 Core/doc/latex/include/tikz_includes.tex
doc: change directory structure

% taken from
% http://www.lns.cornell.edu/~pt267/files/code/TikZFeynman.tex

\usepackage{tikz}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{trees}
\usetikzlibrary{matrix,arrows} 				% For commutative diagram
											% http://www.felixl.de/commu.pdf
\usetikzlibrary{positioning}				% For "above of=" commands
\usetikzlibrary{calc,through}				% For coordinates
\usetikzlibrary{decorations.pathreplacing}  % For curly braces
% http://www.math.ucla.edu/~getreuer/tikz.html
\usepackage{pgffor}							% For repeating patterns

\usetikzlibrary{decorations.pathmorphing}	% For Feynman Diagrams
\usetikzlibrary{decorations.markings}
\tikzset{
	>=stealth', %%  Uncomment for more conventional arrows
    vector/.style={decorate, decoration={snake}, draw},
	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
    fermion/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow{>}}}},
    fermionbar/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow{<}}}},
    fermionnoarrow/.style={draw=black},
    gluon/.style={decorate, draw=black,
        decoration={coil,amplitude=4pt, segment length=5pt}},
    scalar/.style={dashed,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow{>}}}},
    scalarbar/.style={dashed,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow{<}}}},
    scalarnoarrow/.style={dashed,draw=black},
    electron/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow{>}}}},
	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
}

### 2015-09-03 Core/doc/latex/paper.tex
paper.tex: first draft (copy from my thesis)

%\documentclass[a4paper,oneside,BCOR12.5mm,ngerman,12pt]{scrartcl}
\documentclass[a4paper, oneside, 10pt]{scrartcl}

\usepackage{booktabs}
\usepackage{hepnames}
\usepackage{hepunits}
\usepackage{url}

\input{include/tikz_includes}
\input{include/colors}

\begin{document}
\section{Development of a General Analysis Framework in C++ \label{section_artus}}

\subsection{Common Workflow of High Energy Physics Analyses \label{section_artus_analysis_workflow}}

Between the data taking at the detector or the generation of Monte Carlo events with the subsequent detector simulation and the showcasing of the physical results, the following analysis steps have to be performed.

The event reconstruction of the raw detector data is performed on large computing centres in the WLCG. The reconstructed data is stored in different formats at multiple sites in the WLCG. Usually, the AOD or the miniAOD format is used for physics analyses. These formats contain as much information about the events as needed to serve the general needs of the analysis groups.

This step is followed by the skimming of data sets that are relevant for a specific analysis. Both the number of events as well as the event content is reduced in order to speed up the following processing of the data. By requiring data sets for certain high level triggers and applying cuts on event quantities, the number of events is reduced. Only the event quantities, that are relevant for a given analysis, are written out. The skimming step is usually performed on grid sites where the data is located. Sometimes, the data is also transferred to sites, where free computing resources are available. The output is an analysis-dependent n-tuple format that is stored at local file servers. The size of files needed for a certain analysis ranges from $\mathcal O(10)$~GB to few~TB.

As an example, the $\PH\to\Pgt\Pgt\to\Pgm\Pgm$ analysis, used a data set containing only events that were accepted by double-muon triggers. Additionally, there was no need to store reconstructed \Pgt leptons (that decay hadronically) as there is no veto on taus like on electrons and third muons.

The skimmed n-tuples are finally analysed by user code on local computing resources. Events are selected and categorised, high-level calculations based on the physics objects are performed and the output is either again written to smaller n-tuples or histograms. The events are usually processed with different configurations depending on the analysis needs. The output is then used for post-processing steps including the plotting of results. The post-processing does not necessarily require an event-based processing and therefore also needs on average the smallest computing resources.

\subsection{The Artus Framework \label{section_artus_motivation}}

The framework introduced in this section handles the last step, the user analysis. In many cases the code is developed without a strategy or structure according to the growing needs of the analysis. This leads to analysis code that convoluted, tangled and unstructured. Such code is difficult to understand and to maintain and also difficult to hand over to new people joining the analysis effort. Secondly, code is rarely shared among different analysis groups, although basic parts of the analysis like the processing n-tuple-structured data or the selection and identification of physics objects follow the same principles. This usually leads to code duplication slowing down the analysis effort.

Following the structure of the CMSSW framework, the Artus framework\footnote{\url{https://github.com/artus-analysis/Artus}} provides a front-to-end solution for the analysis of event-based data. The basic concept of modules processing the events within an event loop is complemented by tools for the configuration of every step. The complete structure is explained in the next section~\ref{section_artus_structure}.

This general framework is applicable to any kind of event processing analysis. The well-tested core is shared among various analyses, providing a reliable fundament for any new analysis. The highly modular structure guides the user to develop analysis software that is easily maintainable and constructively extensible. Thus, thes Artus framework avoids the aforementioned problems of separate user code for individual analyses.

The Artus framework is written in C++. The core of the framework only depends on the boost library\footnote{\url{http://www.boost.org/}}. Further dependencies may be introduced by the actual analysis code. C++ is chosen for performance reasons and in order to be able to integrate existing frameworks and libraries that are commonly used in high energy physics.

\subsection{Structure of the Framework \label{section_artus_structure}}

The basic concept of the framework is taken from the code used for the $\PZ+\text{jet}$ analysis documented in reference~\cite{joram_phd}. It is generalised and extended to satisfy the needs of various analysis groups. The structure is illustrated in figure~\ref{figure_artus_structure}.

\begin{figure}[p]
\centering \input{figures/artus_structure}
\caption[Structure of an Artus analysis.]{Structure of an Artus analysis. The input is read by an event provider. Within the pipelines the event content is analysed by the processors. Consumers in local pipelines write results to a common output. All parts of the analysis are configurable.}
\label{figure_artus_structure}

\vspace{10ex}

\centering \input{figures/artus_pipeline}
\caption[Organisation of processors in a pipeline.]{Organisation of processors in a pipeline. Producers and filters are run before the consumers. All processors can access the pipeline settings, the event content and the product. Only producers have write access to the product. Consumers can write results to the output file.}
\label{figure_artus_pipeline}
\end{figure}

At the beginning a configuration file in the JSON format is read in. It contains information on the input data and settings for the pipelines and processors described in the following. Each of the modules described in the following has access to the settings read in from the configuration file.

The input is handled by an event provider. Its purpose is to manage reading events contents from any kind of input into an event object and to provide information about the total number of events to be processed.

The events are then sequentially processed by processors organised in pipelines. First, a so-called global pipeline is run. Then the execution is split up into multiple so-called local pipelines, that are also processed sequentially. The composition of a pipeline is illustrated in figure~\ref{figure_artus_pipeline}.

Each pipeline has its own settings. The local pipelines can access both their own settings and the ones of the global pipeline. Thus, a mechanism exists that enables processing the same event with different configurations, whereas the costly reading of the input is only needed to be done once. Similarly, a product object is managed by each pipeline. The product is meant to store new quantities produced in the analysis. The product for the global pipeline is empty at the beginning of the processing of a new event. Local pipelines start with a copy of the global product.

A pipeline consists of an arbitrary number of processor modules that are run in a sequence. Three kinds of processors are distinguished:
\begin{description}
\item[Producers] are meant to calculate new quantities based on the information in the event and the product and following the settings of the pipeline.
\item[Filters] apply cuts. In case an event does not survive a requirement defined by a filter, the processing of the subsequent producers and filters is skipped.
\item[Consumers] can be added to local pipelines. They are executed after the producers and filters. The task of consumers is to take quantities from the event and the product and store them in the output according to the pipeline settings.
\end{description}
Producers and filters can be configured in an arbitrary order. Consumers are executed after the chain of producers and filters. The output together with the complete configuration is written to a ROOT file. These processors are created and managed by a dedicated factory according to the configuration.

This structure extends the established concepts of existing frameworks like FWLite~\cite{FWLite} from CMSSW to the following four main advantages:
\begin{description}
\item[Modular structure] Analysis steps are implemented in processors, breaking down the complete analysis in well-defined and easily understandable and writeable parts.
\item[Re-utilisation of code] Processors can be shared among different analysis groups. Every user contributes to the testing of existing code and improves the confidence in this code.
\item[Configurability] Each module uses settings that are read from the the configuration. Each pipeline is mapped to a separate sub-set of the configuration.
\item[High performance] The concept of pipelines allows to analyse the data with different configurations at the same time, while the data is only read in only once and common processing steps are shared in the global pipeline. Therefore the cost-intensive input operations are reduced to a minimum.
\end{description}

\subsection{Building an End-user Analysis \label{section_artus_analysis}}

In the Artus framework each concrete analysis is defined by a set of object types. It needs an implementation of the classes for settings, the event and the product. The settings class defines the tags that should be able to be read from the configuration file and the corresponding types of the values. The event class defines the event content being read from the input and the product class contains members for new quantities being calculated by the analysis. These three classes need to be derived from the base classes in the core of the framework.

An implementation of an event provider must be available. The event provider must know how to read event content from the input files and how to store them in the event object. Furthermore, a factory managing the creation of analysis-specific processors needs to exists. These classes also have to be derived from the Artus base classes.

The most important part of an analysis are the processors. The abstract processors of the Artus core need to be implemented to realise the physics needs of the analysis in the form of code. New processors have to be registered in the factory. After the basic structure of an analysis is set up, most of changes and additions are only related to the processors.

Analyses that share the input file format can easily also share processors, that implement basic analysis steps in a general fashion. Analysis-specific parts can either derive from exiting processor classer or be modelled in new processors.

\subsection{HarryPlotter -- Python Post-processing Framework \label{section_artus_harryplotter}}

The computationally expensive event processing steps are followed by the post-processing of the results and their presentation. From a technical point of view the focus here is rather on flexibility than on performance. The inputs for this step are either histograms filled in the previous step or n-tuples whose entries can be filled into histograms at low no cost. For this reason, Python has been chosen as language for the HarryPlotter framework\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/HarryPlotter}}. As the name implies, the main focus is on plotting of results. The modular structure allows to integrate multiple analysis steps and several output formats.

\begin{figure}[htb]
\centering \input{figures/harry_plotter}
\caption{Structure of the HarryPlotter framework. The processing of input modules is followed by the run of analysis modules and concluded by the execution of plot modules. The configuration via a command line interface or via JSON files is parsed by an argument parser whose arguments are defined by the individual modules.}
\label{figure_artus_harry_plotter}
\end{figure}

The structure of the framework is illustrated in figure~\ref{figure_artus_harry_plotter}. It follows the idea of processors in the Artus framework. Three kinds of processor modules are executed subsequently:
\begin{enumerate}
\item One or, in special cases, more input modules are run to read in data from an input source. The input format is defined by the input module. The most commonly used input module is the one that reads histograms or other objects from ROOT files.
\item An arbitrary number of analysis modules is appended. They can perform calculations based on the inputs or the results of previously run analysis modules.
\item One or, in special cases, multiple plot modules are executed in the last step. Their function is to output the processed data in the specified format. In most of the cases, the output is a plot but it is also possible to store the objects in new ROOT files.
\end{enumerate}
All processors share a common plot data objects and possible meta-data where they can add new information and read the existing one. For example, the input modules add histograms read in from input files and the plot modules access these histograms.

The configuration is provided by an argument parser that can handle both arguments from a command line interface and content from JSON configuration files or Python dictionaries. This makes it possible to use either the HarryPlotter executable configured via the command line or call the main function within another Python script. The executable can perform one single plot per run. For the execution within a script functions exist to create multiple plots in parallel.

The parsing of the arguments is performed in two steps. The first time it determines the sequence of modules to be executed. These modules are then initialised and can define additional arguments needed for their configuration, such that every module can manage its own settings but can also access the settings of entire program. After all arguments are defined the configuration is parsed a second time providing the full settings for the HarryPlotter run. Then all processors are executed as described above.

\subsection{A Real World Application -- the $\PH\to\Pgt\Pgt$ Analysis \label{section_artus_example_htt}}

Currently, the Artus framework is used for various user analysis of CMS data ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model. As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis presented in this thesis are explained in the following.

The $\PH\to\Pgt\Pgt$ analysis developed in the scope of this thesis makes use of skimmed data sets in the Kappa format. The Kappa framework\footnote{\url{https://github.com/KappaAnalysis/Kappa}} is designed for skimming CMS data into small n-tuples that can be analysed independently of the CMSSW software. The only dependence is the ROOT framework. The n-tuples store high-level information such as four-momentum vectors, collections of leptons and vertices. Similar as the Artus framework, Kappa aims to satisfy general analysis needs.

A large part of the Artus software is specialised on the analysis of Kappa n-tuples\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/KappaAnalysis}}. An event provider is available for reading Kappa n-tuples. The event class contains members for all important physics objects used in analyses. The branches of the n-tuples, that should be read in from the input files, are configurable. Reducing the amount of information transferred from the input files accelerates the analysis significantly.

The structure of the pipelines is chosen such that for each decay channel a separate pipeline exists. Each of the pipelines is duplicated and modified in order to implement the different settings for shifts of quantities affected by systematic uncertainties. For example, the \Pgt energy scale is shifted up and down with respect to the nominal value. The change of the \Pgt four-momentum is then propagated through the entire analysis and the effect on the final result is studied. For this, each pipeline for decay channels involving hadronically decaying \Pgt leptons is duplicated three times and the setting for the \Pgt energy scale shift is modified accordingly. The global pipeline is used to perform actions that are common for all channels. This is for example the identification of jets and their correction as well as the filtering of valid data events.

The producers and filters are implemented to perform small tasks of the analysis. Main producers are the ones for the identification and the selection of valid leptons and jets. Further producers perform the matching with trigger or generator objects and do the splitting into decay channels or the categorisation. Also the mass reconstruction is done in a separate producer. The selection of events according to high level trigger decisions as well as the selection of decay channels are examples for filters. The filters are executed as early as possible in the chain of processors in order to avoid running subsequent processors without real need.

Table~\ref{table_artus_runtime_comparison} shows a runtime measurement for the baseline part of the $\PH\to\Pgt\Pgt$ in the four main channels ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$ and $\Pgt\Pgt$). It illustrates the main advantage of the Artus structure: sub-analyses with different sets of configurations can be performed in the same run avoiding the multiple IO overhead when the configurations would be performed sequentially in different runs.

%time HiggsToTauTauAnalysis.py @HiggsAnalysis/KITHiggsToTauTau/data/ArtusWrapperConfigs/Sync13TeV.cfg -i HiggsAnalysis/KITHiggsToTauTau/data/Samples/NAF_sample_DYJetsToLLM50_RunIISpring15DR74_Asympt25ns_13TeV_MINIAOD_amcatnloFXFX-pythia8_recent.txt -f 10
\begin{table}[h!]
\centering
\begin{tabular}{lrr}
\textbf{Pipelines}                                & \textbf{Runtime / \minute} & \textbf{Event Rate / \reciprocal\second} \\ \midrule
%0                                                & 5:53                             & 1296 \\
 0                                                & 5:12                             & 1470 \\ \midrule
%\em                                              & 6:27                             & 1181 \\
 1 ($\Pe\Pe$)                                     & 6:31                             & 1174 \\
%1 ($\Pe\Pgt$)                                    & 7:03                             & 1084 \\
 1 ($\Pe\Pgt$)                                    & 7:26                             & 1028 \\
%1 ($\Pgm\Pgt$)                                   & 7:14                             & 1054 \\
 1 ($\Pgm\Pgt$)                                   & 7:14                             & 1052 \\
%1 ($\Pgt\Pgt$)                                   & 6:14                             & 1224 \\
 1 ($\Pgt\Pgt$)                                   & 6:07                             & 1247 \\ \midrule
%2 ($\Pgm\Pgt$, $\Pe\Pgt$)                        & 8:33                             & 893 \\
 2 ($\Pgm\Pgt$, $\Pe\Pgt$)                        & 8:32                             & 896 \\
%3 ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$)             & 9:59                             & 760 \\
 3 ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$)             & 9:54                             & 767 \\
%4 ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$, $\Pgt\Pgt$) & 10:46                            & 712 \\
 4 ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$, $\Pgt\Pgt$) & 10:01                            & 758 \\
\end{tabular}
\caption[Measurement of the runtime of the baseline $\PH\to\Pgt\Pgt$ analysis.]{Measurement of the runtime of the baseline $\PH\to\Pgt\Pgt$ analysis. The analysis is performed on 10 files with a total size of 6.1~GB containing 452229 simulated $\PZ+\text{jet}$ events. The measurement is performed with different numbers of pipelines, where each pipeline implements the analysis of one sub-channel of the analysis. The values are compared with the execution without any pipelines and without global processors. It is clearly visible, that the time needed for reading the inputs amounts to a large part of the overall runtime and that the simultaneous execution of multiple pipelines can reduce the runtime significantly compared to the case where different configuration are performed sequentially including separate IO operations.}
\label{table_artus_runtime_comparison}
\end{table}

The outputs are flat n-tuples suitable for performing the background modelling step done in HarryPlotter. Histograms are read while cuts for the final event selection are applied. As an example, the cut on the transverse mass is applied on this level because events from control regions needed to be preserved for the background modelling step. For each background process, an analysis module has been developed performing the estimation of the samples. Most of them perform calculations on multiple histograms, defining the yield and the shape of the final quantity in signal and control regions. They add a single histogram to the plot data object containing the final estimation for a given sample. Similarly, ratios comparing the compatibility of data and the simulation for the sub-plots are determined and added this way.

The post-processing step either outputs the plots shown in this thesis or writes the histograms to ROOT files and passes them over to the limit calculation tools.

\end{document}

### 2015-09-07 Utility/python/jsonTools.py
jsonTools.py: fixed uncommenting

@@ -302,7 +302,9 @@ class JsonDict(dict):
 					pass
 					#del jsonDict[key]
 				else:
-					if isinstance(value, basestring) and value.strip().startswith(JsonDict.COMMENT_DELIMITER):
+					if isinstance(value, dict):
+						JsonDict.deepuncomment(value)
+					elif isinstance(value, basestring) and value.strip().startswith(JsonDict.COMMENT_DELIMITER):
 						del jsonDict[key]
 					elif isinstance(value, collections.Iterable) and not isinstance(value, basestring):
 						for index, element in list(enumerate(value))[::-1]:
@@ -313,8 +315,6 @@ class JsonDict(dict):
 									log.fatal("Error removeing Key %s from Arguments" % element)
 									sys.exit()
 
-					if isinstance(value, dict):
-						JsonDict.deepuncomment(value)
 		return jsonDict
 
 	@staticmethod

### 2015-09-07 Utility/python/jsonTools.py
jsonTools.py, dcache-tools.py: fixed log.fatal calls

@@ -313,7 +313,7 @@ class JsonDict(dict):
 									del value[index]
 								except KeyError, e:
 									log.fatal("Error removeing Key %s from Arguments" % element)
-									sys.exit()
+									sys.exit(1)
 
 		return jsonDict
 

### 2015-09-07 Utility/scripts/dcache-tools.py

@@ -58,6 +58,7 @@ def list_of_files(prefix, src, recursive):
 def get_mapping_src_dst(src_files, src_files_recursive, dst_files):
 	if not (len(dst_files) == 1 or len(dst_files) == len(src_files)):
 		log.fatal("Wrong number of destinations!")
+		sys.exit(1)
 	
 	tmp_dst_files = (dst_files * len(src_files))[:len(src_files)]
 	

### 2015-09-07 KappaAnalysis/interface/Producers/JetCorrectionsProducer.h
JetCorrectionsProducer.h: correct jets only if at least one correction parameters file has been specified

@@ -71,7 +71,10 @@ public:
 			jecParameters.push_back(JetCorrectorParameters(*jecParametersFile));
 			LOG(DEBUG) << "\t\t" << *jecParametersFile;
 		}
-		factorizedJetCorrector = new FactorizedJetCorrector(jecParameters);
+		if (jecParameters.size() > 0)
+		{
+			factorizedJetCorrector = new FactorizedJetCorrector(jecParameters);
+		}
 		
 		// initialise uncertainty calculation
 		LOG(DEBUG) << "\tLoading JetCorrectionUncertainty from files...";
@@ -112,9 +115,12 @@ public:
 		}
 		
 		// apply jet energy corrections and uncertainty shift
-		correctJets(&correctJetsForJecTools, factorizedJetCorrector, jetCorrectionUncertainty,
-		            event.m_pileupDensity->rho, event.m_vertexSummary->nVertices, -1,
-		            settings.GetJetEnergyCorrectionUncertaintyShift());
+		if (factorizedJetCorrector != nullptr)
+		{
+			correctJets(&correctJetsForJecTools, factorizedJetCorrector, jetCorrectionUncertainty,
+			            event.m_pileupDensity->rho, event.m_vertexSummary->nVertices, -1,
+			            settings.GetJetEnergyCorrectionUncertaintyShift());
+		}
 		
 		// create the shared pointers to store in the product
 		(product.*m_correctedJetsMember).clear();
@@ -157,8 +163,8 @@ private:
 	std::vector<TJet>* KappaEvent::*m_basicJetsMember;
 	std::vector<std::shared_ptr<TJet> > KappaProduct::*m_correctedJetsMember;
 	
-	FactorizedJetCorrector* factorizedJetCorrector = 0;
-	JetCorrectionUncertainty* jetCorrectionUncertainty = 0;
+	FactorizedJetCorrector* factorizedJetCorrector = nullptr;
+	JetCorrectionUncertainty* jetCorrectionUncertainty = nullptr;
 };
 
 

### 2015-09-07 KappaAnalysis/interface/Producers/JetCorrectionsProducer.h
JetCorrectionsProducer.h: improvements

@@ -78,11 +78,15 @@ public:
 		
 		// initialise uncertainty calculation
 		LOG(DEBUG) << "\tLoading JetCorrectionUncertainty from files...";
-		if (! settings.GetJetEnergyCorrectionUncertaintyParameters().empty())
+		if ((! settings.GetJetEnergyCorrectionUncertaintyParameters().empty()) &&
+		    (settings.GetJetEnergyCorrectionUncertaintyShift() != 0.0))
 		{
-			JetCorrectorParameters *jecUncertaintyParameters = NULL;
+			JetCorrectorParameters* jecUncertaintyParameters = nullptr;
 			if (!settings.GetJetEnergyCorrectionUncertaintySource().empty()) {
-				jecUncertaintyParameters = new JetCorrectorParameters(settings.GetJetEnergyCorrectionUncertaintyParameters(), settings.GetJetEnergyCorrectionUncertaintySource());
+				jecUncertaintyParameters = new JetCorrectorParameters(
+						settings.GetJetEnergyCorrectionUncertaintyParameters(),
+						settings.GetJetEnergyCorrectionUncertaintySource()
+				);
 			}
 			else {
 				jecUncertaintyParameters = new JetCorrectorParameters(settings.GetJetEnergyCorrectionUncertaintyParameters());
@@ -115,12 +119,9 @@ public:
 		}
 		
 		// apply jet energy corrections and uncertainty shift
-		if (factorizedJetCorrector != nullptr)
-		{
-			correctJets(&correctJetsForJecTools, factorizedJetCorrector, jetCorrectionUncertainty,
-			            event.m_pileupDensity->rho, event.m_vertexSummary->nVertices, -1,
-			            settings.GetJetEnergyCorrectionUncertaintyShift());
-		}
+		correctJets(&correctJetsForJecTools, factorizedJetCorrector, jetCorrectionUncertainty,
+		            event.m_pileupDensity->rho, event.m_vertexSummary->nVertices, -1,
+		            settings.GetJetEnergyCorrectionUncertaintyShift());
 		
 		// create the shared pointers to store in the product
 		(product.*m_correctedJetsMember).clear();

### 2015-09-07 Core/doc/latex/paper.tex
paper.tex: change to paper.tex document class, removed one level of sections

@@
-%\documentclass[a4paper,oneside,BCOR12.5mm,ngerman,12pt]{scrartcl}
-\documentclass[a4paper, oneside, 10pt]{scrartcl}
+% http://www.elsevier.com/authors/author-schemas/latex-instructions
+% http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/elsarticle/doc/elsdoc.pdf
+\documentclass[3p]{elsarticle}
 
@@
 
+% http://latex-community.org/forum/viewtopic.php?f=4&t=11123#p42875
+\makeatletter
+\def\ps@pprintTitle{%
+  \let\@oddhead\@empty
+  \let\@evenhead\@empty
+  \def\@oddfoot{\reset@font\hfil\thepage\hfil}
+  \let\@evenfoot\@oddfoot
+}
+\makeatother
+
 \begin{document}
-\section{Development of a General Analysis Framework in C++ \label{section_artus}}
 
-\subsection{Common Workflow of High Energy Physics Analyses \label{section_artus_analysis_workflow}}
+\begin{frontmatter}
+\title{Artus -- Framework for Event-based Data Analysis in High Energy Physics}
+
+\author[kit]{Thomas M\"uller}
+\address[kit]{Karlsruhe Institute of Technology, Wolfgang-Gaede-Stra\ss{}e 1, D-76131 Karlsruhe}
+
+\begin{abstract}
+abstract
+\end{abstract}
+
+%\begin{keyword}
+%keyword
+%\end{keyword}
+\end{frontmatter}
+
+\section{Common Workflow of High Energy Physics Analyses \label{section_artus_analysis_workflow}}
 
@@
 
-\subsection{The Artus Framework \label{section_artus_motivation}}
+\section{The Artus Framework \label{section_artus_motivation}}
 
@@
 
-\subsection{Structure of the Framework \label{section_artus_structure}}
+\section{Structure of the Framework \label{section_artus_structure}}
 
@@
 
-\subsection{Building an End-user Analysis \label{section_artus_analysis}}
+\section{Building an End-user Analysis \label{section_artus_analysis}}
 
@@
 
-\subsection{HarryPlotter -- Python Post-processing Framework \label{section_artus_harryplotter}}
+\section{HarryPlotter -- Python Post-processing Framework \label{section_artus_harryplotter}}
 
@@
 
-\subsection{A Real World Application -- the $\PH\to\Pgt\Pgt$ Analysis \label{section_artus_example_htt}}
+\section{A Real World Application -- the $\PH\to\Pgt\Pgt$ Analysis \label{section_artus_example_htt}}
 

### 2015-09-07 Core/doc/latex/paper.tex
paper.tex: comments by Gregor

@@
 In many cases the code is developed without a strategy or structure according to the growing needs of the analysis.
-This leads to analysis code that convoluted, tangled and unstructured.
+This leads to analysis code that is convoluted, tangled and unstructured.
 Such code is difficult to understand and to maintain and also difficult to hand over to new people joining the analysis effort.
@@
 Analyses that share the input file format can easily also share processors, that implement basic analysis steps in a general fashion.
-Analysis-specific parts can either derive from exiting processor classer or be modelled in new processors.
+Analysis-specific parts can either derive from existing processor classer or be modelled in new processors.
 
@@
 From a technical point of view the focus here is rather on flexibility than on performance.
-The inputs for this step are either histograms filled in the previous step or n-tuples whose entries can be filled into histograms at low no cost.
+The inputs for this step are either histograms filled in the previous step or n-tuples whose entries can be filled into histograms at low cost.
 For this reason, Python has been chosen as language for the HarryPlotter framework\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/HarryPlotter}}.
@@
 \end{enumerate}
-All processors share a common plot data objects and possible meta-data where they can add new information and read the existing one.
+All processors share a common plot data object and possible meta-data where they can add new information and read the existing one.
 For example, the input modules add histograms read in from input files and the plot modules access these histograms.

### 2015-09-07 HarryPlotter/python/plotdata.py
plotdata: add default value in case the key does not exist

@@ -107,7 +107,7 @@ class PlotData(object):
 				)
 				if self.plotdict["export_json"]:
 					files_to_copy += [self.plotdict["export_json"]]
-				if self.plotdict["save_legend"]:
+				if self.plotdict.get("save_legend", False):
 					files_to_copy += [os.path.join(self.plotdict["output_dir"], ".".join([self.plotdict["save_legend"], _format])) for _format in self.plotdict["formats"]]
 				# create remote dir, copy files
 				sshpc = tools.get_environment_variable("HARRY_SSHPC")

### 2015-09-07 HarryPlotter/python/plot_modules/plotmpl.py
plotmpl.py: implement step option for plotting of TGraphs

@@ -237,8 +237,8 @@ class PlotMpl(plotbase.PlotBase):
 				self.plot_dimension = 1
 				self.mplhist = MplGraph(root_object)
 
-				if (isinstance(root_object, ROOT.TGraphErrors) and  marker=='fill'):
-					self.plot_tgrapherrors_envelope(self.mplhist, ax, label, color, line_style, line_width)
+				if marker=='fill':
+					self.plot_tgrapherrors_envelope(self.mplhist, ax, label, color, line_style, line_width, step)
 				else:
 					self.plot_errorbar(self.mplhist, ax=ax,
 					               show_xerr=x_error, show_yerr=y_error,
@@ -671,17 +671,31 @@ class PlotMpl(plotbase.PlotBase):
 			cmap=cmap, linewidth=0, antialiased=True, shade=False)
 		return artist
 
-	def plot_tgrapherrors_envelope(self, mplhist, ax, label, color, line_style, line_width):
+	def plot_tgrapherrors_envelope(self, mplhist, ax, label, color, line_style, line_width, step):
 		""" Plot the envelope given by y-errors around a TGraphErrors"""
-		ax.plot(self.mplhist.x, self.mplhist.y, label=label, color=color, linestyle=line_style, linewidth=line_width)
-		ax.fill_between(self.mplhist.x,
-			[(y_val-error) for y_val, error in zip(self.mplhist.y, self.mplhist.yerr)],
-			[(y_val+error) for y_val, error in zip(self.mplhist.y, self.mplhist.yerr)],
-			facecolor=color,
-			edgecolor=color,
-			interpolate=True,
-			alpha=0.2
-		)
+		if step:
+			# central values:
+			ax.step(self.steppify_bin(mplhist.xbinedges, isx=True), self.steppify_bin(mplhist.y),
+				label=label, linestyle=line_style)
+			# plot errors as shaded area:
+			ax.fill_between(
+				self.steppify_bin(mplhist.xbinedges, isx=True),
+				self.steppify_bin([(y_val+error) for y_val, error in zip(self.mplhist.y, self.mplhist.yerr)]),
+				y2=self.steppify_bin([(y_val-error) for y_val, error in zip(self.mplhist.y, self.mplhist.yerr)]),
+				color=color,
+				alpha=0.2,
+			)
+		else:
+			# draw a smooth curve with error band around
[…]

### 2015-09-07 Configuration/scripts/artusMergeOutputs.py
artusMergeOutputs.py: added multiprocessing

@@ -14,7 +14,13 @@ ROOT.gROOT.SetBatch(True)
 ROOT.PyConfig.IgnoreCommandLineOptions = True
 ROOT.gErrorIgnoreLevel = ROOT.kError
 
+import Artus.Utility.tools as tools
 import Artus.Utility.progressiterator as pi
+
+
+def _call_command(command):
+	log.debug(command)
+	logger.subprocessCall(command.split())
 
 
 def main():
@@ -22,6 +28,8 @@ def main():
 	parser = argparse.ArgumentParser(description="Merge Artus outputs per nick name.", parents=[logger.loggingParser])
 
 	parser.add_argument("project_dir", help="Artus Project directory containing the files \"output/*/*.root\" to merge")
+	parser.add_argument("-n", "--n-processes", type=int, default=1,
+	                    help="Number of (parallel) processes. [Default: %(default)s]")
 
 	args = parser.parse_args()
 	logger.initLogger(args)
@@ -31,6 +39,7 @@ def main():
 	outputs_per_nick = {nick : glob.glob(os.path.join(args.project_dir, "output", nick, "*.root")) for nick in nick_names}
 	outputs_per_nick = {nick : files for nick, files in outputs_per_nick.iteritems() if len(files) > 0}
 	
+	commands = []
 	for nick_name, output_files in pi.ProgressIterator(outputs_per_nick.iteritems(),
 	                                                   length=len(outputs_per_nick),
 	                                                   description="Merging Artus outputs"):
@@ -38,11 +47,9 @@ def main():
 		if not os.path.exists(merged_dir):
 			os.makedirs(merged_dir)
 	
-		command = "hadd -f %s %s" % (os.path.join(merged_dir, nick_name+".root"), " ".join(output_files))
-		log.info(command)
-		logger.subprocessCall(command.split())
-		log.info("\n")
-
+		commands.append("hadd -f %s %s" % (os.path.join(merged_dir, nick_name+".root"), " ".join(output_files)))
+	
+	tools.parallelize(_call_command, commands, n_processes=args.n_processes)
 
 if __name__ == "__main__":
 	main()

### 2015-09-07 HarryPlotter/python/plot_modules/plotmpl.py
plotbase.py: centralise creation of output directory

@@ -200,6 +200,8 @@ class PlotMpl(plotbase.PlotBase):
 		super(PlotMpl, self).set_style(plotData)
 	
 	def create_canvas(self, plotData):
+		super(PlotMpl, self).create_canvas(plotData)
+		
 		# fig = plt.figure(figsize = [
 			# plotData.plotdict['axes_layout'][0] * matplotlib.rcParams['figure.figsize'][0],
 			# plotData.plotdict['axes_layout'][1] * matplotlib.rcParams['figure.figsize'][1]

### 2015-09-07 HarryPlotter/python/plotbase.py

@@ -203,15 +203,6 @@ class PlotBase(processor.Processor):
 		
 		if plotData.plotdict["www"] != None:
 			plotData.plotdict["output_dir"] = os.path.join("websync", datetime.date.today().strftime("%Y_%m_%d"), (plotData.plotdict["www"] or ""))
-		# create output directory if not exisiting
-		try:
-			os.makedirs(plotData.plotdict["output_dir"])
-			log.info("Created output directory \"%s\"." % plotData.plotdict["output_dir"])
-		except OSError as exc:
-			# if target directory already exists, ignore exception:
-			if exc.errno == errno.EEXIST and os.path.isdir(plotData.plotdict["output_dir"]):
-				pass
-			else: raise
 		
 		# construct file name from x/y/z expressions if not specified by user
 		if plotData.plotdict["filename"] == None:
@@ -298,7 +289,15 @@ class PlotBase(processor.Processor):
 		pass
 	
 	def create_canvas(self, plotData):
-		pass
+		# create output directory if not exisiting
+		try:
+			os.makedirs(plotData.plotdict["output_dir"])
+			log.info("Created output directory \"%s\"." % plotData.plotdict["output_dir"])
+		except OSError as exc:
+			# if target directory already exists, ignore exception:
+			if exc.errno == errno.EEXIST and os.path.isdir(plotData.plotdict["output_dir"]):
+				pass
+			else: raise
 	
 	def prepare_histograms(self, plotData):
 		# handle stacks

### 2015-09-09 Core/doc/latex/paper.tex
paper: added abstract

@@
 \begin{abstract}
-abstract
+We present Artus, a data-processing application for high energy physics experiments. Artus is designed for large-scale data analysis in a collaborative environment.
+The architecture design choices take into account typical challenges and are based on experiences with similar applications.
+The structure of the framework and its advantages are described.
+An example usecase and performance measurements are presented.
+The framwork is well-tested and successfully used by several analysis groups.
+
 \end{abstract}

### 2015-09-09 Core/doc/latex/paper.tex
paper: added some authors
paper: 'Artus' in \textsc

@@
 
+\newcommand{\software}[1]{\textsc{#1}\xspace}
+\newcommand{\artus}{\software{Artus}}
+
 \begin{document}
@@
 \begin{frontmatter}
-\title{Artus -- Framework for Event-based Data Analysis in High Energy Physics}
+\title{\artus -- Framework for Event-based Data Analysis in High Energy Physics}
 
-\author[kit]{Thomas M\"uller}
+\author[kit]{Thomas M\"uller, Thomas Hauth, Dominik Haitz}
 \address[kit]{Karlsruhe Institute of Technology, Wolfgang-Gaede-Stra\ss{}e 1, D-76131 Karlsruhe}
@@
 \begin{abstract}
-We present Artus, a data-processing application for high energy physics experiments. Artus is designed for large-scale data analysis in a collaborative environment.
+We present \artus, a data-processing framework for high energy physics experiments. \artus is designed for large-scale data analysis in a collaborative environment.
 The architecture design choices take into account typical challenges and are based on experiences with similar applications.
@@
 An example usecase and performance measurements are presented.
-The framwork is well-tested and successfully used by several analysis groups.
+The framework is well-tested and successfully used by several analysis groups.
 
@@
 
-\section{The Artus Framework \label{section_artus_motivation}}
+\section{The \artus Framework \label{section_artus_motivation}}
 
@@
 
-Following the structure of the CMSSW framework, the Artus framework\footnote{\url{https://github.com/artus-analysis/Artus}} provides a front-to-end solution for the analysis of event-based data.
+Following the structure of the CMSSW framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/\artus}} provides a front-to-end solution for the analysis of event-based data.
 The basic concept of modules processing the events within an event loop is complemented by tools for the configuration of every step.
@@
 The highly modular structure guides the user to develop analysis software that is easily maintainable and constructively extensible.
-Thus, thes Artus framework avoids the aforementioned problems of separate user code for individual analyses.
+Thus, thes \artus framework avoids the aforementioned problems of separate user code for individual analyses.
 
-The Artus framework is written in C++.
+The \artus framework is written in C++.
 The core of the framework only depends on the boost library\footnote{\url{http://www.boost.org/}}.
@@
 \centering \input{figures/artus_structure}
-\caption[Structure of an Artus analysis.]{Structure of an Artus analysis.
+\caption[Structure of an \artus analysis.]{Structure of an \artus analysis.
 The input is read by an event provider.
@@
 
-In the Artus framework each concrete analysis is defined by a set of object types.
+In the \artus framework each concrete analysis is defined by a set of object types.
 It needs an implementation of the classes for settings, the event and the product.
@@
 Furthermore, a factory managing the creation of analysis-specific processors needs to exists.
-These classes also have to be derived from the Artus base classes.
+These classes also have to be derived from the \artus base classes.
 
 The most important part of an analysis are the processors.
-The abstract processors of the Artus core need to be implemented to realise the physics needs of the analysis in the form of code.
+The abstract processors of the \artus core need to be implemented to realise the physics needs of the analysis in the form of code.
 New processors have to be registered in the factory.
@@
 The structure of the framework is illustrated in figure~\ref{figure_artus_harry_plotter}.
-It follows the idea of processors in the Artus framework.
+It follows the idea of processors in the \artus framework.
 Three kinds of processor modules are executed subsequently:
@@
 
-Currently, the Artus framework is used for various user analysis of CMS data ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model.
+Currently, the \artus framework is used for various user analysis of CMS data ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model.
 As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis presented in this thesis are explained in the following.
@@
 The n-tuples store high-level information such as four-momentum vectors, collections of leptons and vertices.
-Similar as the Artus framework, Kappa aims to satisfy general analysis needs.
+Similar as the \artus framework, Kappa aims to satisfy general analysis needs.
 
-A large part of the Artus software is specialised on the analysis of Kappa n-tuples\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/KappaAnalysis}}.
+A large part of the \artus software is specialised on the analysis of Kappa n-tuples\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/KappaAnalysis}}.
 An event provider is available for reading Kappa n-tuples.
@@
 Table~\ref{table_artus_runtime_comparison} shows a runtime measurement for the baseline part of the $\PH\to\Pgt\Pgt$ in the four main channels ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$ and $\Pgt\Pgt$).
-It illustrates the main advantage of the Artus structure: sub-analyses with different sets of configurations can be performed in the same run avoiding the multiple IO overhead when the configurations would be performed sequentially in different runs.
+It illustrates the main advantage of the \artus structure: sub-analyses with different sets of configurations can be performed in the same run avoiding the multiple IO overhead when the configurations would be performed sequentially in different runs.
 

### 2015-09-09 Core/doc/latex/paper.tex
paper: added 'Requirements' section

@@
 The post-processing does not necessarily require an event-based processing and therefore also needs on average the smallest computing resources.
+
+\section{Requirements and Challenges for Analysis Software\label{section_artus_challenges}}
+%define requirements based on previous section, following sections: describe how they are fullfilled
+Based on the workflow described in the previous section, the following demands for an analyis framework arise:
+\begin{itemize}
+ \item High performance to cope with massive data amounts % -> C++, pipelines, only necessary producers
+ \item Usable for different physics analyses % -> modular structure, producers
+ \item Flexibility %TODO define need for different configurations in previous section
+ \item Compatible with different data formats % -> data format defined outside (kappa)
+ \item Easy to install, use and understand; also for programming newcomers % test analysis, tutorial, documentation(TODO)
+ \item Possibility to include libraries and existing HEP code % -> C++ used
+ \item Reliable and checked source code % -> Unit tests, code sharing
+ \item Compatibility with different operating platforms/environments % standalone compile with make, integrated batch/GC functionality
+\end{itemize}
+The \artus design choices are fully based on these requirements.
 

### 2015-09-09 Core/doc/latex/include/bib.tex
paper: added bibliography

 \begin{thebibliography}{99}

    \bibitem{joram_phd}Joram Berger,
      \textit{Search for the Higgs Boson Produced via Vector-Boson
                        Fusion in the Decay Channel H $\to \tau \tau$},
      CERN-THESIS-2014-092.

\end{thebibliography}

### 2015-09-09 HarryPlotter/python/inputbase.py
inputbase.py: Added some debug output

@@ -98,6 +98,7 @@ class InputBase(processor.Processor):
 
 			if isinstance(root_object, ROOT.TH1):
 				root_object.Scale(scale_factor)
+				log.debug("Scaling histogram {} by {}".format(nick, scale_factor))
 			elif scale_factor != 1.0:
 				log.warning("Scaling currently only implemented for histograms!")
 

### 2015-09-09 Core/doc/latex/paper.tex
paper: added comments for workflow section
paper: added bibliography
add todonotes package with first note
introduction sentence

@@
 \usepackage{url}
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
 
@@
 \begin{abstract}
-We present \artus, a data-processing framework for high energy physics experiments. \artus is designed for large-scale data analysis in a collaborative environment.
+We present \artus, an event-by-event data-processing framework for high energy physics experiments. \artus is designed for large-scale data analysis in a collaborative environment.
 The architecture design choices take into account typical challenges and are based on experiences with similar applications.
@@
 An example usecase and performance measurements are presented.
-The framework is well-tested and successfully used by several analysis groups.
-
+The framework is well-tested and successfully used by several analysis groups.\todo{Mention them, maybe with publications?}
 \end{abstract}
@@
 The post-processing does not necessarily require an event-based processing and therefore also needs on average the smallest computing resources.
+
+%Add:
+% collaborative environment, high fluctuation in developers/users with wide range of programming skills (bachelor-n00b to postdoc level)
+% different configurations also for one single analysis (testing etc.)
 
@@
 
+\vspace{2cm}
+\input{include/bib}
+
 \end{document}

### 2015-09-09 Core/doc/latex/paper.tex
intro

@@
 
-Between the data taking at the detector or the generation of Monte Carlo events with the subsequent detector simulation and the showcasing of the physical results, the following analysis steps have to be performed.
+Between the data taking at the detector or the generation of simulated events with the subsequent detector simulation and the showcasing of the physical results, the following analysis steps have shown to be the best compromise in terms of turnaround time and efficiency as explained in Figure \ref{figure_analysis_steps}.
 
-The event reconstruction of the raw detector data is performed on large computing centres in the WLCG.
+The event reconstruction of the raw detector data is performed on large computing centres in the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing grid.
 The reconstructed data is stored in different formats at multiple sites in the WLCG.
-Usually, the AOD or the miniAOD format is used for physics analyses.
+Usually, already a condensed format is used for physics analyses, where high-level physics objects are already reconstructed.
 These formats contain as much information about the events as needed to serve the general needs of the analysis groups.
 
-This step is followed by the skimming of data sets that are relevant for a specific analysis.
-Both the number of events as well as the event content is reduced in order to speed up the following processing of the data.
-By requiring data sets for certain high level triggers and applying cuts on event quantities, the number of events is reduced.
+This step is followed by the selection of data sets that are relevant for a specific analysis.
+This step is usually being referred to as skimming.
+Skimming means, that only those events that are interesting for the analysis are selected, e.g.
+by requiring only data sets for certain high level triggers or the presence of certain physical objects with desired kinematical properties.
 Only the event quantities, that are relevant for a given analysis, are written out.
-The skimming step is usually performed on grid sites where the data is located.
-Sometimes, the data is also transferred to sites, where free computing resources are available.
-The output is an analysis-dependent n-tuple format that is stored at local file servers.
+Since the WLCG follows the concept of data locality, the skimming step is usually performed on grid sites where the data is located.
+With rising network bandwith over the last few years, data locality is weakened up and techniques arose that also allow the access of data on remote sites.
+The output of the skimming is an mostly analysis-dependent n-tuple format that is small enough to be at smaller file servers, often owned and operated by a single intitute.
 The size of files needed for a certain analysis ranges from $\mathcal O(10)$~GB to few~TB.
@@
 
-The skimmed n-tuples are finally analysed by user code on local computing resources.
-Events are selected and categorised, high-level calculations based on the physics objects are performed and the output is either again written to smaller n-tuples or histograms.
+The skimmed n-tuples are finally processed by user code on resources indipendent from the WLCG.
+The analysis performs further events selectetion and categorization.
+High-level calculations based on the physics objects are performed and the output is either again written to smaller n-tuples or histograms.
 The events are usually processed with different configurations depending on the analysis needs.

### 2015-09-09 Core/doc/latex/paper.tex
analysis steps figure

@@
 
+\begin{figure}[p]
+\centering \input{figures/analysis_steps}
+\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics.
+I/O intensive operations are done in highly parallel in the WLCG.
+The computing-intensive operations are only performed if really necessary.
+This means that selection steps are performed as early as possible.}
+\label{figure_analysis_steps}
+\end{figure}
+\clearpage
 \section{Requirements and Challenges for Analysis Software\label{section_artus_challenges}}

### 2015-09-09 Core/doc/latex/paper.tex
list with substructure

@@
 \begin{itemize}
- \item High performance to cope with massive data amounts % -> C++, pipelines, only necessary producers
- \item Usable for different physics analyses % -> modular structure, producers
+ \item Performance
+ \begin{itemize}
+  \item High performance for fast turnaround cycles, even with large data amounts % -> C++, pipelines, only necessary producers
   \item Flexibility %TODO define need for different configurations in previous section
+ \end{itemize}
+ \item Maintainability
+ \begin{itemize}
+  \item Easy to install
+  \item Readable and understandable, also for programming newcomers
+  \item Compatibility with different operating platforms/environments % standalone compile with make, integrated batch/GC functionality
   \item Compatible with different data formats % -> data format defined outside (kappa)
- \item Easy to install, use and understand; also for programming newcomers % test analysis, tutorial, documentation(TODO)
- \item Possibility to include libraries and existing HEP code % -> C++ used
+  \item Clear separation of code, data and settings % -> json config
+ \end{itemize}
+
+ \item Reliability
+ \begin{itemize}
+  \item Use existing libraries and existing HEP code wherever possible % -> C++ used
   \item Reliable and checked source code % -> Unit tests, code sharing
- \item Compatibility with different operating platforms/environments % standalone compile with make, integrated batch/GC functionality
+  \item Avoids frequent re-implementations by being used in different physics analyses % -> modular structure, producers
+  \item Readable, since sourcecode is the most precise documentation possible
  \end{itemize}
+\end{itemize}
+
 The \artus design choices are fully based on these requirements.

### 2015-09-09 Core/doc/latex/paper.tex
on Artus

@@
 
-Following the structure of the CMSSW framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/\artus}} provides a front-to-end solution for the analysis of event-based data.
+Following the structure of the CMSSW \todo{Referenz?
+zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/\artus}} provides a front-to-end solution for the analysis of event-based data.
 The basic concept of modules processing the events within an event loop is complemented by tools for the configuration of every step.
@@
 The highly modular structure guides the user to develop analysis software that is easily maintainable and constructively extensible.
-Thus, thes \artus framework avoids the aforementioned problems of separate user code for individual analyses.
+Thus, the \artus framework avoids the aforementioned problems of separate user code for individual analyses.
 
@@
 C++ is chosen for performance reasons and in order to be able to integrate existing frameworks and libraries that are commonly used in high energy physics.
+
+\artus has no need to use multi-core techniques, since it can be parallelized trivially by splitting the input dataset and sending it to different computing instances.
+This is possible, because the processed events are know to be independent of each other.
 

### 2015-09-09 Core/doc/latex/paper.tex
further work

@@
 
-At the beginning a configuration file in the JSON format is read in.
+\artus respects the separation of code and settings.
+Settings select what has to be done and with wich parameters.
+The code does perform these steps, ideally without the user being fully aware of implementation details.
+The single source of truth for an analysis is therefore a JSON file that completely defines the analysis.
 It contains information on the input data and settings for the pipelines and processors described in the following.
 Each of the modules described in the following has access to the settings read in from the configuration file.
+The \artus package comes with sophisticated tools written in python, that help in generating this JSON file.
 
@@
 \item[Producers] are meant to calculate new quantities based on the information in the event and the product and following the settings of the pipeline.
-\item[Filters] apply cuts. In case an event does not survive a requirement defined by a filter, the processing of the subsequent producers and filters is skipped.
+\item[Filters] apply a selection based on event properties. In case an event does not survive a requirement defined by a filter, the processing of the subsequent producers and filters can be skipped.
 \item[Consumers] can be added to local pipelines.
@@
 Consumers are executed after the chain of producers and filters.
-The output together with the complete configuration is written to a ROOT file.
+The output together with the complete configuration is written to a ROOT \todo{Referenz auf ROOT?} file.
 These processors are created and managed by a dedicated factory according to the configuration.
-
+\todo{I would not put the remaining part of this chapter here.
+It should be either part of the requirements or part of the summary what Artus does achieve; but in this technical part in between it feels misplaced}
 This structure extends the established concepts of existing frameworks like FWLite~\cite{FWLite} from CMSSW to the following four main advantages:
@@
 \section{Building an End-user Analysis \label{section_artus_analysis}}
-
+\todo{If I wouldn't know the structure already, the following part wouldn't have helped my. Either we support it with a drawing and more detailled explanations or we just refer to a readme...}
 In the \artus framework each concrete analysis is defined by a set of object types.
@@
 New processors have to be registered in the factory.
-After the basic structure of an analysis is set up, most of changes and additions are only related to the processors.
+After the basic structure of an analysis is set up, most changes and additions are only related to the processors.
 

### 2015-09-10 Core/doc/latex/paper.tex
Authors
paper: one sentencer per line for better version control
paper: is not a thesis

@@
 
-\author[kit]{Thomas M\"uller, Thomas Hauth, Dominik Haitz}
+\author[kit]{Thomas M\"uller, Thomas Hauth, Dominik Haitz, Raphael Friese}
 \address[kit]{Karlsruhe Institute of Technology, Wolfgang-Gaede-Stra\ss{}e 1, D-76131 Karlsruhe}
@@
 \begin{abstract}
-We present \artus, an event-by-event data-processing framework for high energy physics experiments. \artus is designed for large-scale data analysis in a collaborative environment.
+We present \artus, an event-by-event data-processing framework for high energy physics experiments.
+\artus is designed for large-scale data analysis in a collaborative environment.
 The architecture design choices take into account typical challenges and are based on experiences with similar applications.
@@
 \clearpage
+
 \section{Requirements and Challenges for Analysis Software\label{section_artus_challenges}}
@@
 
-A pipeline consists of an arbitrary number of processor modules that are run in a sequence. Three kinds of processors are distinguished:
+A pipeline consists of an arbitrary number of processor modules that are run in a sequence.
+Three kinds of processors are distinguished:
 \begin{description}
 \item[Producers] are meant to calculate new quantities based on the information in the event and the product and following the settings of the pipeline.
-\item[Filters] apply a selection based on event properties. In case an event does not survive a requirement defined by a filter, the processing of the subsequent producers and filters can be skipped.
+\item[Filters] apply a selection based on event properties.
+In case an event does not survive a requirement defined by a filter, the processing of the subsequent producers and filters can be skipped.
 \item[Consumers] can be added to local pipelines.
@@
 \item[Modular structure] Analysis steps are implemented in processors, breaking down the complete analysis in well-defined and easily understandable and writeable parts.
-\item[Re-utilisation of code] Processors can be shared among different analysis groups. Every user contributes to the testing of existing code and improves the confidence in this code.
-\item[Configurability] Each module uses settings that are read from the the configuration. Each pipeline is mapped to a separate sub-set of the configuration.
+\item[Re-utilisation of code] Processors can be shared among different analysis groups.
+Every user contributes to the testing of existing code and improves the confidence in this code.
+\item[Configurability] Each module uses settings that are read from the the configuration.
+Each pipeline is mapped to a separate sub-set of the configuration.
 \item[High performance] The concept of pipelines allows to analyse the data with different configurations at the same time, while the data is only read in only once and common processing steps are shared in the global pipeline.
@@
 \section{Building an End-user Analysis \label{section_artus_analysis}}
-\todo{If I wouldn't know the structure already, the following part wouldn't have helped my. Either we support it with a drawing and more detailled explanations or we just refer to a readme...}
+\todo{If I wouldn't know the structure already, the following part wouldn't have helped my.
+Either we support it with a drawing and more detailled explanations or we just refer to a readme...}
 In the \artus framework each concrete analysis is defined by a set of object types.
@@
 The most commonly used input module is the one that reads histograms or other objects from ROOT files.
-\item An arbitrary number of analysis modules is appended. They can perform calculations based on the inputs or the results of previously run analysis modules.
+\item An arbitrary number of analysis modules is appended.
+They can perform calculations based on the inputs or the results of previously run analysis modules.
 \item One or, in special cases, multiple plot modules are executed in the last step.
@@
 Currently, the \artus framework is used for various user analysis of CMS data ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model.
-As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis presented in this thesis are explained in the following.
+As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis are explained in the following.
 
-The $\PH\to\Pgt\Pgt$ analysis developed in the scope of this thesis makes use of skimmed data sets in the Kappa format.
+The $\PH\to\Pgt\Pgt$ analysis makes use of skimmed data sets in the Kappa format.
 The Kappa framework\footnote{\url{https://github.com/KappaAnalysis/Kappa}} is designed for skimming CMS data into small n-tuples that can be analysed independently of the CMSSW software.
@@
 
-The post-processing step either outputs the plots shown in this thesis or writes the histograms to ROOT files and passes them over to the limit calculation tools.
+The post-processing step either output plots or writes the histograms to ROOT files and passes them over to the limit calculation tools.
 

### 2015-09-10 Core/doc/latex/paper.tex
paper: some comments on the comments from RF

@@
 An example usecase and performance measurements are presented.
-The framework is well-tested and successfully used by several analysis groups.\todo{Mention them, maybe with publications?}
+The framework is well-tested and successfully used by several analysis groups.\todo{Mention them, maybe with publications? -> mentioned at the beginning of Htt chapter. Do we have publications?}
 \end{abstract}
@@
 \end{figure}
+\todo{Should we drop CMS-specific technical terms like AOD/miniAOD?
+Maybe not put this figure on a dedicated page?}
 \clearpage
@@
 These processors are created and managed by a dedicated factory according to the configuration.
+
 \todo{I would not put the remaining part of this chapter here.
-It should be either part of the requirements or part of the summary what Artus does achieve; but in this technical part in between it feels misplaced}
+It should be either part of the requirements or part of the summary what Artus does achieve; but in this technical part in between it feels misplaced
+-> Should we put this part into a dedicated section directly after this one?
+I think the idea was to explain how certain design decisions, e.g. pipelines, achieve the \artus design goals.
+Therefore it shouldnt be too far from the technical descriptions.
+}
 This structure extends the established concepts of existing frameworks like FWLite~\cite{FWLite} from CMSSW to the following four main advantages:
@@
 \todo{If I wouldn't know the structure already, the following part wouldn't have helped my.
-Either we support it with a drawing and more detailled explanations or we just refer to a readme...}
+Either we support it with a drawing and more detailled explanations or we just refer to a readme...
+Maybe rewrite parts of this section}
 In the \artus framework each concrete analysis is defined by a set of object types.

### 2015-09-10 Core/doc/latex/paper.tex
paper: move 'problems of existing analyses' part into workflow chapter
paper: trying to condense workflow chapter

@@
 \section{Common Workflow of High Energy Physics Analyses \label{section_artus_analysis_workflow}}
+% This section should contain a short description of a HEP/CMS-typical workflow.
+% Especially common problems and challenges should be highlighted.
+% From these problems, the design requirements for Artus are derived.
 
@@
 
-The event reconstruction of the raw detector data is performed on large computing centres in the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing grid.
-The reconstructed data is stored in different formats at multiple sites in the WLCG.
-Usually, already a condensed format is used for physics analyses, where high-level physics objects are already reconstructed.
-These formats contain as much information about the events as needed to serve the general needs of the analysis groups.
+The reconstruction of the raw detector data is performed on large computing centres in the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing Grid.
+The resulting data sets contain event information and high-level physics objects and are of $\mathcal O(10-100)$~TB in size. \todo{move file size numbers to Figure \ref{figure_analysis_steps}?}
 
-This step is followed by the selection of data sets that are relevant for a specific analysis.
-This step is usually being referred to as skimming.
-Skimming means, that only those events that are interesting for the analysis are selected, e.g.
-by requiring only data sets for certain high level triggers or the presence of certain physical objects with desired kinematical properties.
-Only the event quantities, that are relevant for a given analysis, are written out.
-Since the WLCG follows the concept of data locality, the skimming step is usually performed on grid sites where the data is located.
-With rising network bandwith over the last few years, data locality is weakened up and techniques arose that also allow the access of data on remote sites.
-The output of the skimming is an mostly analysis-dependent n-tuple format that is small enough to be at smaller file servers, often owned and operated by a single intitute.
-The size of files needed for a certain analysis ranges from $\mathcal O(10)$~GB to few~TB.
+This is followed by the selection of data that is relevant for a specific analysis, a step usually  referred to as \textit{skimming}.
+The output of the skimming is a mostly analysis-dependent n-tuple format that is small enough to be stored at local file servers, often owned and operated by a single institute.
+The size of these files ranges from $\mathcal O(10)$~GB to few~TB.
 
-As an example, the $\PH\to\Pgt\Pgt\to\Pgm\Pgm$ analysis, used a data set containing only events that were accepted by double-muon triggers.
-Additionally, there was no need to store reconstructed \Pgt leptons (that decay hadronically) as there is no veto on taus like on electrons and third muons.
-
-The skimmed n-tuples are finally processed by user code on resources indipendent from the WLCG.
-The analysis performs further events selectetion and categorization.
-High-level calculations based on the physics objects are performed and the output is either again written to smaller n-tuples or histograms.
+The skimmed n-tuples are finally processed by user code on local resources.
+This means performing further event selection and categorization steps or high-level calculations based on the physics objects.
 The events are usually processed with different configurations depending on the analysis needs.
 The output is then used for post-processing steps including the plotting of results.
-The post-processing does not necessarily require an event-based processing and therefore also needs on average the smallest computing resources.
 
-%Add:
-% collaborative environment, high fluctuation in developers/users with wide range of programming skills (bachelor-n00b to postdoc level)
-% different configurations also for one single analysis (testing etc.)
+In many cases the code for the last step is developed without a strategy or structure according to the growing needs of the analysis.
+This leads to code that is convoluted, tangled and unstructured.
+Such code is difficult to understand and to maintain and also difficult to hand over to new people joining the analysis effort.
+Also, code is rarely shared among different groups, although basic parts of the analysis like data formats, the processing of n-tuple-structured files or the selection and identification of physics objects follow the same principles.
+The analysis groups usually consist of several people of different academic levels, some joining the analysis effort only for a short time.
+This results in a high user fluctuation and a wide range of programming skills.
 
@@
 
-The framework introduced in this section handles the last step, the user analysis.
-In many cases the code is developed without a strategy or structure according to the growing needs of the analysis.
-This leads to analysis code that is convoluted, tangled and unstructured.
-Such code is difficult to understand and to maintain and also difficult to hand over to new people joining the analysis effort.
-Secondly, code is rarely shared among different analysis groups, although basic parts of the analysis like the processing n-tuple-structured data or the selection and identification of physics objects follow the same principles.
-This usually leads to code duplication slowing down the analysis effort.
+The framework introduced in this section handles the last step of the workflow, the user analysis.
 

### 2015-09-10 HarryPlotter/python/plot_modules/plotmpl.py
plotmpl.py: add ugly workaround for MPL bug for pdf-plots without legend frame

@@ -427,6 +427,13 @@ class PlotMpl(plotbase.PlotBase):
 
 	def add_labels(self, plotData):
 		super(PlotMpl, self).add_labels(plotData)
+		# apparently MPL 121 has a bug for the PDF backend for legends without frame.
+		# workaround: set legend.frameon True, but after legend creation set edgecolor to white.
+		if ('pdf' in plotData.plotdict["formats"]) and (not matplotlib.rcParams['legend.frameon']) and (self.mpl_version == 121):
+			matplotlib.rcParams['legend.frameon'] = True
+			legend_workaround=True
+		else:
+			legend_workaround=False
 
 		#iterate over all axis objects
 		for ax in [plotData.plot.axes[0]]:
@@ -438,6 +445,8 @@ class PlotMpl(plotbase.PlotBase):
 			if len(ax.get_legend_handles_labels()[0]) > 1 and plotData.plotdict["legend"] is not None:
 				legend = ax.legend(*self.get_legend_handles_labels_ordered(ax, plotData.plotdict['labels']), loc=plotData.plotdict["legend"], ncol=plotData.plotdict["legend_cols"], columnspacing=0.5, handletextpad=0.3)
 				legend.set_zorder(100)
+				if legend_workaround:
+					legend.get_frame().set_edgecolor('#FFFFFF')
 
 			if self.mpl_version >= 121:
 				plt.tight_layout()
@@ -448,9 +457,10 @@ class PlotMpl(plotbase.PlotBase):
 		if len(plotData.plot.axes) > 1:
 			for ax in [plotData.plot.axes[1]]:
 				if len(ax.get_legend_handles_labels()[0]) > 1 and plotData.plotdict["subplot_legend"] is not None:
-					ax.legend(*self.get_legend_handles_labels_ordered(ax, plotData.plotdict['labels']), loc=plotData.plotdict["subplot_legend"], ncol=1, columnspacing=0.5, handletextpad=0.3)
-		# if plotData.plotdict['ratio'] and list(set(plotData.plotdict['ratio_labels'])) != [None]:
-			# plotData.plot.ax2.legend(loc=plotData.plotdict["legend"])
+					legend = ax.legend(*self.get_legend_handles_labels_ordered(ax, plotData.plotdict['labels']), loc=plotData.plotdict["subplot_legend"], ncol=1, columnspacing=0.5, handletextpad=0.3)
+					if legend_workaround:
[…]

### 2015-09-10 Core/doc/latex/paper.tex
paper: partial rewriting of the introduction (non controversial)

@@
 % From these problems, the design requirements for Artus are derived.
+Without loss of generality, in what follows the workflow of the experiments collecting data at the Large Hadron Collider (LHC) at CERN is taken as an example to illustate the organization and needs of a modern High Energy Physics analysis.
 
@@
 
-The reconstruction of the raw detector data is performed on large computing centres in the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing Grid.
-The resulting data sets contain event information and high-level physics objects and are of $\mathcal O(10-100)$~TB in size. \todo{move file size numbers to Figure \ref{figure_analysis_steps}?}
+The reconstruction of the raw data coming from the experiments is performed on large computing centres organized into the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing Grid.
+The resulting datasets contain event information and high-level physics objects and are of $\mathcal O(10-100)$~TB in size.
+\todo{move file size numbers to Figure \ref{figure_analysis_steps}?}
 
-This is followed by the selection of data that is relevant for a specific analysis, a step usually  referred to as \textit{skimming}.
-The output of the skimming is a mostly analysis-dependent n-tuple format that is small enough to be stored at local file servers, often owned and operated by a single institute.
+The data which are relevant for a specific analysis are selected in a step usually referred to as \textit{skimming}.
+The output of the skimming is a mostly analysis-dependent file, usually in an n-tuple format, small enough to be stored at local file servers, often owned and operated by a single institute.
 The size of these files ranges from $\mathcal O(10)$~GB to few~TB.
 
-The skimmed n-tuples are finally processed by user code on local resources.
-This means performing further event selection and categorization steps or high-level calculations based on the physics objects.
-The events are usually processed with different configurations depending on the analysis needs.
-The output is then used for post-processing steps including the plotting of results.
+Finally, the skimmed n-tuples are processed by user code running on local resources.
+This processing step includes further event selections, event categorization or high-level calculations based on the selected physics objects.
+The events are usually processed with different configurations, depending from the specific analysis needs.
+The output is then used for post-processing steps, including plotting of the results and their statistical interpretation.
 
-In many cases the code for the last step is developed without a strategy or structure according to the growing needs of the analysis.
-This leads to code that is convoluted, tangled and unstructured.
-Such code is difficult to understand and to maintain and also difficult to hand over to new people joining the analysis effort.
-Also, code is rarely shared among different groups, although basic parts of the analysis like data formats, the processing of n-tuple-structured files or the selection and identification of physics objects follow the same principles.
-The analysis groups usually consist of several people of different academic levels, some joining the analysis effort only for a short time.
-This results in a high user fluctuation and a wide range of programming skills.
+In many cases the code for the last step is developed without a predefined strategy or structure, following the evolving needs of the analysis which are often physics-driven and not always entirely predictable in the code design phase.
+This leads to convoluted, tangled and unstructured code, which is difficult to understand and to maintain and also difficult to hand over to new people joining the analysis effort.
+Also, code is rarely shared among different groups, although the basic parts of an analysis, such as handling of input data having the same formats, their processing and the selection and identification of physics objects follow similar or equivalent specifications.
+Looking at the user side, an analysis group usually consists of several people having different academic levels and different programming skills, some of them joining the analysis effort only for a short period of time and with a well-defined task.
 

### 2015-09-11 HarryPlotter/python/analysis_modules/cutflow.py
cutflow: handle cutflow histograms with different cuts

@@ -10,6 +10,7 @@ log = logging.getLogger(__name__)
 import ROOT
 
 import Artus.HarryPlotter.analysisbase as analysisbase
+import Artus.HarryPlotter.utility.extrafunctions as extrafunctions
 
 
 class Cutflow(analysisbase.AnalysisBase):
@@ -51,3 +52,34 @@ class Cutflow(analysisbase.AnalysisBase):
 				else:
 					root_histogram.Scale(1.0 / root_histogram.GetBinContent(1))
 
+		# get list of filternames (= bin labels) from all cutflow histograms
+		filternames = {}
+		for nick, root_histogram in plotData.plotdict["root_objects"].iteritems():
+			filternames[nick] = []
+			for binnumber in range(1, root_histogram.GetNbinsX()+1):
+				filternames[nick].append(root_histogram.GetXaxis().GetBinLabel(binnumber))
+
+		# check whether number of bins is the same for all cutflow histograms:
+		if len(set( [len(filternames[nick]) for nick in filternames] )) > 1:
+			log.warning("Cutflow histograms have different number of bins! New histograms containing all cuts will be constructed.")
+
+			# construct list containing ALL cuts while preserve ordering
+			allcuts = filternames[plotData.plotdict["root_objects"].keys()[0]]
+			for nick in plotData.plotdict["root_objects"].keys()[1:]:
+				allcuts = extrafunctions.merge_sequences(allcuts, filternames[nick])
+
+			for nick, root_histogram in plotData.plotdict["root_objects"].iteritems():
+				# new histo with bins for all cuts
+				new_histo = ROOT.TH1F(root_histogram.GetName()+"_new", root_histogram.GetTitle()+"_new", len(allcuts), 0, len(allcuts))
+				cut_efficiency = 1.
+				cut_efficiency_error = 0.
+				for index, cut in enumerate(allcuts):
+					# if the cut is available for the current nick, use its efficiceny.
+					# if not, take the efficiency from the last available cut.
+					if cut in filternames[nick]:
+						cut_efficiency = root_histogram.GetBinContent(filternames[nick].index(cut)+1)
+						cut_efficiency_error = root_histogram.GetBinError(filternames[nick].index(cut)+1)
+					new_histo.SetBinContent(index+1, cut_efficiency)
+					new_histo.SetBinError(index+1, cut_efficiency_error)
+					new_histo.GetXaxis().SetBinLabel(index+1, cut)
+				plotData.plotdict["root_objects"][nick] = new_histo

### 2015-09-11 HarryPlotter/python/utility/extrafunctions.py

@@ -10,6 +10,7 @@ log = logging.getLogger(__name__)
 
 import os
 import subprocess
+from difflib import SequenceMatcher
 
 import ROOT
 
@@ -44,3 +45,20 @@ def isfloat(element):
 	except ValueError:
 		return False
 
+
+def merge_sequences(seq1,seq2):
+	"""http://stackoverflow.com/questions/14241320/interleave-different-length-lists-elimating-duplicates-and-preserve-order-in-py"""
+	sm=SequenceMatcher(a=seq1,b=seq2)
+	res = []
+	for (op, start1, end1, start2, end2) in sm.get_opcodes():
+		if op == 'equal' or op=='delete':
+			#This range appears in both sequences, or only in the first one.
+			res += seq1[start1:end1]
+		elif op == 'insert':
+			#This range appears in only the second sequence.
+			res += seq2[start2:end2]
+		elif op == 'replace':
+			#There are different ranges in each sequence - add both.
+			res += seq1[start1:end1]
+			res += seq2[start2:end2]
+	return res

### 2015-09-11 HarryPlotter/python/analysis_modules/cutflow.py
fix for previous commit

@@ -79,6 +79,8 @@ class Cutflow(analysisbase.AnalysisBase):
 					if cut in filternames[nick]:
 						cut_efficiency = root_histogram.GetBinContent(filternames[nick].index(cut)+1)
 						cut_efficiency_error = root_histogram.GetBinError(filternames[nick].index(cut)+1)
+					elif plotData.plotdict["rel_cuts"]:
+						cut_efficiency = 1.
 					new_histo.SetBinContent(index+1, cut_efficiency)
 					new_histo.SetBinError(index+1, cut_efficiency_error)
 					new_histo.GetXaxis().SetBinLabel(index+1, cut)

### 2015-09-11 HarryPlotter/python/plot_modules/plotmpl.py
plotmpl.py: increase distance between subplots to avoid clashing y-axis ticklabels

@@ -210,7 +210,7 @@ class PlotMpl(plotbase.PlotBase):
 		axes = []
 		if plotData.plotdict["subplot_nicks"]:
 			axes = [plt.subplot2grid((100,1), (0, 0), rowspan=(100-plotData.plotdict["subplot_fraction"])),
-			        plt.subplot2grid((100,1), ((100-plotData.plotdict["subplot_fraction"]+1), 0), rowspan=plotData.plotdict["subplot_fraction"])]
+			        plt.subplot2grid((100,1), ((100-plotData.plotdict["subplot_fraction"]+4), 0), rowspan=plotData.plotdict["subplot_fraction"])]
 		else:
 			kwargs = {'projection':'3d'} if (plotData.plotdict['3d'] is not False) else {}
 			axes = [fig.add_subplot(1,1,1, **kwargs)]

### 2015-09-11 KappaAnalysis/interface/Producers/ValidJetsProducer.h
Update jet ID to recent 2015 values

@@ -52,6 +52,8 @@ public:
 		             // first run 2 version identical to run 1 legacy version
 		ID73X = 3,   // new run 2 version identical to ID2014 but change in cmssw 7.3.x fraction definitions
 		ID73Xtemp = 4, // temporary recommendation for first run 2 events due to ID problems in the forward region
+		ID73XnoHF = 5, // as temp but invalidate forward jets
+		ID2015 = 6,  // new jet ID for run 2 updated on 2015-09-11
 	};
 
 	static ValidJetsInput ToValidJetsInput(std::string const& validJetsInput)
@@ -65,9 +67,11 @@ public:
 		if (jetIDVersion == "2010") return JetIDVersion::ID2010;
 		else if (jetIDVersion == "2014") return JetIDVersion::ID2014;
 		else if (jetIDVersion == "73x") return JetIDVersion::ID73X;
-		else if (jetIDVersion == "73xtemp") return JetIDVersion::ID73X;
+		else if (jetIDVersion == "73xtemp") return JetIDVersion::ID73Xtemp;
+		else if (jetIDVersion == "73xnohf") return JetIDVersion::ID73XnoHF;
+		else if (jetIDVersion == "2015") return JetIDVersion::ID2015;
 		else LOG(FATAL) << "Jet ID version '" << jetIDVersion << "' is not available";
-		return JetIDVersion::ID73X;
+		return JetIDVersion::ID2015;
 	}
 
 	ValidJetsProducerBase(std::vector<TJet>* KappaEvent::*jets,
@@ -94,11 +98,13 @@ public:
 		noID = (jetID == "none");
 		if (jetID == "medium" && jetIDVersion != JetIDVersion::ID2010)
 			LOG(WARNING) << "Since 2012, the medium jet ID is not supported officially any longer.";
-		if (!noID && jetIDVersion != JetIDVersion::ID73X)
+		if (!noID && (jetIDVersion == JetIDVersion::ID2010 || jetIDVersion == JetIDVersion::ID2014))
 			LOG(WARNING) << "This jet ID version is not valid for 73X samples.";
 
+		maxMuFraction = 1.0f;
+		maxCEMFraction = 0.99f;
 		maxFraction = 1.0f;
-		if (jetID == "tight")
+		if (jetID == "tight" || jetID == "tightlepveto")
 			maxFraction = 0.90f;
 		else if (jetID ==  "medium")
[…]

### 2015-09-15 HarryPlotter/python/plotdata.py
Improved webplotting: one gallery entry for multiple formats (non controversial)

@@ -59,16 +59,13 @@ class PlotData(object):
 			if self.plotdict["www"] != None:
 				# set some needed variables
 				user = tools.get_environment_variable("HARRY_REMOTE_USER")
+				html_content = ""
 				overview_filename = 'overview.html'
 				date = datetime.date.today().strftime('%Y_%m_%d')
 				remote_dir = os.path.expandvars(os.path.join("$HARRY_REMOTE_DIR", date, (self.plotdict["www"] if type(self.plotdict["www"])==str else "")))
 				remote_path = os.path.expandvars(os.path.join("$HARRY_REMOTE_PATH", remote_dir))
 				url = os.path.expandvars(os.path.join("$HARRY_URL", remote_dir, overview_filename))
-				
 				plots_for_gallery = [p for p in sorted(os.listdir(self.plotdict["output_dir"])) if (os.path.isfile(os.path.join(self.plotdict["output_dir"], p)) and all([not p.endswith("."+ext) for ext in ["json", "html", "root"]]))]
-				html_content = ""
-
-				log.info("Copying plots to webspace...")
 
 				# get the html templates
 				html_texts = {}
@@ -79,19 +76,24 @@ class PlotData(object):
 				if self.plotdict["www_text"]:
 					html_texts['description'] = self.plotdict["www_text"]
 
-				# loop over plots, make gallery
-				for plot in [p for p in plots_for_gallery]:
-					# try to link to pdf file, if it exists
-					href = plot.replace('.png', '.pdf')
-					if href not in plots_for_gallery:
-						href = plot
-					filename = os.path.splitext(plot)[0]
+				# loop over plots, make gallery (one entry for multiple formats)
+				for plot in list(set([os.path.splitext(plot)[0] for plot in plots_for_gallery])):
+					formats = [os.path.splitext(p)[1] for p in plots_for_gallery if (plot == os.path.splitext(p)[0])]
+					# use png for preview, if it exists
+					image = plot + ('.png' if (plot +'.png' in plots_for_gallery) else formats[0])
+
+					# links for the different formats
+					links = ""
+					for fileformat in formats:
+						links +=' <a href="{}">{}</a>'.format(plot+fileformat, fileformat[1:])
+
 					html_content += html_texts['plot'].substitute(
-							title=filename,
-							href=href,
-							plot=plot,
+							title=plot,
+							image=image,
+							links=links,
 							json=filename+".json"
 					)
+
[…]

### 2015-09-15 HarryPlotter/python/plotdata.py
fix non-controversial commit

@@ -77,7 +77,7 @@ class PlotData(object):
 					html_texts['description'] = self.plotdict["www_text"]
 
 				# loop over plots, make gallery (one entry for multiple formats)
-				for plot in list(set([os.path.splitext(plot)[0] for plot in plots_for_gallery])):
+				for plot in sorted(list(set([os.path.splitext(plot)[0] for plot in plots_for_gallery]))):
 					formats = [os.path.splitext(p)[1] for p in plots_for_gallery if (plot == os.path.splitext(p)[0])]
 					# use png for preview, if it exists
 					image = plot + ('.png' if (plot +'.png' in plots_for_gallery) else formats[0])

### 2015-09-15 HarryPlotter/python/analysis_modules/cutflow.py
cutflow.py: dont set y-lims

@@ -32,9 +32,6 @@ class Cutflow(analysisbase.AnalysisBase):
 			plotData.plotdict["x_label"] = ""
 		if plotData.plotdict["y_label"] == parser.get_default("y_label"):
 			plotData.plotdict["y_label"] = ("Relative " if plotData.plotdict["rel_cuts"] else "") + "Cut Efficiency"
-		
-		if plotData.plotdict["y_lims"] == parser.get_default("y_lims"):
-			plotData.plotdict["y_lims"] = [1e-5, 1.5] if plotData.plotdict["y_log"] else [0.0, 1.1]
 	
 	def run(self, plotData=None):
 		super(Cutflow, self).run(plotData)

### 2015-09-16 HarryPlotter/python/plotdata.py
plotdata.py: enable web copying of additional files via 'additional_output_files' key in plotdict

@@ -107,6 +107,8 @@ class PlotData(object):
 					self.plotdict["output_filenames"]
 					+ [os.path.join(self.plotdict["output_dir"], overview_filename)]
 				)
+				if "additional_output_files" in self.plotdict:
+					files_to_copy += self.plotdict["additional_output_files"]
 				if self.plotdict["export_json"]:
 					files_to_copy += [self.plotdict["export_json"]]
 				if self.plotdict.get("save_legend", False):

### 2015-09-16 HarryPlotter/python/plot_modules/plotmpllegendtable.py
plotmpllegendtable.py: post-plot module to save MPL legend entries in tabular legend

@@ -1,0 +1,90 @@
+# -*- coding: utf-8 -*-
+
+"""
+	Plot the legend in tabular format in extra file.
+
+	Basic usage: harry.py HARRY-ARGS --plot-modules PlotMpl PlotMplLegendTable --legend-table-column-headers a b --legend-table-row-headers 1 2 3
+"""
+
+import numpy as np
+import os
+from matplotlib.patches import Rectangle
+import matplotlib.pyplot as plt
+
+import Artus.HarryPlotter.plotbase as plotbase
+from Artus.HarryPlotter.plot_modules.plotmpl import PlotMpl
+
+
+class PlotMplLegendTable(plotbase.PlotBase):
+
+	def modify_argument_parser(self, parser, args):
+		super(PlotMplLegendTable, self).modify_argument_parser(parser, args)
+		self.legendtable_options = parser.add_argument_group(title="{} options".format(self.name()), description="legend table")
+		self.legendtable_options.add_argument("--legend-table-column-headers", nargs="*", type=str,
+		                                     help="Names of the column headers")
+		self.legendtable_options.add_argument("--legend-table-row-headers", nargs="*", type=str,
+		                                     help="Names of the row headers")
+		self.legendtable_options.add_argument("--legend-table-invert", action="store_true",
+		                                     help="Invert legend handle columns/rows")
+		self.legendtable_options.add_argument("--legend-table-filename", type=str, default='legend_table',
+		                                     help="Filename for the legend table. [Default: %(default)s]")
+
+	def run(self, plotData):
+
+		fig = plt.figure(figsize=(1,1))
+		ax = fig.add_subplot(111, frameon=False)
+		ax.xaxis.set_visible(False)
+		ax.yaxis.set_visible(False)
+
+		column_headers = plotData.plotdict['legend_table_column_headers']
+		row_headers = plotData.plotdict['legend_table_row_headers']
+
+		n_columns = len(column_headers)
+		n_rows = len(row_headers)
+		# blank rectangle as handle for index column/row
+		rectangle = Rectangle((0, 0), 1, 1, fc="w", fill=False, edgecolor='none', linewidth=0)
+
+		labels = plotData.plot.labels
+		# switch rows and colum handles:
+		if plotData.plotdict['legend_table_invert']:
+			inverted_labels = []
+			for i_column in range(n_columns):
[…]

### 2015-09-16 Configuration/scripts/ini_ArtusAnalysis.sh
Collected adaptations and extensions for the embedding tests

@@ -24,7 +24,7 @@ export USERPC=`who am i | sed 's/.*(\([^]]*\)).*/\1/g'`
 if [[ `hostname` == *naf* ]]; then
 	export ARTUS_WORK_BASE="/nfs/dust/cms/user/${USER}/artus/"
 elif [[ `hostname` == *ekp* ]]; then
-	export ARTUS_WORK_BASE="/storage/a/${USER}/artus/"
+	export ARTUS_WORK_BASE="/storage/6/${USER}/artus/"
 elif [[ `hostname` == *cern* ]]; then
 	export ARTUS_WORK_BASE="/afs/cern.ch/work/${USER:0:1}/${USER}/artus/"
 fi

### 2015-09-16 KappaAnalysis/interface/Consumers/KappaCollectionsConsumers.h

@@ -6,10 +6,12 @@
 #include "Artus/Utility/interface/RootFileHelper.h"
 #include "Artus/Utility/interface/SafeMap.h"
 #include "Artus/KappaAnalysis/interface/KappaTypes.h"
-
+#include "TLorentzVector.h"
 
 /**
    \brief KappaCollectionsConsumer, create an TTree with one entry for each valid (Kappa) object.
+=======
+>>>>>>> Stashed changes
 
    This producer creates an ntuple with all data members of the Kappa object as variables.
    Additionally, a matching to gen particles is possible.
@@ -36,6 +38,8 @@ public:
 	KappaCollectionsConsumerBase(std::string treeName,
 	                             std::vector<TObject*> product_type::*validObjects,
 	                             bool (setting_type::*GetBranchGenMatchedObjects)(void) const,
+								 bool (setting_type::*GetBranchObjectMatchedPF)(void) const,
+	                             bool (setting_type::*GetBranchObjectMatchedPFEtsum)(void) const,
 	                             TObjectMetaInfo* event_type::*objectMetaInfo = nullptr,
 	                             std::map<TObject*, KGenParticle*> product_type::*genParticleMatchedObjects = nullptr,
 	                             std::map<TObject*, KGenTau*> product_type::*genTauMatchedObjects = nullptr,
@@ -44,6 +48,8 @@ public:
 		m_treeName(treeName),
 		m_validObjects(validObjects),
 		GetBranchGenMatchedObjects(GetBranchGenMatchedObjects),
+		GetBranchObjectMatchedPF(GetBranchObjectMatchedPF),
+		GetBranchObjectMatchedPFEtsum(GetBranchObjectMatchedPFEtsum),
 		m_objectMetaInfo(objectMetaInfo),
 		m_objectMetaInfoAvailable(objectMetaInfo != nullptr),
 		m_genParticleMatchedObjects(genParticleMatchedObjects),
@@ -92,11 +98,69 @@ public:
[…]

### 2015-09-16 KappaAnalysis/interface/Consumers/KappaLambdaNtupleConsumer.h

@@ -47,7 +47,6 @@ public:
 		{
 			return event.m_vertexSummary->nVertices;
 		});
-
 		bool bInpData = settings.GetInputIsData();
 		LambdaNtupleConsumer<TTypes>::AddFloatQuantity("npuMean", [bInpData](event_type const& event, product_type const& product)
 		{
@@ -63,6 +62,12 @@ public:
 			return static_cast<int>(static_cast<KGenEventInfo*>(event.m_eventInfo)->nPU);
 		});
 
+		LambdaNtupleConsumer<TTypes>::AddIntQuantity("ootPU", [](event_type const& event, product_type const& product)
+		{
+			return static_cast<KGenEventInfo*>(event.m_eventInfo)->nPUm1 +
+				static_cast<KGenEventInfo*>(event.m_eventInfo)->nPUp1;
+		});
+		
 		LambdaNtupleConsumer<TTypes>::AddFloatQuantity("rho", [](event_type const& event, product_type const& product) {
 			return event.m_pileupDensity->rho;
 		});

### 2015-09-16 KappaAnalysis/interface/Filters/ValidLeptonsMinDeltaRFilter.h

@@ -48,7 +48,7 @@ public:
 						deltaRMatched = ROOT::Math::VectorUtil::DeltaR((*validObject1)->p4, (*validObject2)->p4);
 						if (deltaRMatched < (settings.*GetMinDeltaRValidLeptons)())
 						{
-							//std::cout << "Deleting event with DeltaR between particles of " << deltaRMatched << std::endl;
+							//std::cout << "Deleting event with DeltaR of " << deltaRMatched << " between particles with masses " << (*validObject1)->p4.M() << " and " << (*validObject2)->p4.M() << std::endl;
 							return false;
 						}
 					}

### 2015-09-16 KappaAnalysis/interface/KappaEvent.h

@@ -54,6 +54,8 @@ public:
 	KPFCandidates* m_pfChargedHadronsNoPileUp = nullptr;
 	KPFCandidates* m_pfNeutralHadronsNoPileUp = nullptr;
 	KPFCandidates* m_pfPhotonsNoPileUp = nullptr;
+	KPFCandidates* m_pfAllChargedParticlesNoPileUp = nullptr;
+	KPFCandidates* m_pfAllChargedParticlesPileUp = nullptr;
 
 	/// pointer to beamspot collection
 	KBeamSpot* m_beamSpot = nullptr;

### 2015-09-16 KappaAnalysis/interface/KappaEventProvider.h

@@ -66,6 +66,10 @@ public:
 			this->m_event.m_pfChargedHadronsPileUp = this->template SecureFileInterfaceGet<KPFCandidates>(settings.GetPFChargedHadronsPileUp());
 		if (! settings.GetPFChargedHadronsNoPileUp().empty())
 			this->m_event.m_pfChargedHadronsNoPileUp = this->template SecureFileInterfaceGet<KPFCandidates>(settings.GetPFChargedHadronsNoPileUp());
+		if (! settings.GetPFAllChargedParticlesNoPileUp().empty())
+			this->m_event.m_pfAllChargedParticlesNoPileUp = this->template SecureFileInterfaceGet<KPFCandidates>(settings.GetPFAllChargedParticlesNoPileUp());
+		if (! settings.GetPFAllChargedParticlesPileUp().empty())
+			this->m_event.m_pfAllChargedParticlesPileUp = this->template SecureFileInterfaceGet<KPFCandidates>(settings.GetPFAllChargedParticlesPileUp());
 		if (! settings.GetPFNeutralHadronsNoPileUp().empty())
 			this->m_event.m_pfNeutralHadronsNoPileUp = this->template SecureFileInterfaceGet<KPFCandidates>(settings.GetPFNeutralHadronsNoPileUp());
 		if (! settings.GetPFPhotonsNoPileUp().empty())

### 2015-09-16 KappaAnalysis/interface/KappaProduct.h

@@ -60,6 +60,10 @@ public:
 	/// added by ValidMuonsProducer
 	std::vector<KMuon*> m_validMuons;
 	std::vector<KMuon*> m_invalidMuons;
+	
+	/// added by MuonFSRProducer	
+	std::vector<double> m_sumMuonFSRPt;
+	std::vector<double> m_MuonPt;
 
 	/// added by TauEnergyCorrectionProducer
 	// needs to be a shared_ptr in order to be deleted when the product is deleted
@@ -139,6 +143,9 @@ public:
 	std::map<KElectron*, KGenJet*> m_genTauJetMatchedElectrons;
 	std::map<KMuon*, KGenJet*> m_genTauJetMatchedMuons;
 	std::map<KTau*, KGenJet*> m_genTauJetMatchedTaus;
+	
+	//std::map<KMuon*, KPFCandidates*> m_pfChargedHadronsPileUp;
+	//std::map<KMuon*, std::vector<KPFCandidates*> > m_pfChargedHadronsPileUp;
 	
 	// MVA outputs
 	std::vector<double> m_discriminators;

### 2015-09-16 KappaAnalysis/interface/KappaSettings.h

@@ -54,6 +54,8 @@ public:
 	IMPL_SETTING_DEFAULT(std::string, PFChargedHadronsNoPileUp, "");
 	IMPL_SETTING_DEFAULT(std::string, PFNeutralHadronsNoPileUp, "");
 	IMPL_SETTING_DEFAULT(std::string, PFPhotonsNoPileUp, "");
+	IMPL_SETTING_DEFAULT(std::string, PFAllChargedParticlesNoPileUp, "");
+	IMPL_SETTING_DEFAULT(std::string, PFAllChargedParticlesPileUp, "");
 
 	/// name of beamspot collection in kappa tuple
 	IMPL_SETTING_DEFAULT(std::string, BeamSpot, "");
@@ -314,4 +316,6 @@ public:
 	IMPL_SETTING_DEFAULT(bool, AddGenMatchedTaus, true)
 	IMPL_SETTING_DEFAULT(bool, AddGenMatchedTauJets, true)
 
+	IMPL_SETTING_DEFAULT(bool, BranchObjectMatchedPF, false);
+	IMPL_SETTING_DEFAULT(bool, BranchObjectMatchedPFEtsum, false);
 };

### 2015-09-16 KappaAnalysis/interface/Producers/GenMuonFSRProducer.h

@@ -1,0 +1,38 @@
+
+#pragma once
+
+#include <Math/VectorUtil.h>
+
+#include "Kappa/DataFormats/interface/Kappa.h"
+
+#include "Artus/KappaAnalysis/interface/KappaProducerBase.h"
+#include "Artus/Utility/interface/SafeMap.h"
+#include "Artus/KappaAnalysis/interface/Consumers/KappaLambdaNtupleConsumer.h"
+
+
+/**
+   \brief GlobalProducer to write out genLevel muon FSR information to matched muons
+
+   Run after ValidMuonProducer and GenParticleProducer
+   Steps of the producer
+   1. genMatching to find genMuons that match a reconstructed muon
+   2. find the FSR emitted by the genMuon
+   3. write out the genMuonFSR to a new quantity genMuonFSR
+*/
+
+class GenMuonFSRProducer: public KappaProducerBase
+{
+public:
+
+	virtual std::string GetProducerId() const ARTUS_CPP11_OVERRIDE;
+
+	virtual void Init(KappaSettings const& settings) ARTUS_CPP11_OVERRIDE;
+ 
+	virtual void Produce(KappaEvent const& event, KappaProduct& product,
+	                     KappaSettings const& settings) const ARTUS_CPP11_OVERRIDE;
+	
+
+private:
+
+};
+

### 2015-09-16 KappaAnalysis/interface/Producers/GenTauMatchingProducers.h

@@ -41,6 +41,8 @@ public:
 		m_genTauMatchedObjects(genTauMatchedObjects),
 		m_validObjects(validObjects),
 		m_invalidObjects(invalidObjects),
+		//m_validObjects(validObjects),
+		//m_validObjects(validObjects),
 		tauDecayMode(tauDecayMode),
 		GetDeltaRMatchingRecoObjectGenTau(GetDeltaRMatchingRecoObjectGenTau),
 		GetInvalidateNonGenTauMatchingObjects(GetInvalidateNonGenTauMatchingObjects),
@@ -59,6 +61,14 @@ public:
 		{
 			return product.m_genTauMatchDeltaR;
 		});
+		//MuonsConsumer<KappaTypes>::AddFloatQuantity("genTauMatchedMuonsDeltaR", [](event_type const & event, product_type const & product)
+		//{
+		//	return product.m_genTauMatchDeltaR;
+		//});
+		//LambdaNtupleConsumer<KappaTypes>::AddFloatQuantity("genTauMatchedTausDeltaR", [](event_type const & event, product_type const & product)
+		//{
+		//	return product.m_genTauMatchDeltaR;
+		//});
 	}
 
 	virtual void Produce(event_type const& event, product_type& product,
@@ -76,12 +86,10 @@ public:
 			{
 				bool objectMatched = false;
 				float deltaR = 0;
-				
 				// loop over all genTaus
 				for (typename std::vector<KGenTau>::iterator genTau = event.m_genTaus->begin();
 					 !objectMatched && genTau != event.m_genTaus->end();++genTau) 
 				{
-					// only use genTaus that will decay into comparable particles
 					if (MatchDecayMode(*genTau,tauDecayMode))
 					{
 						deltaR = static_cast<float>(ROOT::Math::VectorUtil::DeltaR((*validObject)->p4, genTau->visible.p4));
@@ -122,6 +130,31 @@ public:
 			product.m_genTauMatchDeltaR = DefaultValues::UndefinedFloat;
 		}
 		product.m_ratioGenTauMatched = ratioGenTauMatched;
+		//std::cout << "Output Map Lenght: " << (product.*m_genTauMatchedObjects).size() << std::endl;
+		//check distance of previously matched particles
+		//print if smaller 1 (.5)
+		//if ((product.*m_genTauMatchedObjects).size() >= 2)
+		//{
+		//	float deltaRMatched = 0;
+		//	int matchid1 = 0;
[…]

### 2015-09-16 KappaAnalysis/interface/Producers/ValidMuonsProducer.h

@@ -192,6 +192,261 @@ public:
 			}
 			return DefaultValues::UndefinedFloat;
 		});
+		LambdaNtupleConsumer<TTypes>::AddIntQuantity("mirrortest06", [](event_type const& event, product_type const& product) {
+			if (product.m_validMuons.size() == 2)
+			{
+				double cut = 0.6;
+				ROOT::Math::LorentzVector<ROOT::Math::PtEtaPhiM4D<float> > origmu0(product.m_validMuons[0]->p4.Pt(),product.m_validMuons[0]->p4.Eta(),-1.*product.m_validMuons[0]->p4.Phi(),product.m_validMuons[0]->p4.M());
+				
+				ROOT::Math::LorentzVector<ROOT::Math::PtEtaPhiM4D<float> > origmu1(product.m_validMuons[1]->p4.Pt(),product.m_validMuons[1]->p4.Eta(),-1.*product.m_validMuons[1]->p4.Phi(),product.m_validMuons[1]->p4.M());
+				
+				double deltaR1 = ROOT::Math::VectorUtil::DeltaR(origmu0, product.m_validMuons[1]->p4);
+				double deltaR2 = ROOT::Math::VectorUtil::DeltaR(origmu1, product.m_validMuons[0]->p4);
+				//Check Mu 0 was not mirrored in original Mu 1
+				if ( (deltaR1 < cut) or (deltaR2 < cut))
+					return 0;
+				else
+					return 1;
+			}	
+			return DefaultValues::UndefinedInt;
+		});
+		LambdaNtupleConsumer<TTypes>::AddIntQuantity("mirrortest05", [](event_type const& event, product_type const& product) {
+			if (product.m_validMuons.size() == 2)
+			{
+				double cut = 0.5;
+				ROOT::Math::LorentzVector<ROOT::Math::PtEtaPhiM4D<float> > origmu0(product.m_validMuons[0]->p4.Pt(),product.m_validMuons[0]->p4.Eta(),-1.*product.m_validMuons[0]->p4.Phi(),product.m_validMuons[0]->p4.M());
+				
+				ROOT::Math::LorentzVector<ROOT::Math::PtEtaPhiM4D<float> > origmu1(product.m_validMuons[1]->p4.Pt(),product.m_validMuons[1]->p4.Eta(),-1.*product.m_validMuons[1]->p4.Phi(),product.m_validMuons[1]->p4.M());
+				
[…]

### 2015-09-16 KappaAnalysis/interface/Producers/ValidTausProducer.h

@@ -98,6 +98,50 @@ public:
 		LambdaNtupleConsumer<KappaTypes>::AddFloatQuantity("trailingTauEta", [](KappaEvent const& event, KappaProduct const& product) {
 			return product.m_validTaus.size() >= 2 ? product.m_validTaus[1]->p4.Eta() : DefaultValues::UndefinedFloat;
 		});
+		LambdaNtupleConsumer<KappaTypes>::AddFloatQuantity("tau0_hpsPFTauDiscriminationByRawChargedIsolationDBSumPtCorr", [](KappaEvent const& event, KappaProduct const& product) {
+			return product.m_validTaus.size() >= 1 ? product.m_validTaus[0]->getDiscriminator("hpsPFTauDiscriminationByRawChargedIsolationDBSumPtCorr", event.m_tauMetadata) : DefaultValues::UndefinedDouble;
+		});
+		LambdaNtupleConsumer<KappaTypes>::AddFloatQuantity("tau1__hpsPFTauDiscriminationByRawChargedIsolationDBSumPtCorr", [](KappaEvent const& event, KappaProduct const& product) {
+			return product.m_validTaus.size() >= 2 ? product.m_validTaus[1]->getDiscriminator("hpsPFTauDiscriminationByRawChargedIsolationDBSumPtCorr", event.m_tauMetadata) : DefaultValues::UndefinedDouble;
+		});
+		LambdaNtupleConsumer<KappaTypes>::AddFloatQuantity("tau0_hpsPFTauDiscriminationByRawCombinedIsolationDBSumPtCorr", [](KappaEvent const& event, KappaProduct const& product) {
+			return product.m_validTaus.size() >= 1 ? product.m_validTaus[0]->getDiscriminator("hpsPFTauDiscriminationByRawCombinedIsolationDBSumPtCorr", event.m_tauMetadata) : DefaultValues::UndefinedDouble;
+		});
+		LambdaNtupleConsumer<KappaTypes>::AddFloatQuantity("tau1__hpsPFTauDiscriminationByRawCombinedIsolationDBSumPtCorr", [](KappaEvent const& event, KappaProduct const& product) {
+			return product.m_validTaus.size() >= 2 ? product.m_validTaus[1]->getDiscriminator("hpsPFTauDiscriminationByRawCombinedIsolationDBSumPtCorr", event.m_tauMetadata) : DefaultValues::UndefinedDouble;
+		});
[…]

### 2015-09-16 KappaAnalysis/src/Consumers/KappaCollectionsConsumers.cc

@@ -6,6 +6,7 @@ KappaElectronsConsumer::KappaElectronsConsumer() :
 	                             &product_type::m_validElectrons,
 	                             &setting_type::GetBranchGenMatchedElectrons,
 								 &setting_type::GetBranchObjectMatchedPF,
+								 &setting_type::GetBranchObjectMatchedPFEtsum,
 	                             nullptr,
 	                             &product_type::m_genParticleMatchedElectrons,
 	                             &product_type::m_genTauMatchedElectrons,
@@ -25,6 +26,7 @@ KappaMuonsConsumer::KappaMuonsConsumer() :
 	                             &product_type::m_validMuons,
 	                             &setting_type::GetBranchGenMatchedMuons,
 								 &setting_type::GetBranchObjectMatchedPF,
+ 			 					 &setting_type::GetBranchObjectMatchedPFEtsum,
 	                             nullptr,
 	                             &product_type::m_genParticleMatchedMuons,
 	                             &product_type::m_genTauMatchedMuons,
@@ -45,6 +47,7 @@ KappaTausConsumer::KappaTausConsumer() :
 	                             &product_type::m_validTaus,
 	                             &setting_type::GetBranchGenMatchedTaus,
 								 &setting_type::GetBranchObjectMatchedPF,
+								 &setting_type::GetBranchObjectMatchedPFEtsum,
 	                             &event_type::m_tauMetadata,
 	                             &product_type::m_genParticleMatchedTaus,
 	                             &product_type::m_genTauMatchedTaus,
@@ -64,6 +67,7 @@ KappaJetsConsumer::KappaJetsConsumer() :
 	                             &product_type::m_validJets,
 	                             &setting_type::GetBranchGenMatchedJets,
 	                             &setting_type::GetBranchObjectMatchedPF,
+	                             &setting_type::GetBranchObjectMatchedPFEtsum,
 	                             nullptr,
 	                             &product_type::m_genParticleMatchedJets,
 	                             nullptr,
@@ -83,6 +87,7 @@ KappaTaggedJetsConsumer::KappaTaggedJetsConsumer() :
 	                             &product_type::m_validJets,
 	                             &setting_type::GetBranchGenMatchedJets,
 	                             &setting_type::GetBranchObjectMatchedPF,
+	                             &setting_type::GetBranchObjectMatchedPFEtsum,
 	                             &event_type::m_jetMetadata,
 	                             &product_type::m_genParticleMatchedJets,
 	                             nullptr,

### 2015-09-16 KappaAnalysis/src/KappaFactory.cc

@@ -6,6 +6,7 @@
 #include "Artus/KappaAnalysis/interface/Producers/GenTauDecayProducer.h"
 #include "Artus/KappaAnalysis/interface/Producers/GenTauDecayModeProducer.h"
 #include "Artus/KappaAnalysis/interface/Producers/GenParticleProducer.h"
+#include "Artus/KappaAnalysis/interface/Producers/GenMuonFSRProducer.h"
 #include "Artus/KappaAnalysis/interface/Producers/ElectronCorrectionsProducer.h"
 #include "Artus/KappaAnalysis/interface/Producers/MuonCorrectionsProducer.h"
 #include "Artus/KappaAnalysis/interface/Producers/TauCorrectionsProducer.h"
@@ -32,6 +33,7 @@
 #include "Artus/KappaAnalysis/interface/Producers/NicknameProducer.h"
 #include "Artus/KappaAnalysis/interface/Producers/GenTauMatchingProducers.h"
 #include "Artus/KappaAnalysis/interface/Producers/GenTauJetMatchingProducers.h"
+#include "Artus/KappaAnalysis/interface/Producers/PFCandidatesProducer.h"
 
 // filter
 #include "Artus/KappaAnalysis/interface/Filters/RunLumiEventFilter.h"
@@ -71,6 +73,8 @@ ProducerBaseUntemplated * KappaFactory::createProducer ( std::string const& id )
   		return new GenTauDecayModeProducer();
 	else if(id == GenParticleProducer().GetProducerId())
   		return new GenParticleProducer();
+	else if(id == GenMuonFSRProducer().GetProducerId())
+  		return new GenMuonFSRProducer();
 	else if(id == HltProducer().GetProducerId())
 		return new HltProducer();
 	else if(id == ElectronCorrectionsProducer().GetProducerId())
@@ -150,6 +154,8 @@ ProducerBaseUntemplated * KappaFactory::createProducer ( std::string const& id )
 		return new RecoMuonGenTauJetMatchingProducer();
 	else if(id == RecoTauGenTauJetMatchingProducer().GetProducerId())
 		return new RecoTauGenTauJetMatchingProducer();
+	else if(id == PFCandidatesProducer().GetProducerId())
+		return new PFCandidatesProducer();
 	else
 		return FactoryBase::createProducer( id );	
 }

### 2015-09-16 KappaAnalysis/src/Producers/GenMuonFSRProducer.cc

@@ -1,0 +1,63 @@
+
+#include "Artus/KappaAnalysis/interface/Producers/GenMuonFSRProducer.h"
+
+
+std::string GenMuonFSRProducer::GetProducerId() const{
+	return "GenMuonFSRProducer";
+}
+
+void GenMuonFSRProducer::Init(KappaSettings const& settings)
+{
+	KappaProducerBase::Init(settings);
+	
+	LambdaNtupleConsumer<KappaTypes>::AddFloatQuantity("leadingMuonFSR", [](event_type const& event, product_type const& product)
+	{
+		return product.m_sumMuonFSRPt[0];
+	});
+	LambdaNtupleConsumer<KappaTypes>::AddFloatQuantity("trailingMuonFSR", [](event_type const& event, product_type const& product)
+	{
+		return product.m_sumMuonFSRPt[1];
+	});
+}
+
+void GenMuonFSRProducer::Produce(KappaEvent const& event, KappaProduct& product,
+                     KappaSettings const& settings) const
+{
+	// start with empty vector	
+	product.m_sumMuonFSRPt.clear();
+	
+	//Loop through all valid Muons
+	for (typename std::vector<KMuon*>::const_iterator validMuon = product.m_validMuons.begin();
+	     validMuon != product.m_validMuons.end(); ++validMuon)
+	{
+		//Look for matched genMuon
+		KGenParticle* currentGenParticle = SafeMap::GetWithDefault((product.m_genParticleMatchedMuons), *validMuon, (KGenParticle*)(0));
+		float sumMuonFSRPt = 0;
+		//for ordered readout
+		//double muonPt = (*validMuon)->p4.Pt();
+		if (currentGenParticle != 0)
+		{
+			//if 2 daughters: FSR radiation -> add pt to sumMuonFSRPt
+			if (currentGenParticle->nDaughters() == 2 and abs(currentGenParticle->pdgId())==13)
+			{
+				//first daughter: Muon itself
+				//second daughter: Photon
+				if (event.m_genParticles->at(currentGenParticle->daughterIndex(1)).pdgId() == 22)
+				{
+					sumMuonFSRPt += event.m_genParticles->at(currentGenParticle->daughterIndex(1)).p4.Pt();
+				}
+				currentGenParticle = &(event.m_genParticles->at(currentGenParticle->daughterIndex(0)));
+			}
+		}
[…]

### 2015-09-16 KappaAnalysis/interface/Producers/PFCandidatesProducer.h
Added PFCandidates Producer

@@ -1,0 +1,36 @@
+
+#pragma once
+
+#include "Artus/KappaAnalysis/interface/KappaProducerBase.h"
+
+
+/**
+   \brief PFCandidatesProducer (can only run locally)
+   Config tags:
+   - EventWeight, e.g. "eventWeight"
+   
+   Multiplies all entries in the map product.m_weights
+   and writes the result to product.m_weights[settings.GetEventWeight()]
+   
+   By adding the weight quantity names to the Quantity config setting,
+   they will be individually written to the ntuple by the LambdaNtupleConsumer
+*/
+
+class PFCandidatesProducer: public KappaProducerBase {
+public:
+
+	virtual std::string GetProducerId() const ARTUS_CPP11_OVERRIDE;
+	
+	~PFCandidatesProducer();
+	
+	virtual void Init(KappaSettings const& settings) ARTUS_CPP11_OVERRIDE;
+	
+	virtual void Produce(KappaEvent const& event, KappaProduct& product,
+	                     KappaSettings const& settings) const ARTUS_CPP11_OVERRIDE;
+
+
+private:
+	std::string pipelineName;
+	mutable std::vector<std::string> m_weightNames;
+};
+

### 2015-09-20 HarryPlotter/python/analysis_modules/binerrorsofemptybins.py
binerrorsofemptybins.py: some fixes

@@ -7,10 +7,13 @@ import logging
 import Artus.Utility.logger as logger
 log = logging.getLogger(__name__)
 
+import ROOT
+
 import Artus.HarryPlotter.analysis_modules.histogrammanipulationbase as histogrammanipulationbase
 
+
 class BinErrorsOfEmptyBins(histogrammanipulationbase.HistogramManipulationBase):
-	"""Missing Documentation"""
+	"""Set bin errors of empty bins to scale factor * sum of weights / entries of histogram."""
 	
 	def modify_argument_parser(self, parser, args):
 		super(BinErrorsOfEmptyBins, self).modify_argument_parser(parser, args)
@@ -18,12 +21,19 @@ class BinErrorsOfEmptyBins(histogrammanipulationbase.HistogramManipulationBase):
 		self.empty_bins_options = parser.add_argument_group("Empty bins errors options")
 		self.empty_bins_options.add_argument("--empty-bin-error-scale", type=float, default=0.6,
 				help="Scale factor for bin errors of empty bins = sf * sum of weights / entries of histogram. [Default: %(default)s]")
-
+	
+	def prepare_args(self, parser, plotData):
+		super(BinErrorsOfEmptyBins, self).prepare_args(parser, plotData)
+		self.whitelist = plotData.plotdict["nicks"]
+	
 	def _selector(self, nick, root_histogram, plotData):
 		if isinstance(root_histogram, ROOT.TH1):
 			self.bin_error_for_empty_bins = plotData.plotdict["empty_bin_error_scale"] * root_histogram.GetSumOfWeights() / root_histogram.GetEntries()
+		else:
+			return False
 		return super(BinErrorsOfEmptyBins, self)._selector(nick, root_histogram, plotData)
 
 	def _manipulate_bin(self, histogram, global_bin):
-		if root_histogram.GetBinContent(global_bin) == 0.0:
-			root_histogram.SetBinError(global_bin, self.bin_error_for_empty_bins)
+		if histogram.GetBinContent(global_bin) == 0.0:
+			histogram.SetBinError(global_bin, self.bin_error_for_empty_bins)
+

### 2015-09-20 HarryPlotter/python/analysis_modules/correctnegativebincontents.py
correctnegativebincontents.py: derive from HistogramManipulationBase, change default to work on all nicks, disable passing whitespace-sparated lists of nicks

@@ -9,10 +9,11 @@ log = logging.getLogger(__name__)
 
 import ROOT
 
-import Artus.HarryPlotter.analysisbase as analysisbase
+import Artus.HarryPlotter.analysis_modules.histogrammanipulationbase as histogrammanipulationbase
 
 
-class CorrectNegativeBinContents(analysisbase.AnalysisBase):
+class CorrectNegativeBinContents(histogrammanipulationbase.HistogramManipulationBase):
+	"""Set bin errors of negative bins to 0 while preserving the integral of histograms."""
 
 	def __init__(self):
 		super(CorrectNegativeBinContents, self).__init__()
@@ -21,41 +22,32 @@ class CorrectNegativeBinContents(analysisbase.AnalysisBase):
 		super(CorrectNegativeBinContents, self).modify_argument_parser(parser, args)
 
 		self.correctnegbincontent_options = parser.add_argument_group("CorrectNegativeBinContents options")
-		self.correctnegbincontent_options.add_argument("--nicks-correct-negative-bins", nargs="+",
-							       default=[],
-							       help="Nicks of histograms to be corrected. [Default: %(default)s]")
+		self.correctnegbincontent_options.add_argument(
+				"--nicks-correct-negative-bins", nargs="+", default=[],
+				help="Nicks of histograms to be corrected. [Default: all]"
+		)
 	
 	def prepare_args(self, parser, plotData):
 		super(CorrectNegativeBinContents, self).prepare_args(parser, plotData)
-
-		plotData.plotdict["nicks_correct_negative_bins"] = [nicks.split() for nicks in plotData.plotdict["nicks_correct_negative_bins"]]
-		if len(plotData.plotdict["nicks_correct_negative_bins"]) == 0:
-			log.warning("CorrectNegativeBinContents module called, but no nicks of the histograms to be corrected are provided")
-	
-	def run(self, plotData=None):
-		super(CorrectNegativeBinContents, self).run(plotData)
 		
-		# loop over all histograms
-		for nicks_correct_negative_bins in plotData.plotdict["nicks_correct_negative_bins"]:
-			for nick in nicks_correct_negative_bins:
-				root_histogram = plotData.plotdict["root_objects"][nick]
-				if isinstance(root_histogram, ROOT.TH1):
-					original_integral = root_histogram.Integral()
-					negative_bin_contents_found = False
-				
-					# loop over all bins
[…]

### 2015-09-20 HarryPlotter/python/analysis_modules/binerrorsofemptybins.py
binerrorsofemptybins.py: fix for empty histograms

@@ -28,7 +28,10 @@ class BinErrorsOfEmptyBins(histogrammanipulationbase.HistogramManipulationBase):
 	
 	def _selector(self, nick, root_histogram, plotData):
 		if isinstance(root_histogram, ROOT.TH1):
-			self.bin_error_for_empty_bins = plotData.plotdict["empty_bin_error_scale"] * root_histogram.GetSumOfWeights() / root_histogram.GetEntries()
+			if root_histogram.GetEntries() == 0:
+				self.bin_error_for_empty_bins = 0.0
+			else:
+				self.bin_error_for_empty_bins = plotData.plotdict["empty_bin_error_scale"] * root_histogram.GetSumOfWeights() / root_histogram.GetEntries()
 		else:
 			return False
 		return super(BinErrorsOfEmptyBins, self)._selector(nick, root_histogram, plotData)

### 2015-09-20 HarryPlotter/python/analysis_modules/binerrorsofemptybins.py
binerrorsofemptybins.py: added argument to configure the nicks to modify

@@ -19,12 +19,22 @@ class BinErrorsOfEmptyBins(histogrammanipulationbase.HistogramManipulationBase):
 		super(BinErrorsOfEmptyBins, self).modify_argument_parser(parser, args)
 		
 		self.empty_bins_options = parser.add_argument_group("Empty bins errors options")
-		self.empty_bins_options.add_argument("--empty-bin-error-scale", type=float, default=0.6,
-				help="Scale factor for bin errors of empty bins = sf * sum of weights / entries of histogram. [Default: %(default)s]")
+		self.empty_bins_options.add_argument(
+				"--nicks-empty-bins", nargs="+", default=[],
+				help="Nicks of histograms to be corrected. [Default: all]"
+		)
+		self.empty_bins_options.add_argument(
+				"--empty-bin-error-scale", type=float, default=0.6,
+				help="Scale factor for bin errors of empty bins = sf * sum of weights / entries of histogram. [Default: %(default)s]"
+		)
 	
 	def prepare_args(self, parser, plotData):
 		super(BinErrorsOfEmptyBins, self).prepare_args(parser, plotData)
-		self.whitelist = plotData.plotdict["nicks"]
+		
+		if len(plotData.plotdict["nicks_empty_bins"]) > 0:
+			self.whitelist = plotData.plotdict["nicks_empty_bins"]
+		else:
+			self.whitelist = plotData.plotdict["nicks"]
 	
 	def _selector(self, nick, root_histogram, plotData):
 		if isinstance(root_histogram, ROOT.TH1):

### 2015-09-21 Configuration/python/artusWrapper.py
changed default batch mode for grid-control config changes to be committed

@@ -348,7 +348,7 @@ class ArtusWrapper(object):
 		                                 help="Measure performance with profiler. Choose igprof or valgrind.")
 		runningOptionsGroup.add_argument("-r", "--root", default=False, action="store_true",
 		                                 help="Open output file in ROOT TBrowser after completion.")
-		runningOptionsGroup.add_argument("-b", "--batch", default=False, const="local", nargs="?",
+		runningOptionsGroup.add_argument("-b", "--batch", default=False, const="naf", nargs="?",
 		                                 help="Run with grid-control. Optionally select backend. [Default: %(default)s]")
 		runningOptionsGroup.add_argument("--no-log-to-se", default=False, action="store_true",
 		                                 help="Do not write logfile in batch mode directly to SE.")

### 2015-09-21 HarryPlotter/scripts/get_binning_with_equal_entries.py
Added script to determine binning with roughly equal number of entries per bin

@@ -1,0 +1,48 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+import logging
+import Artus.Utility.logger as logger
+log = logging.getLogger(__name__)
+
+import argparse
+
+import Artus.HarryPlotter.analysis_modules.eventselectionoverlap as eventselectionoverlap
+from Artus.HarryPlotter.utility.tfilecontextmanager import TFileContextManager
+
+
+def get_binning_with_equal_entries():
+	"""Get binning with roughly equal number of entries per bin
+	
+		Example usage: get_binning_with_equal_entries.py artus_output.root  folder/ntuple  quantityname  --n-bins 10
+	"""
+
+	parser = argparse.ArgumentParser(description="Print binning of histograms", parents=[logger.loggingParser])
+
+	parser.add_argument("root_file", help="Input ROOT file")
+	parser.add_argument("folder", help="Folder to TTree")
+	parser.add_argument("quantity", help="Quantity for which binning should be determined")
+	parser.add_argument("--n-bins", type=int, help="Number of bins. [Default: %(default)s]", default=25)
+	parser.add_argument("--selection", type=str, help="Optional selection", default="1")
+
+	args = parser.parse_args()
+	logger.initLogger(args)
+	
+	with TFileContextManager(args.root_file, "READ") as root_file:
+		tree = root_file.Get(args.folder)
+
+		events_list = sorted([e[0] for e in eventselectionoverlap.EventSelectionOverlap.get_events_list_from_tree(tree, args.quantity, args.selection)])
+		assert(len(events_list) > args.n_bins)
+
+		# slice events list
+		bin_border_list = []
+		for i_bin in range(args.n_bins):
+			bin_border_list.append(events_list[int(round(i_bin/float(args.n_bins)*len(events_list)))])
+		bin_border_list.append(events_list[-1])
+		
+		log.info("Bin borders for {} bins:".format(args.n_bins))
+		log.info(" ".join([str(i) for i in bin_border_list]))
+
+
+if __name__ == "__main__":
+	get_binning_with_equal_entries()

### 2015-09-21 Utility/python/tools.py
tools.py: small fix

@@ -148,10 +148,7 @@ def parallelize(function, arguments_list, n_processes=1):
 	if n_processes <= 1:
 		results = []
 		for arguments in arguments_list:
-			if isinstance(arguments, basestring):
-				results.append(function(arguments))
-			else:
-				results.append(function(*arguments))
+			results.append(function(arguments))
 		return results
 	else:
 		pool = multiprocessing.Pool(processes=min(n_processes, len(arguments_list)))

### 2015-09-21 HarryPlotter/python/plot_modules/plotroot.py
plotroot: possible solution for adding bin labels which survive the axis replot

@@ -299,15 +299,7 @@ class PlotRoot(plotbase.PlotBase):
 				if (not plotData.plotdict["z_label"] is None) and (plotData.plotdict["z_label"] != "" and hasattr(root_object, "GetZaxis")):
 					root_object.GetZaxis().SetTitle(plotData.plotdict["z_label"])
 			
-			# tick labels
-			if plotData.plotdict["x_tick_labels"] and len(plotData.plotdict["x_tick_labels"]) > 0:
-				for x_bin in range(min(root_object.GetNbinsX(), len(plotData.plotdict["x_tick_labels"]))):
-					root_object.GetXaxis().SetBinLabel(x_bin+1, plotData.plotdict["x_tick_labels"][x_bin])
-			
-			if plotData.plotdict["y_tick_labels"] and len(plotData.plotdict["y_tick_labels"]) > 0:
-				for y_bin in range(min(root_object.GetNbinsY(), len(plotData.plotdict["y_tick_labels"]))):
-					root_object.GetYaxis().SetBinLabel(y_bin+1, plotData.plotdict["y_tick_labels"][y_bin])
-			
+			# tick labels (z-axis) TODO: unify this with the x and y bin labels mechanism?
 			if plotData.plotdict["z_tick_labels"] and len(plotData.plotdict["z_tick_labels"]) > 0:
 				for z_bin in range(min(root_object.GetNbinsZ(), len(plotData.plotdict["z_tick_labels"]))):
 					root_object.GetZaxis().SetBinLabel(z_bin+1, plotData.plotdict["z_tick_labels"][z_bin])
@@ -439,17 +431,19 @@ class PlotRoot(plotbase.PlotBase):
 		super(PlotRoot, self).make_plots(plotData)
 		
 		# draw empty histograms for the axes
-		n_bins = 1 # TODO: consider axis ticks
-		n_sub_bins = 1 # TODO: consider axis ticks
+		n_binsX = len(plotData.plotdict["x_tick_labels"]) if plotData.plotdict["x_tick_labels"] else 1
+		n_binsY = len(plotData.plotdict["y_tick_labels"]) if plotData.plotdict["y_tick_labels"] else 1
+		n_sub_binsX = len(plotData.plotdict["x_tick_labels"]) if plotData.plotdict["x_tick_labels"] else 1
[…]

### 2015-09-21 HarryPlotter/python/utility/roottools.py
roottools: small addition in printout

@@ -57,7 +57,7 @@ class RootTools(object):
 					if print_quantities:
 						log.info("List of all histogram/graph/function quantities (in the first file):")
 						for key, path in sorted(RootTools.walk_root_directory(root_object), key=lambda element: element[1]):
-							if key.GetClassName().startswith("TH") or key.GetClassName().startswith("TF") or "Graph" in key.GetClassName():
+							if key.GetClassName().startswith("TH") or key.GetClassName().startswith("TF") or key.GetClassName().startswith("Roo") or "Graph" in key.GetClassName():
 								log.info("\t%s (%s)" % (path, key.GetClassName()))
 					return ROOT.TH1
 				else:

### 2015-09-21 HarryPlotter/python/input_modules/inputrootsimple.py
HarryPlotter: new input module Very simple input module which just opens a ROOT file and stores the desired ROOT/RooFit content into the dictionary.

@@ -1,0 +1,43 @@
+# -*- coding: utf-8 -*
+
+"""
+	Just opens a ROOT file and stores the ROOT/RooFit content in the root_objects.
+"""
+
+import logging
+import Artus.Utility.logger as logger
+log = logging.getLogger(__name__)
+
+import ROOT
+
+import Artus.HarryPlotter.inputbase as inputbase
+
+
+class InputRootSimple(inputbase.InputBase):
+
+	def modify_argument_parser(self, parser, args):
+		super(InputRootSimple, self).modify_argument_parser(parser, args)
+		
+		self.input_options.add_argument("-i", "--files", type=str, nargs="+",
+		                                help="Input (root) file(s).")
+		self.input_options.add_argument("--root-names", nargs="+",
+		                                help="Name(s) of ROOT/RooFit objects to retrieve.")
+
+	def prepare_args(self, parser, plotData):
+		super(InputRootSimple, self).prepare_args(parser, plotData)
+		self.prepare_list_args(plotData, ["root_names"])
+
+		if plotData.plotdict.get("nicks", None) == [None]:
+			plotData.plotdict["nicks"] = []
+
+		if all([item == [None] for item in [plotData.plotdict.get(item2+"_expressions", None) for item2 in ['x', 'y', 'z']]]) and plotData.plotdict["filename"] == None:
+			plotData.plotdict["filename"] = None
+
+	def run(self, plotData):
+		for index, filename in enumerate(plotData.plotdict['files']):
+			file = ROOT.TFile(filename)
+
+			for name in plotData.plotdict["root_names"]:
+				root_obj = file.Get(name)
+				plotData.plotdict.setdefault("nicks", []).append(name)
+				plotData.plotdict.setdefault("root_objects", {})[name] = root_obj

### 2015-09-21 Core/doc/latex/paper.tex
points to prose

@@
 Based on the workflow described in the previous section, the following demands for an analyis framework arise:
-\begin{itemize}
- \item Performance
- \begin{itemize}
-  \item High performance for fast turnaround cycles, even with large data amounts % -> C++, pipelines, only necessary producers
-  \item Flexibility %TODO define need for different configurations in previous section
- \end{itemize}
- \item Maintainability
- \begin{itemize}
-  \item Easy to install
-  \item Readable and understandable, also for programming newcomers
-  \item Compatibility with different operating platforms/environments % standalone compile with make, integrated batch/GC functionality
-  \item Compatible with different data formats % -> data format defined outside (kappa)
-  \item Clear separation of code, data and settings % -> json config
- \end{itemize}
+\subsection{Performance}
+The main performance indicator is the \emph{turnaround time}, which means the time that is needed for the whole analysis in case new requirements arise.
+Since the runtime is often limited by the transfer speed to the storage elements, \artus is designed to load each event only once from the storage system and performs all necessary steps directly.
+This is made possible with the pipelining concept.
+Still, since analysis requirements sometimes change within a few hours, a high flexibility is needed.
+This explains the need for a modular structure, where only those parts of the code are executed that really are necessary for the analysis.
+\subsection{Maintainability}
+Keeping code maintained, i.e.
+up-to-date with the latest requirements while not losing backwards compatibility is a challenge for each software project.
+The first important step is an always updated recipe that works out of the box on each machine offering CVMFS.
+To make the entry level as low as possible, beginners can start with an example analysis.
+In \artus, everything is steered via JSON config files.
+The modules then implement what has to be done while the data is stored in desired data format.
 
- \item Reliability
- \begin{itemize}
-  \item Use existing libraries and existing HEP code wherever possible % -> C++ used
-  \item Reliable and checked source code % -> Unit tests, code sharing
-  \item Avoids frequent re-implementations by being used in different physics analyses % -> modular structure, producers
-  \item Readable, since sourcecode is the most precise documentation possible
- \end{itemize}
-\end{itemize}
+\artus has the built-in possibility to submit analysis jobs with grid-control, a job submission tool.
 
-The \artus design choices are fully based on these requirements.
+\subsection{Reliability}
+In most cases, analysis never leave prototype status.
+This leads to frequent re-implementations and low trust in reliability.
+\artus allows the re-use of analysis code due to its modular structur as well as sharing it between different analysis groups, with improves code quality by far.
+
+Sourcecode and configuration files have become the most precise form of documentation.
+Therefore, readability also for people who have not written the code is crucial.
+Also, if possible, standard existing libraries from HEP are interfaced.
 

### 2015-09-21 Core/doc/latex/paper.tex
adjustments: KIT colors, numbers from Joram's thesis'

@@
 \centering \input{figures/analysis_steps}
-\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics.
+\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics, numbers taken from \cite{joram_phd}.
+Data size is reduced by six orders of magnitude, turnaround time by 4.
 I/O intensive operations are done in highly parallel in the WLCG.

### 2015-09-22 HarryPlotter/python/plotbase.py
plotbase: add possible settings related to the canvas

@@ -80,6 +80,9 @@ class PlotBase(processor.Processor):
 		self.axis_options.add_argument("--z-tick-labels", type=str, nargs="+",
 		                               help="Custom tick labels for the Z-axis")
 
+		# canvas settings
+		self.canvas_options = parser.add_argument_group("Canvas options")
+
 		#plot formatting
 		self.formatting_options = parser.add_argument_group("Formatting options")
 		self.formatting_options.add_argument("--color-scheme", default="default",

### 2015-09-22 KappaAnalysis/interface/Producers/ValidElectronsProducer.h
ValidElectronsProducer: fix for cutbased ID/iso

@@ -171,6 +171,11 @@ public:
 		electronIso = ToElectronIso(boost::algorithm::to_lower_copy(boost::algorithm::trim_copy((settings.*GetElectronIso)())));
 		electronReco = ToElectronReco(boost::algorithm::to_lower_copy(boost::algorithm::trim_copy((settings.*GetElectronReco)())));
 		
+		if ((boost::algorithm::contains((settings.*GetElectronID)(), "vbft95")) && (electronIso==ElectronIso::NONE))
+		{
+			LOG(WARNING) << "ValidElectronsProducer: using cutbased vbft95 ID, but isolation is not set!";
+		}
+
 		// add possible quantities for the lambda ntuples consumers
 		LambdaNtupleConsumer<TTypes>::AddIntQuantity("nElectrons", [](event_type const& event, product_type const& product) {
 			return product.m_validElectrons.size();
@@ -344,8 +349,8 @@ public:
 			       (electron->sigmaIetaIeta < 0.01f) &&
 			       (electron->hadronicOverEm < 0.15f) &&
 			       (std::abs(electron->track.getDxy(&event.m_vertexSummary->pv)) < 0.04f) &&
-			       (std::abs(electron->track.getDz(&event.m_vertexSummary->pv)) < 0.2f) &&
-			       (electron->pfIso() / electron->p4.Pt() < 0.15f);
+			       (std::abs(electron->track.getDz(&event.m_vertexSummary->pv)) < 0.2f);
+			       // no isolation
 		}
 		else
 		{
@@ -355,7 +360,7 @@ public:
 			       (electron->sigmaIetaIeta < 0.03f) &&
 			       (std::abs(electron->track.getDxy(&event.m_vertexSummary->pv)) < 0.04f) &&
 			       (std::abs(electron->track.getDz(&event.m_vertexSummary->pv)) < 0.2f);
-			       (electron->pfIso() / electron->p4.Pt() < 0.15f);
+			       // no isolation
 		}
 		return false;
 	}
@@ -413,6 +418,7 @@ public:
 		       (std::abs(electron->track.getDz(&event.m_vertexSummary->pv)) < Dz) &&
 		       (std::abs(1.0f/(electron->ecalEnergy) - 1.0f/(electron->ecalEnergy/electron->eSuperClusterOverP)) < EP) &&
 		       (electron->track.nInnerHits <= missingHits);
+		       // no isolation
 		       // no conversion rejection
 	}
 

### 2015-09-22 HarryPlotter/python/plot_modules/plotroot.py
plotroot: add title in the keys for the nice labels

@@ -195,7 +195,7 @@ class PlotRoot(plotbase.PlotBase):
 			plotData.plotdict["legend"] += [0.6, 0.6, 0.9, 0.9][len(plotData.plotdict["legend"]):]
 			plotData.plotdict["legend"] = plotData.plotdict["legend"][:4]
 		
-		for key in ["labels", "x_label", "y_label", "z_label"]:
+		for key in ["labels", "x_label", "y_label", "z_label", "title"]:
 			if isinstance(plotData.plotdict[key], basestring):
 				plotData.plotdict[key] = self.nice_labels.get_nice_label(plotData.plotdict[key])
 			elif isinstance(plotData.plotdict[key], collections.Iterable):

### 2015-09-22 HarryPlotter/python/analysis_modules/functionplot.py
functionplot.py: add option for parameter names

@@ -26,6 +26,8 @@ class FunctionPlot(analysisbase.AnalysisBase):
 						help="Fit backend. ROOT and RooFit are available. Check sourcecode which parts of RooFit are implemented. [Default: %(default)s]")
 		self.function_options.add_argument("--function-display-result", action='store_true',
 						help="Display the parameters of the fit on the plots")
+		self.function_options.add_argument("--function-fit-parameter-names", type=str, nargs="+", default=["Parameter"],
+						help="Names of the parameters (e.g. 'Slope'). Only relevant if --function-display-result is True. [Default: %(default)s]")
 
 
 	def prepare_args(self, parser, plotData):
@@ -178,9 +180,15 @@ class FunctionPlot(analysisbase.AnalysisBase):
 		text = "Fit results"
 		if len(plotData.plotdict["function_fit"]) > 1:  # only add the nickname if more than one fit
 			text += " {}:".format(function_nick)
+
+		# expand paramter_names if necessary
+		if len(plotData.plotdict["function_fit_parameter_names"]) < plotData.plotdict["root_objects"][function_nick].GetNpar():
+			plotData.plotdict["function_fit_parameter_names"] *= plotData.plotdict["root_objects"][function_nick].GetNpar()/len(plotData.plotdict["function_fit_parameter_names"])
+		l = max([len(s) for s in plotData.plotdict["function_fit_parameter_names"]])
+
 		for i_par in range(plotData.plotdict["root_objects"][function_nick].GetNpar()):
 			#TODO automatically adjust decimal precision
-			text += "\n  $Parameter {} = {:.3f} \pm {:.3f}$".format(i_par,
+			text += "\n  ${} = {:.3f} \pm {:.3f}$".format(plotData.plotdict["function_fit_parameter_names"][i_par],
 			        plotData.plotdict["root_objects"][function_nick].GetParameter(i_par),
 			        plotData.plotdict["root_objects"][function_nick].GetParError(i_par))
 		text += "\n  $\chi^2 / \mathit{{n.d.f}} = {:.2f} / {}$".format(

### 2015-09-22 Core/doc/latex/paper.tex
text fixes and improvements to the Artus paper

@@
 \begin{abstract}
-We present \artus, an event-by-event data-processing framework for high energy physics experiments.
-\artus is designed for large-scale data analysis in a collaborative environment.
+We present \artus, an event-based data-processing framework for high energy physics experiments.
+\mbox{\artus} is designed for large-scale data analysis in a collaborative environment.
 The architecture design choices take into account typical challenges and are based on experiences with similar applications.
 The structure of the framework and its advantages are described.
-An example usecase and performance measurements are presented.
+An example use case and performance measurements are presented.
 The framework is well-tested and successfully used by several analysis groups.\todo{Mention them, maybe with publications? -> mentioned at the beginning of Htt chapter. Do we have publications?}
@@
 % From these problems, the design requirements for Artus are derived.
-Without loss of generality, in what follows the workflow of the experiments collecting data at the Large Hadron Collider (LHC) at CERN is taken as an example to illustate the organization and needs of a modern High Energy Physics analysis.
+The workflow of the experiments collecting data at the Large Hadron Collider (LHC) at CERN is taken as an example to illustrate the organization and needs of a modern High Energy Physics (HEP) analysis.
+Still, equal or very similar requirements are also present for HEP experiments not located at the LHC.
 
@@
 The data which are relevant for a specific analysis are selected in a step usually referred to as \textit{skimming}.
-The output of the skimming is a mostly analysis-dependent file, usually in an n-tuple format, small enough to be stored at local file servers, often owned and operated by a single institute.
+The output of the skimming process is an analysis-dependent file, usually in an n-tuple format, and small enough to be stored on local file servers, often owned and operated by a single institute.
 The size of these files ranges from $\mathcal O(10)$~GB to few~TB.
@@
 This processing step includes further event selections, event categorization or high-level calculations based on the selected physics objects.
-The events are usually processed with different configurations, depending from the specific analysis needs.
+The events are usually processed with different configurations, depending on the specific analysis needs.
 The output is then used for post-processing steps, including plotting of the results and their statistical interpretation.
 
-In many cases the code for the last step is developed without a predefined strategy or structure, following the evolving needs of the analysis which are often physics-driven and not always entirely predictable in the code design phase.
+In many cases, the code for the last step is developed without a predefined strategy or structure, following the evolving needs of the analysis which are often physics-driven and not always entirely predictable in the code design phase.
 This leads to convoluted, tangled and unstructured code, which is difficult to understand and to maintain and also difficult to hand over to new people joining the analysis effort.
@@
 \caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics, numbers taken from \cite{joram_phd}.
-Data size is reduced by six orders of magnitude, turnaround time by 4.
+Data size is reduced by six orders of magnitude, turnaround time by a factor of 4.
 I/O intensive operations are done in highly parallel in the WLCG.
-The computing-intensive operations are only performed if really necessary.
-This means that selection steps are performed as early as possible.}
+The data reduction is achieved by performing the data-intensive operations only rarely and applying sensible event selection steps as early as possible.}
 \label{figure_analysis_steps}
@@
 %define requirements based on previous section, following sections: describe how they are fullfilled
-Based on the workflow described in the previous section, the following demands for an analyis framework arise:
+Based on the workflow described in the previous section, the following demands for an analysis framework arise:
 \subsection{Performance}
-The main performance indicator is the \emph{turnaround time}, which means the time that is needed for the whole analysis in case new requirements arise.
-Since the runtime is often limited by the transfer speed to the storage elements, \artus is designed to load each event only once from the storage system and performs all necessary steps directly.
+The main performance indicator is the \emph{turnaround time}, which means the time that is needed to run the whole analysis in case new requirements arise.
+Since the runtime is often limited by the transfer speed of the storage servers, \artus is designed to load each event only once and perform all necessary processing steps.
 This is made possible with the pipelining concept.
-Still, since analysis requirements sometimes change within a few hours, a high flexibility is needed.
+Still, since analysis requirements sometimes change within a few hours, a high level of flexibility is needed.
 This explains the need for a modular structure, where only those parts of the code are executed that really are necessary for the analysis.
 \subsection{Maintainability}
-Keeping code maintained, i.e.
-up-to-date with the latest requirements while not losing backwards compatibility is a challenge for each software project.
-The first important step is an always updated recipe that works out of the box on each machine offering CVMFS.
+Source code maintenance, i.e.
+to be up-to-date with the latest requirements while not losing backwards compatibility, is a challenge for each software project.
+The first important step is to always have  an updated recipe that works out of the box on each machine offering CVMFS.
 To make the entry level as low as possible, beginners can start with an example analysis.
-In \artus, everything is steered via JSON config files.
+In \artus, everything is steered via JSON configuration files.
 The modules then implement what has to be done while the data is stored in desired data format.
@@
 \subsection{Reliability}
-In most cases, analysis never leave prototype status.
+In most cases, analyses never leave prototype status.
 This leads to frequent re-implementations and low trust in reliability.
-\artus allows the re-use of analysis code due to its modular structur as well as sharing it between different analysis groups, with improves code quality by far.
+\artus allows the re-use of analysis code due to its modular structur as well as sharing it between different analysis groups, and therefore improving code quality significantly.
 
-Sourcecode and configuration files have become the most precise form of documentation.
+Source code and configuration files have become the most precise form of documentation.
 Therefore, readability also for people who have not written the code is crucial.
-Also, if possible, standard existing libraries from HEP are interfaced.
+Also, if possible, existing and well-established libraries of the HEP community are interfaced.
 
@@
 zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/\artus}} provides a front-to-end solution for the analysis of event-based data.
-The basic concept of modules processing the events within an event loop is complemented by tools for the configuration of every step.
+The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.
 The complete structure is explained in the next section~\ref{section_artus_structure}.
@@
 
-\artus respects the separation of code and settings.
+\artus respects the separation of code and configuration.
 Settings select what has to be done and with wich parameters.
@@
 First, a so-called global pipeline is run.
-Then the execution is split up into multiple so-called local pipelines, that are also processed sequentially.
+Then, the execution is split up into multiple so-called local pipelines, that are also processed sequentially.
 The composition of a pipeline is illustrated in figure~\ref{figure_artus_pipeline}.
@@
 The local pipelines can access both their own settings and the ones of the global pipeline.
-Thus, a mechanism exists that enables processing the same event with different configurations, whereas the costly reading of the input is only needed to be done once.
+Thus, a mechanism exists that enables processing the same event with different configurations, whereas the costly reading of the input is only done once.
 Similarly, a product object is managed by each pipeline.
@@
 \item[Filters] apply a selection based on event properties.
-In case an event does not survive a requirement defined by a filter, the processing of the subsequent producers and filters can be skipped.
+In case an event does not fulfil a requirement defined by a filter, the processing of the subsequent producers and filters can be skipped.
 \item[Consumers] can be added to local pipelines.
@@
 \item[High performance] The concept of pipelines allows to analyse the data with different configurations at the same time, while the data is only read in only once and common processing steps are shared in the global pipeline.
-Therefore the cost-intensive input operations are reduced to a minimum.
+Therefore, the cost-intensive input operations are reduced to a minimum.
 \end{description}
@@
 Maybe rewrite parts of this section}
-In the \artus framework each concrete analysis is defined by a set of object types.
-It needs an implementation of the classes for settings, the event and the product.
-The settings class defines the tags that should be able to be read from the configuration file and the corresponding types of the values.
-The event class defines the event content being read from the input and the product class contains members for new quantities being calculated by the analysis.
-These three classes need to be derived from the base classes in the core of the framework.
+In the \artus framework, each concrete analysis is defined by a set of object types.
+The analysis programmer must provide an implementation of the classes for settings, the event and the product class.
+The settings class defines the tags that are read from the configuration file and the corresponding types of these values.
+The event class defines the event content which is read from the input and the product class contains members for new quantities calculated during the analysis stage.
+These three classes need to be derived from the base classes provided by the core of the \artus framework.
 
@@
 The event provider must know how to read event content from the input files and how to store them in the event object.
-Furthermore, a factory managing the creation of analysis-specific processors needs to exists.
+Furthermore, a factory managing the creation of analysis-specific processors needs to exist.
 These classes also have to be derived from the \artus base classes.
@@
 The computationally expensive event processing steps are followed by the post-processing of the results and their presentation.
-From a technical point of view the focus here is rather on flexibility than on performance.
-The inputs for this step are either histograms filled in the previous step or n-tuples whose entries can be filled into histograms at low cost.
+From a technical point of view, the focus here is rather on flexibility than on performance.
+The inputs for this step are either histograms filled in the previous step or n-tuples whose entries can be filled into histograms with reasonable computing costs.
 For this reason, Python has been chosen as language for the HarryPlotter framework\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/HarryPlotter}}.
@@
 \item One or, in special cases, multiple plot modules are executed in the last step.
-Their function is to output the processed data in the specified format.
-In most of the cases, the output is a plot but it is also possible to store the objects in new ROOT files.
+Their task is to output the processed data in the specified format.
+In most cases, the output is a plot but it is also possible to store the objects in new ROOT files.
 \end{enumerate}
 All processors share a common plot data object and possible meta-data where they can add new information and read the existing one.
-For example, the input modules add histograms read in from input files and the plot modules access these histograms.
+For example, the input modules add histograms read from input files and the plot modules access these histograms.
 
@@
 The executable can perform one single plot per run.
-For the execution within a script functions exist to create multiple plots in parallel.
+For the execution within a script, functions exist to create multiple plots in parallel.
 
-The parsing of the arguments is performed in two steps.
-The first time it determines the sequence of modules to be executed.
-These modules are then initialised and can define additional arguments needed for their configuration, such that every module can manage its own settings but can also access the settings of entire program.
-After all arguments are defined the configuration is parsed a second time providing the full settings for the HarryPlotter run.
+The parsing of the arguments is performed in two steps:
+First, the sequence of modules to be executed is determined.
+These modules are then initialised and can define additional arguments needed for their configuration, such that every module can manage its own settings but can also access the settings of the entire program.
+After all arguments are defined, the configuration is parsed a second time providing the full settings for the HarryPlotter run.
 Then all processors are executed as described above.
@@
 
-Currently, the \artus framework is used for various user analysis of CMS data ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model.
+Currently, the \artus framework is used for various user analysas of CMS data, ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model.
 As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis are explained in the following.
@@
 The event class contains members for all important physics objects used in analyses.
-The branches of the n-tuples, that should be read in from the input files, are configurable.
-Reducing the amount of information transferred from the input files accelerates the analysis significantly.
+The branches of the n-tuples, that should be read in from the input files, are configurable and which reduces the amount of information transferred from the input files and therefore accelerates the analysis significantly.
 
-The structure of the pipelines is chosen such that for each decay channel a separate pipeline exists.
+The structure of the pipelines is chosen such that, for each decay channel, a separate pipeline exists.
 Each of the pipelines is duplicated and modified in order to implement the different settings for shifts of quantities affected by systematic uncertainties.
@@
 The global pipeline is used to perform actions that are common for all channels.
-This is for example the identification of jets and their correction as well as the filtering of valid data events.
+This is for example the identification of jets and their corrections as well as the filtering of valid data events.
 
@@
 Main producers are the ones for the identification and the selection of valid leptons and jets.
-Further producers perform the matching with trigger or generator objects and do the splitting into decay channels or the categorisation.
+Further producers perform the matching with trigger or generator objects and perform the splitting into decay channels or the categorisation.
 Also the mass reconstruction is done in a separate producer.
@@
 
-The post-processing step either output plots or writes the histograms to ROOT files and passes them over to the limit calculation tools.
+The post-processing step either outputs plots or writes the histograms to ROOT files and passes them over to the limit calculation tools.
 

### 2015-09-22 HarryPlotter/scripts/ini_harry_cmssw.sh
Remove extra path for HarryPlotter
This part of the python path was only needed in older CMSSW versions and
is now obsolete.

@@ -1,8 +1,5 @@
 #!/bin/bash
 
-# This line fixes a bug in CMSSW6. The dateutils are not present there. This uses the dateutils from python 2.6
-export PYTHONPATH=$PYTHONPATH:${CMSSW_RELEASE_BASE}/../../../../slc5_amd64_gcc462/external/py2-matplotlib/1.0.1/lib/python2.6/site-packages/
-
 # set some variables needed for --userpc and web plotting
 # set HARRY_REMOTE_USER manually if you have a different user name on the web plot server
 if [ -z $HARRY_REMOTE_USER ]; then

### 2015-09-22 HarryPlotter/python/input_modules/inputrootsimple.py
InputRootSimple: give defaults

@@ -19,9 +19,9 @@ class InputRootSimple(inputbase.InputBase):
 		super(InputRootSimple, self).modify_argument_parser(parser, args)
 		
 		self.input_options.add_argument("-i", "--files", type=str, nargs="+",
-		                                help="Input (root) file(s).")
+		                                default='', help="Input (root) file(s).")
 		self.input_options.add_argument("--root-names", nargs="+",
-		                                help="Name(s) of ROOT/RooFit objects to retrieve.")
+		                                default=[], help="Name(s) of ROOT/RooFit objects to retrieve.")
 
 	def prepare_args(self, parser, plotData):
 		super(InputRootSimple, self).prepare_args(parser, plotData)
@@ -34,7 +34,7 @@ class InputRootSimple(inputbase.InputBase):
 			plotData.plotdict["filename"] = None
 
 	def run(self, plotData):
-		for index, filename in enumerate(plotData.plotdict['files']):
+		for index, filename in enumerate(plotData.plotdict["files"]):
 			file = ROOT.TFile(filename)
 
 			for name in plotData.plotdict["root_names"]:

### 2015-09-23 Core/doc/latex/paper.tex
added conclusion

@@
 
+\section{Conclusion}
+% what Artus does
+% what it brought to the analysis:
+% - code reuse among analysis groups
+% - faster turnaround
+% - faster new analysis
+% - increased data in Run 2
+
+The \artus analysis framework presented in this paper offers a comprehensive and well-integrated solution for event-based data analyses in the HEP domain.
+In conjunction with the plotting toolkit HarryPlotter, all data analysis needs are covered.
+
+The modular and structured manner, in which the processing required for an analysis, can be expressed within the \artus framework, allowed the involved research groups to share and re-use source code on a scale not possible before.
+The concept underlying the \artus framework also enabled us to share program code between analysis and even across different universities and research centres.
+
+Especially new students joining the analysis groups can contribute very quickly.
+Once they have understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.
+In a similar manner, using the \artus framework, it is now much less work to set up a new analysis because a rich library of processors, filters and consumers exists and can be reused for new analysis.
+
 \vspace{2cm}

### 2015-09-23 Core/doc/latex/paper.tex
paper.tex: improved placement of figures
paper.tex: make todos inline to better read them

@@
 An example use case and performance measurements are presented.
-The framework is well-tested and successfully used by several analysis groups.\todo{Mention them, maybe with publications? -> mentioned at the beginning of Htt chapter. Do we have publications?}
+The framework is well-tested and successfully used by several analysis groups.\todo[inline]{Mention them, maybe with publications?
+-> mentioned at the beginning of Htt chapter.
+Do we have publications?}
 \end{abstract}
@@
 The resulting datasets contain event information and high-level physics objects and are of $\mathcal O(10-100)$~TB in size.
-\todo{move file size numbers to Figure \ref{figure_analysis_steps}?}
+\todo[inline]{move file size numbers to Figure \ref{figure_analysis_steps}?}
 
@@
 
-\begin{figure}[p]
+\begin{figure}[t]
 \centering \input{figures/analysis_steps}
@@
 \end{figure}
-\todo{Should we drop CMS-specific technical terms like AOD/miniAOD?
+
+\todo[inline]{Should we drop CMS-specific technical terms like AOD/miniAOD?
 Maybe not put this figure on a dedicated page?}
-\clearpage
 
@@
 
-Following the structure of the CMSSW \todo{Referenz?
+Following the structure of the CMSSW \todo[inline]{Referenz?
 zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/\artus}} provides a front-to-end solution for the analysis of event-based data.
@@
 Consumers are executed after the chain of producers and filters.
-The output together with the complete configuration is written to a ROOT \todo{Referenz auf ROOT?} file.
+The output together with the complete configuration is written to a ROOT \todo[inline]{Referenz auf ROOT?} file.
 These processors are created and managed by a dedicated factory according to the configuration.
 
-\todo{I would not put the remaining part of this chapter here.
+\todo[inline]{I would not put the remaining part of this chapter here.
 It should be either part of the requirements or part of the summary what Artus does achieve; but in this technical part in between it feels misplaced
@@
 \section{Building an End-user Analysis \label{section_artus_analysis}}
-\todo{If I wouldn't know the structure already, the following part wouldn't have helped my.
+\todo[inline]{If I wouldn't know the structure already, the following part wouldn't have helped my.
 Either we support it with a drawing and more detailled explanations or we just refer to a readme...
@@
 
-The structure of the framework is illustrated in figure~\ref{figure_artus_harry_plotter}.
+The structure of the framework is illustrated in Figure~\ref{figure_artus_harry_plotter}.
 It follows the idea of processors in the \artus framework.

### 2015-09-23 Core/doc/latex/paper.tex
paper.tex: more authors
paper.tex: more packages

@@
 \usepackage{url}
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+\usepackage{palatino}
+\usepackage[hidelinks=true,bookmarks=true,plainpages=false]{hyperref}
+\usepackage[colorinlistoftodos,prependcaption]{todonotes}
 
@@
 
-\author[kit]{Thomas M\"uller, Thomas Hauth, Dominik Haitz, Raphael Friese}
-\address[kit]{Karlsruhe Institute of Technology, Wolfgang-Gaede-Stra\ss{}e 1, D-76131 Karlsruhe}
+\author{Fabio Colombo}
+\author{Raphael Friese}
+\author{Dominik Haitz}
+\author{Thomas Hauth}
+\author{Thomas M\"uller}
+\author{G\"unter Quast}
+\author{Georg Sieber}
+\address{Karlsruhe Institute of Technology, Wolfgang-Gaede-Stra\ss{}e 1, D-76131 Karlsruhe}
 
@@
 \end{frontmatter}
+
+%\tableofcontents
 
@@
 Following the structure of the CMSSW \todo[inline]{Referenz?
-zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/\artus}} provides a front-to-end solution for the analysis of event-based data.
+zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
 The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.
@@
 The \artus framework is written in C++.
-The core of the framework only depends on the boost library\footnote{\url{http://www.boost.org/}}.
+The core of the framework only depends on the boost library\footnote{\url{http://www.boost.org}}.
 Further dependencies may be introduced by the actual analysis code.

### 2015-09-23 Core/doc/latex/paper.tex
paper.tex: fixed typos (according to US English)

@@
 
-The reconstruction of the raw data coming from the experiments is performed on large computing centres organized into the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing Grid.
+The reconstruction of the raw data coming from the experiments is performed on large computing centers organized into the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing Grid.
 The resulting datasets contain event information and high-level physics objects and are of $\mathcal O(10-100)$~TB in size.
@@
 This leads to frequent re-implementations and low trust in reliability.
-\artus allows the re-use of analysis code due to its modular structur as well as sharing it between different analysis groups, and therefore improving code quality significantly.
+\artus allows the re-use of analysis code due to its modular structure as well as sharing it between different analysis groups, and therefore improving code quality significantly.
 
@@
 The basic concept of the framework is taken from the code used for the $\PZ+\text{jet}$ analysis documented in reference~\cite{joram_phd}.
-It is generalised and extended to satisfy the needs of various analysis groups.
+It is generalized and extended to satisfy the needs of various analysis groups.
 The structure is illustrated in figure~\ref{figure_artus_structure}.
@@
 The input is read by an event provider.
-Within the pipelines the event content is analysed by the processors.
+Within the pipelines the event content is analyzed by the processors.
 Consumers in local pipelines write results to a common output.
@@
 \centering \input{figures/artus_pipeline}
-\caption[Organisation of processors in a pipeline.]{Organisation of processors in a pipeline.
+\caption[Organization of processors in a pipeline.]{Organization of processors in a pipeline.
 Producers and filters are run before the consumers.
@@
 \artus respects the separation of code and configuration.
-Settings select what has to be done and with wich parameters.
+Settings select what has to be done and with which parameters.
 The code does perform these steps, ideally without the user being fully aware of implementation details.
@@
 
-The events are then sequentially processed by processors organised in pipelines.
+The events are then sequentially processed by processors organized in pipelines.
 First, a so-called global pipeline is run.
@@
 \item[Filters] apply a selection based on event properties.
-In case an event does not fulfil a requirement defined by a filter, the processing of the subsequent producers and filters can be skipped.
+In case an event does not fulfill a requirement defined by a filter, the processing of the subsequent producers and filters can be skipped.
 \item[Consumers] can be added to local pipelines.
@@
 I think the idea was to explain how certain design decisions, e.g. pipelines, achieve the \artus design goals.
-Therefore it shouldnt be too far from the technical descriptions.
+Therefore it should not be too far from the technical descriptions.
 }
@@
 \begin{description}
-\item[Modular structure] Analysis steps are implemented in processors, breaking down the complete analysis in well-defined and easily understandable and writeable parts.
-\item[Re-utilisation of code] Processors can be shared among different analysis groups.
+\item[Modular structure] Analysis steps are implemented in processors, breaking down the complete analysis in well-defined and easily understandable and writable parts.
+\item[Re-utilization of code] Processors can be shared among different analysis groups.
 Every user contributes to the testing of existing code and improves the confidence in this code.
@@
 Each pipeline is mapped to a separate sub-set of the configuration.
-\item[High performance] The concept of pipelines allows to analyse the data with different configurations at the same time, while the data is only read in only once and common processing steps are shared in the global pipeline.
+\item[High performance] The concept of pipelines allows to analyze the data with different configurations at the same time, while the data is only read in only once and common processing steps are shared in the global pipeline.
 Therefore, the cost-intensive input operations are reduced to a minimum.
@@
 \section{Building an End-user Analysis \label{section_artus_analysis}}
-\todo[inline]{If I wouldn't know the structure already, the following part wouldn't have helped my.
-Either we support it with a drawing and more detailled explanations or we just refer to a readme...
+\todo[inline]{If I would not know the structure already, the following part would not have helped my.
+Either we support it with a drawing and more detailed explanations or we just refer to a readme...
 Maybe rewrite parts of this section}
@@
 The most important part of an analysis are the processors.
-The abstract processors of the \artus core need to be implemented to realise the physics needs of the analysis in the form of code.
+The abstract processors of the \artus core need to be implemented to realize the physics needs of the analysis in the form of code.
 New processors have to be registered in the factory.
@@
 Analyses that share the input file format can easily also share processors, that implement basic analysis steps in a general fashion.
-Analysis-specific parts can either derive from existing processor classer or be modelled in new processors.
+Analysis-specific parts can either derive from existing processor classer or be modeled in new processors.
 
@@
 First, the sequence of modules to be executed is determined.
-These modules are then initialised and can define additional arguments needed for their configuration, such that every module can manage its own settings but can also access the settings of the entire program.
+These modules are then initialized and can define additional arguments needed for their configuration, such that every module can manage its own settings but can also access the settings of the entire program.
 After all arguments are defined, the configuration is parsed a second time providing the full settings for the HarryPlotter run.
@@
 
-Currently, the \artus framework is used for various user analysas of CMS data, ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model.
+Currently, the \artus framework is used for various user analyses of CMS data, ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model.
 As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis are explained in the following.
@@
 The $\PH\to\Pgt\Pgt$ analysis makes use of skimmed data sets in the Kappa format.
-The Kappa framework\footnote{\url{https://github.com/KappaAnalysis/Kappa}} is designed for skimming CMS data into small n-tuples that can be analysed independently of the CMSSW software.
+The Kappa framework\footnote{\url{https://github.com/KappaAnalysis/Kappa}} is designed for skimming CMS data into small n-tuples that can be analyzed independently of the CMSSW software.
 The only dependence is the ROOT framework.
@@
 
-A large part of the \artus software is specialised on the analysis of Kappa n-tuples\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/KappaAnalysis}}.
+A large part of the \artus software is specialized on the analysis of Kappa n-tuples\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/KappaAnalysis}}.
 An event provider is available for reading Kappa n-tuples.
@@
 Main producers are the ones for the identification and the selection of valid leptons and jets.
-Further producers perform the matching with trigger or generator objects and perform the splitting into decay channels or the categorisation.
+Further producers perform the matching with trigger or generator objects and perform the splitting into decay channels or the categorization.
 Also the mass reconstruction is done in a separate producer.
@@
 
-The outputs are flat n-tuples suitable for performing the background modelling step done in HarryPlotter.
+The outputs are flat n-tuples suitable for performing the background modeling step done in HarryPlotter.
 Histograms are read while cuts for the final event selection are applied.
-As an example, the cut on the transverse mass is applied on this level because events from control regions needed to be preserved for the background modelling step.
+As an example, the cut on the transverse mass is applied on this level because events from control regions needed to be preserved for the background modeling step.
 For each background process, an analysis module has been developed performing the estimation of the samples.
@@
 The modular and structured manner, in which the processing required for an analysis, can be expressed within the \artus framework, allowed the involved research groups to share and re-use source code on a scale not possible before.
-The concept underlying the \artus framework also enabled us to share program code between analysis and even across different universities and research centres.
+The concept underlying the \artus framework also enabled us to share program code between analysis and even across different universities and research centers.
 

### 2015-09-23 Core/doc/latex/paper.tex
paper.tex: better description environments

@@
 Based on the workflow described in the previous section, the following demands for an analysis framework arise:
-\subsection{Performance}
+
+\begin{description}
+\item[Performance:]
 The main performance indicator is the \emph{turnaround time}, which means the time that is needed to run the whole analysis in case new requirements arise.
@@
 This explains the need for a modular structure, where only those parts of the code are executed that really are necessary for the analysis.
-\subsection{Maintainability}
+
+\item[Maintainability:]
 Source code maintenance, i.e.
@@
 
-\subsection{Reliability}
+\item[Reliability:]
 In most cases, analyses never leave prototype status.
@@
 Also, if possible, existing and well-established libraries of the HEP community are interfaced.
+\end{description}
 
@@
 \begin{description}
-\item[Modular structure] Analysis steps are implemented in processors, breaking down the complete analysis in well-defined and easily understandable and writable parts.
-\item[Re-utilization of code] Processors can be shared among different analysis groups.
+\item[Modular structure:] Analysis steps are implemented in processors, breaking down the complete analysis in well-defined and easily understandable and writable parts.
+\item[Re-utilization of code:] Processors can be shared among different analysis groups.
 Every user contributes to the testing of existing code and improves the confidence in this code.
-\item[Configurability] Each module uses settings that are read from the the configuration.
+\item[Configurability:] Each module uses settings that are read from the the configuration.
 Each pipeline is mapped to a separate sub-set of the configuration.
-\item[High performance] The concept of pipelines allows to analyze the data with different configurations at the same time, while the data is only read in only once and common processing steps are shared in the global pipeline.
+\item[High performance:] The concept of pipelines allows to analyze the data with different configurations at the same time, while the data is only read in only once and common processing steps are shared in the global pipeline.
 Therefore, the cost-intensive input operations are reduced to a minimum.

### 2015-09-23 Utility/scripts/compareRootFiles.py
Allow negligible differences in file compare
Otherwise we have to many false positives in checks

@@ -284,7 +284,8 @@ def compareNtuple(directory1, directory2, ntupleID):
 		ntuple1.GetEntry(n)
 		ntuple2.GetEntry(n)
 		for i in range(nleaves1):
-			if leaves1.UncheckedAt(i).GetValue() != leaves2.UncheckedAt(i).GetValue():
+			value2 = leaves2.UncheckedAt(i).GetValue() or 1e-9
+			if (leaves1.UncheckedAt(i).GetValue() - leaves2.UncheckedAt(i).GetValue()) / value2 > 1e-6:
 				log.critical("different leaf value: " + str(leaves1.UncheckedAt(i).GetValue()) + ", " + str(leaves2.UncheckedAt(i).GetValue()) + " for name " + leaves1.UncheckedAt(i).GetName())
 				if leaves1.UncheckedAt(i).GetValue() != 0:
 					# save relative difference between the two leaves

### 2015-09-23 Core/doc/latex/paper.tex
paper.tex: added top/bottom rule to table
paper.tex: one sentence per line for better version control
Complement labels and fix warnings

@@
 \usepackage{palatino}
-\usepackage[hidelinks=true,bookmarks=true,plainpages=false]{hyperref}
+\usepackage[hidelinks,bookmarks=true,plainpages=false]{hyperref}
 \usepackage[colorinlistoftodos,prependcaption]{todonotes}
@@
 
-\section{Common Workflow of High Energy Physics Analyses \label{section_artus_analysis_workflow}}
+\section{Common Workflow of High Energy Physics Analyses}
+\label{section_artus_analysis_workflow}
 % This section should contain a short description of a HEP/CMS-typical workflow.
@@
 
-\section{Requirements and Challenges for Analysis Software\label{section_artus_challenges}}
+\section{Requirements and Challenges for Analysis Software}
+\label{section_artus_challenges}
 %define requirements based on previous section, following sections: describe how they are fullfilled
@@
 \item[Maintainability:]
-Source code maintenance, i.e.
-to be up-to-date with the latest requirements while not losing backwards compatibility, is a challenge for each software project.
+Source code maintenance, i.e.\ to be up-to-date with the latest requirements while not losing backwards compatibility, is a challenge for each software project.
 The first important step is to always have  an updated recipe that works out of the box on each machine offering CVMFS.
@@
 In most cases, analyses never leave prototype status.
-This leads to frequent re-implementations and low trust in reliability.
+This leads to frequent re-imple\-men\-ta\-tions and low trust in reliability.
 \artus allows the re-use of analysis code due to its modular structure as well as sharing it between different analysis groups, and therefore improving code quality significantly.
@@
 
-\section{The \artus Framework \label{section_artus_motivation}}
+\section{The \artus Framework}
+\label{section_artus_motivation}
 
@@
 
-\section{Structure of the Framework \label{section_artus_structure}}
+\section{Structure of the Framework}
+\label{section_artus_structure}
 
@@
 -> Should we put this part into a dedicated section directly after this one?
-I think the idea was to explain how certain design decisions, e.g. pipelines, achieve the \artus design goals.
+I think the idea was to explain how certain design decisions, e.g.\ pipelines, achieve the \artus design goals.
 Therefore it should not be too far from the technical descriptions.
 }
-This structure extends the established concepts of existing frameworks like FWLite~\cite{FWLite} from CMSSW to the following four main advantages:
+This structure extends the established concepts of existing frameworks like FWLite from CMSSW to the following four main advantages:
 \begin{description}
@@
 
-\section{Building an End-user Analysis \label{section_artus_analysis}}
+\section{Building an End-user Analysis}
+\label{section_artus_analysis}
 \todo[inline]{If I would not know the structure already, the following part would not have helped my.
@@
 
-\section{HarryPlotter -- Python Post-processing Framework \label{section_artus_harryplotter}}
+\section{HarryPlotter -- Python Post-processing Framework}
+\label{section_artus_harryplotter}
 
@@
 
-\section{A Real World Application -- the $\PH\to\Pgt\Pgt$ Analysis \label{section_artus_example_htt}}
+\section{\texorpdfstring{A Real World Application -- the $\PH\to\Pgt\Pgt$ Analysis}{A Real World Application - the H to Tau Tau Analysis}}
+\label{section_artus_example_htt}
 
@@
 \begin{tabular}{lrr}
+\toprule
 \textbf{Pipelines}                                & \textbf{Runtime / \minute} & \textbf{Event Rate / \reciprocal\second} \\ \midrule
@@
  4 ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$, $\Pgt\Pgt$) & 10:01                            & 758 \\
+\bottomrule
 \end{tabular}
@@
 \section{Conclusion}
+\label{section_conclusion}
 % what Artus does

### 2015-10-08 Core/doc/latex/figures/analysis_steps.tex

\begin{tikzpicture}[scale=1.0]
% horizontal axis
\draw[->] (0,0) -- (10,0) node[anchor=north] {};
% vertical axis
\draw[blue,->] (0,0) -- (0,4) node[anchor=east] {File size};
\draw[red,->] (10,0) -- (10,4) node[anchor=east] {Number of iterations};
% file size
\draw[blue,domain=0:10] plot (\x,{4*exp(-\x/2)});
\draw[red,domain=0:10] plot (\x,{4*exp((\x-10)/2)});
% labels
\draw	(0,0) node[anchor=north] {AOD}
		(2.5,0) node[anchor=north] {miniAOD}
		(5,0) node[anchor=north] {Skim}
		(7.5,0) node[anchor=north] {N-Tuple}
		(10,0) node[anchor=north] {Histogram};
\end{tikzpicture}

### 2015-10-08 Core/doc/latex/figures/analysis_steps.tex

@@
 % horizontal axis
-\draw[->] (0,0) -- (10,0) node[anchor=north] {};
+\draw[thick, ->] (0.7,0) -- (9.3,0) node[anchor=north] {};
 % vertical axis
-\draw[blue,->] (0,0) -- (0,4) node[anchor=east] {File size};
-\draw[red,->] (10,0) -- (10,4) node[anchor=east] {Number of iterations};
+\draw[KIT_gruen_1,->] (0,0) -- (0,4) node[anchor=south] {File size /$\mathrm{MB}$};
+
+\foreach \y/\ytext in {1/0,2/3, 3/6}
+\draw[KIT_gruen_1,shift={(0,\y)}] (2pt,0pt)  node[left] {$10^\ytext$};
+
+\filldraw[KIT_gruen_1] (0.3,3.11) circle(.05cm) node[black,anchor=south west]{EDM};
+\filldraw[KIT_gruen_1] (3.3,2.269) circle(.05cm) node[black, anchor=west]{Kappa};
+\filldraw[KIT_gruen_1] (6.6,1.03) circle(.05cm) node[black, anchor=south west]{N-Tuple};
+\filldraw[KIT_gruen_1] (9.7,0) circle(.05cm) node[black, anchor=north]{Plot};
+
+\draw[KIT_rot_1,->] (10,0) -- (10,4) node[anchor=south] {Turnarounds /h};
+\foreach \y/\ytext in {1/-1,2/1, 3/3}
+\draw[left,KIT_rot_1, shift={(0,\y)}, anchor=east] (11cm,0pt)  node[left] {\hfill$10^{\ytext}$};
+
+\filldraw[KIT_rot_1] (1.65,0.66) circle(.05cm) node[black, anchor=west]{Skim};
+\filldraw[KIT_rot_1] (5,1.65) circle(.05cm) node[black, anchor=north]{Analysis};
+\filldraw[KIT_rot_1] (8.3,3.08) circle(.05cm) node[black, anchor=south]{Plotting};
 % file size
-\draw[blue,domain=0:10] plot (\x,{4*exp(-\x/2)});
-\draw[red,domain=0:10] plot (\x,{4*exp((\x-10)/2)});
+\draw[KIT_rot_1,->,thick] (0.5,0.3) -- (9.5,3.3) ;
+\draw[KIT_gruen_1,->,thick] (.5,3.1) -- (9.5,0.2) ;
+
 % labels
-\draw	(0,0) node[anchor=north] {AOD}
-		(2.5,0) node[anchor=north] {miniAOD}
-		(5,0) node[anchor=north] {Skim}
-		(7.5,0) node[anchor=north] {N-Tuple}
-		(10,0) node[anchor=north] {Histogram};
+\draw (5,0) node[anchor=north] {Analysis Progress};
 \end{tikzpicture}

### 2015-10-08 Core/doc/latex/paper.tex

--- 2015-09-23 Core/doc/latex/paper.tex
@@
 -> Should we put this part into a dedicated section directly after this one?
-I think the idea was to explain how certain design decisions, e.g. pipelines, achieve the \artus design goals.
+I think the idea was to explain how certain design decisions, e.g.\ pipelines, achieve the \artus design goals.
 Therefore it should not be too far from the technical descriptions.

### 2015-10-08 HarryPlotter/python/input_modules/inputinteractive.py
enabled custom binning for InputInteractive thanks to Thomas

@@ -42,6 +42,11 @@ class InputInteractive(inputbase.InputBase):
 			except:
 				return input_string
 		
+		for key in ["x_bins", "y_bins", "z_bins"]:
+			for index, binning in enumerate(plotData.plotdict[key]):	
+				if (not binning is None) and (len(binning) > 1):
+					plotData.plotdict[key][index] = [float(bin_edge) for bin_edge in binning]
+		
 		# parse values/errors to plot
 		values_keys = ["x_expressions", "y_expressions", "z_expressions"]
 		errors_keys = ["x_errors", "y_errors", "z_errors"]

### 2015-10-08 HarryPlotter/python/utility/roottools.py

@@ -412,7 +412,6 @@ class RootTools(object):
 		"""
 		Create an empty ROOT histogram with a given binning
 		"""
-		
 		# prepare unique histogram name
 		if name == None:
 			name = "histogram_{0}".format(hashlib.md5("_".join([str(x_bins), str(y_bins), str(z_bins), str(profile_histogram)])).hexdigest())
@@ -422,7 +421,7 @@ class RootTools(object):
 		if isinstance(x_bins, basestring) or ((len(x_bins) == 1) and isinstance(x_bins[0], basestring)):
 			x_binning_string, x_bin_edges = RootTools.prepare_binning(x_bins[0])
 		else:
-			x_bin_edges = x_bins
+			x_bin_edges = array.array('d', x_bins)
 		
 		y_bin_edges = None
 		if not y_bins is None:

### 2015-10-08 Configuration/python/artusWrapper.py
artusWrapper.py: better default for wall time

@@ -361,7 +361,7 @@ class ArtusWrapper(object):
 		                                 help="Files per batch job. [Default: %(default)s]")
 		runningOptionsGroup.add_argument("--area-files", default=None,
 		                                 help="Additional area files. [Default: %(default)s]")
-		runningOptionsGroup.add_argument("--wall-time", default="02:00:00",
+		runningOptionsGroup.add_argument("--wall-time", default="24:00:00",
 		                                 help="Wall time of batch jobs. [Default: %(default)s]")
 		runningOptionsGroup.add_argument("--memory", type=int, default=3000,
 		                                 help="Memory (in MB) for batch jobs. [Default: %(default)s]")

### 2015-10-13 KappaAnalysis/interface/KappaProduct.h
*CorrectionsProducer: added mapping from corrected object to original object

@@ -64,7 +64,10 @@ public:
 	/// added by TauEnergyCorrectionProducer
 	// needs to be a shared_ptr in order to be deleted when the product is deleted
 	std::vector<std::shared_ptr<KTau> > m_correctedTaus;
-
+	
+	/// added by <Lepton>CorrectionProducers
+	std::map<const KLepton*, const KLepton*> m_originalLeptons; // key: corrected, value: original
+	
 	/// added by ValidTausProducer
 	std::vector<KTau*> m_validTaus;
 	std::vector<KTau*> m_invalidTaus;
@@ -76,6 +79,7 @@ public:
 	/// added by JetEnergyCorrectionProducer
 	std::vector<std::shared_ptr<KBasicJet> > m_correctedJets;
 	std::vector<std::shared_ptr<KJet> > m_correctedTaggedJets;
+	std::map<const KBasicJet*, const KBasicJet*> m_originalJets; // key: corrected, value: original
 	
 	/// added by ValidJetsProducer
 	std::vector<KBasicJet*> m_validJets;

### 2015-10-13 KappaAnalysis/src/Producers/TauCorrectionsProducer.cc

@@ -24,6 +24,7 @@ void TauCorrectionsProducer::Produce(KappaEvent const& event, KappaProduct& prod
 		 tau != event.m_taus->end(); ++tau)
 	{
 		product.m_correctedTaus[tauIndex] = std::shared_ptr<KTau>(new KTau(*tau));
+		product.m_originalLeptons[product.m_correctedTaus[tauIndex].get()] = &(*tau);
 		++tauIndex;
 	}
 	

### 2015-10-14 Core/doc/latex/paper.tex
Paper: First easy to fix issues we discussed

--- 2015-09-23 Core/doc/latex/paper.tex
@@
 \begin{abstract}
-We present \artus, an event-based data-processing framework for high energy physics experiments.
-\mbox{\artus} is designed for large-scale data analysis in a collaborative environment.
+\artus is an event-based data-processing framework for high energy physics experiments.
+It is designed for large-scale data analysis in a collaborative environment.
 The architecture design choices take into account typical challenges and are based on experiences with similar applications.
@@
 An example use case and performance measurements are presented.
-The framework is well-tested and successfully used by several analysis groups.\todo[inline]{Mention them, maybe with publications?
--> mentioned at the beginning of Htt chapter.
-Do we have publications?}
+The framework is well-tested and successfully used by several analysis groups.
 \end{abstract}
@@
 
-\section{Common Workflow of High Energy Physics Analyses}
+\section{Typical Workflow of High Energy Physics Analyses}
 \label{section_artus_analysis_workflow}
@@
 
-Between the data taking at the detector or the generation of simulated events with the subsequent detector simulation and the showcasing of the physical results, the following analysis steps have shown to be the best compromise in terms of turnaround time and efficiency as explained in Figure \ref{figure_analysis_steps}.
+Between the data taking at the detector or the generation of simulated events with the subsequent detector simulation and the presentation of the physical results, the following analysis steps have shown to be the best compromise in terms of turnaround time and efficiency as explained in Figure \ref{figure_analysis_steps}.
 
-The reconstruction of the raw data coming from the experiments is performed on large computing centers organized into the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing Grid.
+The reconstruction of the raw data coming from the experiments is performed on large computing centers organized in the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing Grid.
 The resulting datasets contain event information and high-level physics objects and are of $\mathcal O(10-100)$~TB in size.
@@
 
-Source code and configuration files have become the most precise form of documentation.
+Source code and configuration files have become the most precise form of description.
 Therefore, readability also for people who have not written the code is crucial.
@@
 
-Following the structure of the CMSSW \todo[inline]{Referenz?
+Following the structure of the CMSSW~\cite{cmssw} \todo[inline]{Referenz?
 zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
@@
 It is generalized and extended to satisfy the needs of various analysis groups.
-The structure is illustrated in figure~\ref{figure_artus_structure}.
+The structure is illustrated in Figure~\ref{figure_artus_structure}.
 
@@
 Then, the execution is split up into multiple so-called local pipelines, that are also processed sequentially.
-The composition of a pipeline is illustrated in figure~\ref{figure_artus_pipeline}.
+The composition of a pipeline is illustrated in Figure~\ref{figure_artus_pipeline}.
 
@@
 Each pipeline is mapped to a separate sub-set of the configuration.
-\item[High performance:] The concept of pipelines allows to analyze the data with different configurations at the same time, while the data is only read in only once and common processing steps are shared in the global pipeline.
+\item[High performance:] The concept of pipelines allows to analyze the data with different configurations at the same time, while the data is read in only once and common processing steps are shared in the global pipeline.
 Therefore, the cost-intensive input operations are reduced to a minimum.
@@
 The abstract processors of the \artus core need to be implemented to realize the physics needs of the analysis in the form of code.
-New processors have to be registered in the factory.
 After the basic structure of an analysis is set up, most changes and additions are only related to the processors.
@@
 
-\section{HarryPlotter -- Python Post-processing Framework}
+\section{HarryPlotter -- A Python Framework for Post-processing}
 \label{section_artus_harryplotter}
@@
 
-Table~\ref{table_artus_runtime_comparison} shows a runtime measurement for the baseline part of the $\PH\to\Pgt\Pgt$ in the four main channels ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$ and $\Pgt\Pgt$).
+Table~\ref{table_artus_runtime_comparison} shows a runtime measurement for the baseline part of the $\PH\to\Pgt\Pgt$ in the four main decay channels ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$ and $\Pgt\Pgt$).
 It illustrates the main advantage of the \artus structure: sub-analyses with different sets of configurations can be performed in the same run avoiding the multiple IO overhead when the configurations would be performed sequentially in different runs.
@@
 The \artus analysis framework presented in this paper offers a comprehensive and well-integrated solution for event-based data analyses in the HEP domain.
-In conjunction with the plotting toolkit HarryPlotter, all data analysis needs are covered.
+In conjunction with the post-processing toolkit HarryPlotter, all data analysis needs are covered.
 

### 2015-10-15 Configuration/scripts/createInputFilelists.py
createInputFilelists: adapt to different dir structure of Crab skims

@@ -31,6 +31,8 @@ def main():
 	                    help="Output directory for the filelists. [Default: %(default)s]")
 	parser.add_argument("-r", "--create-recent-symlinks", default=False, action="store_true",
 	                    help="Create symlinks to filelists as recent ones. [Default: %(default)s]")
+	parser.add_argument("-c", "--crab", default=False, action="store_true",
+	                    help="Skimming output directory was created by Crab (it has a different structure). [Default: %(default)s]")
 
 	args = parser.parse_args()
 	logger.initLogger(args)
@@ -46,6 +48,15 @@ def main():
 	for skimming_dir in skimming_dirs:
 		nick = os.path.basename(skimming_dir)
 		files = sorted(glob.glob(os.path.join(skimming_dir, "*.root")))
+
+		if args.crab:			
+			nick = os.path.basename(glob.glob(os.path.join(skimming_dir, "crab_*"))[0]).strip("crab_")
+			files = sorted(glob.glob(os.path.join(skimming_dir, "crab_*/*/*/*.root")))
+
+		if (len(files) == 0):
+			log.critical("Input file list empty. If the skims have been produced with Crab, switch on the --crab option")
+			sys.exit(1)
+
 		filelists = os.path.join(args.output_dir, "%s_sample_%s_%s.txt" % ("%s", nick, "%s"))
 		
 		dcache_settings = {

### 2015-10-23 HarryPlotter/python/input_modules/inputroot.py
HarryPlotter: additional debug output for list expansion

@@ -76,7 +76,7 @@ class InputRoot(inputfile.InputFile):
 		else:
 			plotData.plotdict["friend_trees"] = [None]
 
-		self.prepare_list_args(plotData, ["nicks", "x_expressions", "y_expressions", "z_expressions", "x_bins", "y_bins", "z_bins", "scale_factors", "files", "directories", "folders", "weights", "friend_trees", "tree_draw_options"])
+		self.prepare_list_args(plotData, ["nicks", "x_expressions", "y_expressions", "z_expressions", "x_bins", "y_bins", "z_bins", "scale_factors", "files", "directories", "folders", "weights", "friend_trees", "tree_draw_options"], help="InputRoot options")
 		inputbase.InputBase.prepare_nicks(plotData)
 		
 		plotData.plotdict["folders"] = [folders.split() if folders else [""] for folders in plotData.plotdict["folders"]]

### 2015-10-23 HarryPlotter/python/plotbase.py

@@ -198,7 +198,8 @@ class PlotBase(processor.Processor):
 			plotData.plotdict["labels"] = plotData.plotdict["nicks"]
 		
 		self.prepare_list_args(plotData, ["nicks", "colors", "labels", "markers", "line_styles", "line_widths"],
-				n_items = max([len(plotData.plotdict[l]) for l in ["nicks", "stacks"] if plotData.plotdict[l] is not None]))
+				n_items = max([len(plotData.plotdict[l]) for l in ["nicks", "stacks"] if plotData.plotdict[l] is not None]),
+				help="Plotting style options")
 		# stacks are expanded by appending None's
 		plotData.plotdict["stacks"] = plotData.plotdict["stacks"]+[None]*(len(plotData.plotdict["nicks"])-len(plotData.plotdict["stacks"]))
 		
@@ -239,7 +240,7 @@ class PlotBase(processor.Processor):
 
 		# prepare arguments for text label(s)
 		if plotData.plotdict["texts"] is not None:
-			self.prepare_list_args(plotData, ["texts", "texts_y", "texts_x", "texts_size"])
+			self.prepare_list_args(plotData, ["texts", "texts_y", "texts_x", "texts_size"], help="texts for plotting")
 			if len(plotData.plotdict["texts"]) == 1 and plotData.plotdict["texts"][0] is None:
 				plotData.plotdict["texts"] = []
 				plotData.plotdict["texts_x"] = []

### 2015-10-23 HarryPlotter/python/plot_modules/plotroot.py
plotroot.py: added option --x-rel-lims

@@ -65,11 +65,13 @@ class PlotRoot(plotbase.PlotBase):
 		
 		self.axis_options.add_argument("--x-lims", type=float, nargs="+",
 		                               help="Lower and Upper limit for x-axis.")
+		self.axis_options.add_argument("--x-rel-lims", type=float, nargs=2, default=[1.0, 1.0],
+		                               help="Relative lower and upper margin for auto x-lims. [Default: %(default)s]")
 		self.axis_options.add_argument("--sym-x-lims", nargs="?", type="bool", default=False, const=True,
 		                               help="Symmetric x-axis limits of the plot. The parameters of --x-lims are taken as <center> <range/2>")
 		self.axis_options.add_argument("--y-lims", type=float, nargs="+",
 		                               help="Lower and Upper limit for y-axis.")
-		self.axis_options.add_argument("--rel-y-lims", type=float, nargs=2,
+		self.axis_options.add_argument("--rel-y-lims", type=float, nargs=2, # TODO: should be renamed into --y-rel-lims for consistency reasons
 		                               help="Relative lower and upper margin for auto y-lims. [Default: [0.9, 1.1] for lin. y-axis and [0.5, 2.0] for log. y-axis.]")
 		self.axis_options.add_argument("--sym-y-lims", nargs="?", type="bool", default=False, const=True,
 		                               help="Symmetric y-axis limits of the plot. The parameters of --y-lims are taken as <center> <range/2>")
@@ -319,11 +321,17 @@ class PlotRoot(plotbase.PlotBase):
 				self.x_min = plotData.plotdict["x_lims"][0] - plotData.plotdict["x_lims"][1]
 				self.x_max = plotData.plotdict["x_lims"][0] + plotData.plotdict["x_lims"][1]
 			else:
+				tmp_x_min = self.x_min * plotData.plotdict["x_rel_lims"][0]
+				tmp_x_max = self.x_max * plotData.plotdict["x_rel_lims"][1]
+				
 				if not plotData.plotdict["x_lims"] is None:
 					center = plotData.plotdict["x_lims"][0]
-					width = max([abs(x - center) for x in [self.x_min, self.x_max]])
+					width = max([abs(x - center) for x in [tmp_x_min, tmp_x_max]])
 					self.x_min = center - width
 					self.x_max = center + width
+				else:
[…]

### 2015-10-23 Core/doc/latex/paper.tex
Paper: Further changes after discussion

@@
 \usepackage{hepnames}
-\usepackage{hepunits}
+\usepackage{siunitx}
 \usepackage{url}
@@
 \begin{frontmatter}
-\title{\artus -- Framework for Event-based Data Analysis in High Energy Physics}
+\title{\artus{} -- Framework for Event-based Data Analysis in High Energy Physics}
 
+\author{Joram Berger}
 \author{Fabio Colombo}
@@
 The workflow of the experiments collecting data at the Large Hadron Collider (LHC) at CERN is taken as an example to illustrate the organization and needs of a modern High Energy Physics (HEP) analysis.
-Still, equal or very similar requirements are also present for HEP experiments not located at the LHC.
+Nonetheless, equal or very similar requirements are also present for HEP experiments not located at the LHC.
 
@@
 
-The reconstruction of the raw data coming from the experiments is performed on large computing centers organized in the WLCG\footnote{\url{http://wlcg-public.web.cern.ch}}, the Worldwide LHC Computing Grid.
-The resulting datasets contain event information and high-level physics objects and are of $\mathcal O(10-100)$~TB in size.
-\todo[inline]{move file size numbers to Figure \ref{figure_analysis_steps}?}
+The reconstruction of the raw data coming from the experiments is performed on large computing centers organized in the Worldwide LHC Computing Grid (WLCG)~\cite{wlcg}.
+The resulting datasets contain event information and high-level physics objects and are in the order of \SI{100}{TB} in size.
 
@@
 The output of the skimming process is an analysis-dependent file, usually in an n-tuple format, and small enough to be stored on local file servers, often owned and operated by a single institute.
-The size of these files ranges from $\mathcal O(10)$~GB to few~TB.
+The size of these files ranges from several \SI{10}{GB} to few~TB.
 
@@
 }
-This structure extends the established concepts of existing frameworks like FWLite from CMSSW to the following four main advantages:
+This structure extends the established concepts of existing frameworks~\cite{cmssw} to the following four main advantages:
 \begin{description}
-\item[Modular structure:] Analysis steps are implemented in processors, breaking down the complete analysis in well-defined and easily understandable and writable parts.
-\item[Re-utilization of code:] Processors can be shared among different analysis groups.
+\item[Modular structure] Analysis steps are implemented in processors, breaking down the complete analysis in well-defined and easily understandable and writable parts.
+\item[Re-utilization of code] Processors can be shared among different analysis groups.
 Every user contributes to the testing of existing code and improves the confidence in this code.
-\item[Configurability:] Each module uses settings that are read from the the configuration.
-Each pipeline is mapped to a separate sub-set of the configuration.
-\item[High performance:] The concept of pipelines allows to analyze the data with different configurations at the same time, while the data is read in only once and common processing steps are shared in the global pipeline.
+\item[Configurability] Each module uses settings which are read from the the configuration.
+A separate sub-set of the configuration is created for each pipeline.
+\item[High performance] The concept of pipelines allows to analyze the data with different configurations at the same time, while the data is read in only once and common processing steps are shared in the global pipeline.
 Therefore, the cost-intensive input operations are reduced to a minimum.
@@
 \toprule
-\textbf{Pipelines}                                & \textbf{Runtime / \minute} & \textbf{Event Rate / \reciprocal\second} \\ \midrule
+\textbf{Pipelines}                                & \textbf{Runtime / \si{min}} & \textbf{Event Rate / \si{s^{-1}} } \\ \midrule
 %0                                                & 5:53                             & 1296 \\

### 2015-10-23 HarryPlotter/python/plot_modules/plotroot.py
plotroot.py: added --right-pad-margin option

@@ -90,8 +90,10 @@ class PlotRoot(plotbase.PlotBase):
 		self.axis_options.add_argument("--reverse-z-axis", nargs="?", type="bool", default=False, const=True,
 		                               help="Reverse Z axis labelling. [Default: %(default)s]")
 		
-		self.canvas_options.add_argument("--left-pad-margin", nargs=1, type=float, default=None,
-		                               help="Left margin of pad. [Default: %(default)s]")
+		self.canvas_options.add_argument("--left-pad-margin", type=float, default=None,
+		                               help="Left margin of pad. [Default: automatically determined]")
+		self.canvas_options.add_argument("--right-pad-margin", type=float, default=None,
+		                               help="Right margin of pad. [Default: automatically determined]")
 		
 		self.formatting_options.add_argument("-C", "--colors", type=str, nargs="+",
 		                                     help="Colors for the plots. For each plot up to two colors (whitespace separated) can be specified, the first for lines and markers and the second for filled areas.")
@@ -257,7 +259,9 @@ class PlotRoot(plotbase.PlotBase):
 		self.plot_pad_right_margin = plot_pad.GetRightMargin()
 		plot_pad.SetRightMargin(0.25)
 		if not plotData.plotdict["left_pad_margin"] is None:
-			plot_pad.SetLeftMargin(plotData.plotdict["left_pad_margin"][0])
+			plot_pad.SetLeftMargin(plotData.plotdict["left_pad_margin"])
+		if not plotData.plotdict["right_pad_margin"] is None:
+			plot_pad.SetRightMargin(plotData.plotdict["right_pad_margin"])
 		if not subplot_pad is None:
 			subplot_pad.SetRightMargin(0.25)
 		
@@ -622,7 +626,7 @@ class PlotRoot(plotbase.PlotBase):
 			self.subplot_axes_histogram.GetYaxis().SetTitleOffset(self.subplot_axes_histogram.GetYaxis().GetTitleOffset() * self.plot_subplot_slider_y)
 			self.subplot_axes_histogram.GetYaxis().SetNdivisions(5, 0, 0)
 		
-		if all([isinstance(root_object, ROOT.TF1) or (root_object.GetListOfFunctions().FindObject("palette") == None) for root_object in plotData.plotdict["root_objects"].values()]):
[…]

### 2015-10-26 HarryPlotter/python/plot_modules/plotmpl.py
Modified y_rel_lims, moved to plotbase

@@ -78,6 +78,7 @@ class PlotMpl(plotbase.PlotBase):
 		self.set_matplotlib_defaults()
 		self.nicelabels = labels.LabelsDict()
 		self.default_linestyles = ['--', '-.', ':', '-']
+		self.rel_y_lim_default['lin']=[0.9, 1.2]
 
 
 	def modify_argument_parser(self, parser, args):
@@ -107,6 +108,7 @@ class PlotMpl(plotbase.PlotBase):
 
 		self.formatting_options.set_defaults(legend="upper right")
 		self.formatting_options.set_defaults(colormap="afmhot")
+
 
 	def prepare_args(self, parser, plotData):
 		super(PlotMpl, self).prepare_args(parser, plotData)
@@ -138,6 +140,10 @@ class PlotMpl(plotbase.PlotBase):
 					plotData.plotdict["markers"][index] = "."
 				else:
 					plotData.plotdict["markers"][index] = "fill"
+					
+		# defaults for axis ranges
+		if plotData.plotdict["y_rel_lims"] is None:
+			plotData.plotdict["y_rel_lims"] = [0.5, 2.0] if plotData.plotdict["y_log"] else [0.9, 1.2]
 
 		# set default colors depending whether there are markers or bars
 		i_marker, i_bar = 0, 0
@@ -372,7 +378,7 @@ class PlotMpl(plotbase.PlotBase):
 					else:
 						ax.set_ylim(self.y_min)
 				if all("TH1" in obj.__class__.__name__ for obj in plotData.plotdict["root_objects"].values()):
-					ax.set_ylim(ymax=self.y_max * (2 if plotData.plotdict["y_log"] else 1.2))
+					ax.set_ylim(ymax=self.y_max * (plotData.plotdict["y_rel_lims"][1]))
 
 		# set log scale
 		for axis in ['x', 'y']:

### 2015-10-26 HarryPlotter/python/plot_modules/plotroot.py

@@ -71,8 +71,6 @@ class PlotRoot(plotbase.PlotBase):
 		                               help="Symmetric x-axis limits of the plot. The parameters of --x-lims are taken as <center> <range/2>")
 		self.axis_options.add_argument("--y-lims", type=float, nargs="+",
 		                               help="Lower and Upper limit for y-axis.")
-		self.axis_options.add_argument("--rel-y-lims", type=float, nargs=2, # TODO: should be renamed into --y-rel-lims for consistency reasons
-		                               help="Relative lower and upper margin for auto y-lims. [Default: [0.9, 1.1] for lin. y-axis and [0.5, 2.0] for log. y-axis.]")
 		self.axis_options.add_argument("--sym-y-lims", nargs="?", type="bool", default=False, const=True,
 		                               help="Symmetric y-axis limits of the plot. The parameters of --y-lims are taken as <center> <range/2>")
 		self.axis_options.add_argument("--z-lims", type=float, nargs="+",
@@ -189,10 +187,6 @@ class PlotRoot(plotbase.PlotBase):
 			plotData.plotdict["marker_styles"][index] = marker_style
 			plotData.plotdict["fill_styles"][index] = fill_style
 			plotData.plotdict["legend_markers"][index] = legend_marker
-		
-		# defaults for axis ranges
-		if plotData.plotdict["rel_y_lims"] is None:
-			plotData.plotdict["rel_y_lims"] = [0.5, 2.0] if plotData.plotdict["y_log"] else [0.9, 1.1]
 		
 		# defaults for legend position
 		if not plotData.plotdict["legend"] is None:
@@ -359,8 +353,8 @@ class PlotRoot(plotbase.PlotBase):
 				self.y_min = plotData.plotdict["y_lims"][0] - plotData.plotdict["y_lims"][1]
 				self.y_max = plotData.plotdict["y_lims"][0] + plotData.plotdict["y_lims"][1]
 			else:
-				tmp_y_min = self.y_min * ((plotData.plotdict["rel_y_lims"][0] if self.y_min > 0.0 else plotData.plotdict["rel_y_lims"][1]) if self.max_dim < 3 else 1.0)
[…]

### 2015-10-26 HarryPlotter/python/plotbase.py

@@ -29,6 +29,10 @@ class PlotBase(processor.Processor):
 		super(PlotBase, self).__init__()
 		
 		self.predefined_colors = None
+		self.rel_y_lim_default={
+			"lin":[0.9, 1.1],
+			"log":[0.5, 2.0],
+		}
 	
 	def modify_argument_parser(self, parser, args):
 		super(PlotBase, self).modify_argument_parser(parser, args)
@@ -56,6 +60,8 @@ class PlotBase(processor.Processor):
 		
 		self.axis_options.add_argument("--y-lims", type=float, nargs=2,
 		                               help="Lower and Upper limit for y-axis.")
+		self.axis_options.add_argument("--y-rel-lims", type=float, nargs=2,
+		                               help="Relative lower and upper margin for auto y-lims. [Default: [{}] for lin. y-axis and [{}] for log. y-axis.]".format(','.join([str(i) for i in self.rel_y_lim_default["lin"]]), ','.join([ str(i) for i in self.rel_y_lim_default["log"]]) ))
 		self.axis_options.add_argument("--y-subplot-lims", type=float, nargs=2,
 		                               help="Lower and Upper limit for y-axis of a possible subplot.")
 		self.axis_options.add_argument("--y-label", type=str, default="Events",
@@ -202,6 +208,11 @@ class PlotBase(processor.Processor):
 		self.prepare_list_args(plotData, ["nicks", "colors", "labels", "markers", "line_styles", "line_widths"],
 				n_items = max([len(plotData.plotdict[l]) for l in ["nicks", "stacks"] if plotData.plotdict[l] is not None]),
 				help="Plotting style options")
+		
+		# defaults for axis ranges
+		if plotData.plotdict["y_rel_lims"] is None:
+			plotData.plotdict["y_rel_lims"] = self.rel_y_lim_default[('log' if plotData.plotdict['y_log'] else 'lin')]
+		
 		# stacks are expanded by appending None's
 		plotData.plotdict["stacks"] = plotData.plotdict["stacks"]+[None]*(len(plotData.plotdict["nicks"])-len(plotData.plotdict["stacks"]))
 		

### 2015-10-27 HarryPlotter/python/plot_modules/plotmpl.py
plotmpl.py: fix y-axis-limits for 2D plots

@@ -373,8 +373,10 @@ class PlotMpl(plotbase.PlotBase):
 					else:
 						ax.set_ylim(ymin=self.y_min)
 				else:
-					if any("TH" in obj.__class__.__name__ for obj in plotData.plotdict["root_objects"].values()):
+					if any("TH1" in obj.__class__.__name__ for obj in plotData.plotdict["root_objects"].values()):
 						ax.set_ylim(0)
+					elif any("TH2" in obj.__class__.__name__ for obj in plotData.plotdict["root_objects"].values()):
+						ax.set_ylim(self.y_min, self.y_max)
 					else:
 						ax.set_ylim(self.y_min)
 				if all("TH1" in obj.__class__.__name__ for obj in plotData.plotdict["root_objects"].values()):

### 2015-10-27 Core/doc/latex/include/bib.tex
Paper: Further changes after discussion
Paper: More references

@@
  \begin{thebibliography}{99}
-
     \bibitem{joram_phd}Joram Berger,
@@
                         Fusion in the Decay Channel H $\to \tau \tau$},
-      CERN-THESIS-2014-092.
-
+      \href{https://cds.cern.ch/record/1747055}{\texttt{CERN-THESIS-2014-092}}.
+    \bibitem{cmssw}\url{https://github.com/cms-sw/cmssw}
+    \bibitem{root}
+      Rene Brun and Fons Rademakers, 
+      \emph{ROOT -- An Object Oriented Data Analysis Framework}, 
+      Proceedings AIHENP'96 Workshop, Lausanne, Sep. 1996, Nucl. Inst. \& Meth. in Phys. Res. A \textbf{389} (1997) 81--86. See also \url{http://root.cern.ch}.
+    \bibitem{cms}
+      CMS Collaboration,
+      \emph{The CMS Experiment at the CERN LHC},
+      JINST \textbf{3} (2008) S08004, 
+      \textsc{doi}: \href{http://dx.doi.org/10.1088/1748-0221/3/08/S08004}{\texttt{10.1088/1748-0221/3/08/S08004}},
+    \bibitem{wlcg}
+      \url{http://wlcg-public.web.cern.ch}.
 \end{thebibliography}

### 2015-10-27 Core/doc/latex/paper.tex
Paper: More references

@@
 
-Following the structure of the CMSSW~\cite{cmssw} \todo[inline]{Referenz?
-zumindest github-link?} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
+Following the structure of the CMSSW~\cite{cmssw} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
 The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.

### 2015-10-27 Core/doc/latex/paper.tex
Paper: Remove Artus details from general goals chapter

@@
 
-\todo[inline]{Should we drop CMS-specific technical terms like AOD/miniAOD?
-Maybe not put this figure on a dedicated page?}
-
 \section{Requirements and Challenges for Analysis Software}
@@
 \begin{description}
-\item[Performance:]
-The main performance indicator is the \emph{turnaround time}, which means the time that is needed to run the whole analysis in case new requirements arise.
-Since the runtime is often limited by the transfer speed of the storage servers, \artus is designed to load each event only once and perform all necessary processing steps.
-This is made possible with the pipelining concept.
+\item[Performance]
+The main performance indicator is the \emph{turnaround time} which is the time needed to run the whole analysis in case new requirements arise.
+Since the runtime is often limited by the transfer speed of the storage servers, the software should load each event only once and perform all necessary processing steps.
 Still, since analysis requirements sometimes change within a few hours, a high level of flexibility is needed.
-This explains the need for a modular structure, where only those parts of the code are executed that really are necessary for the analysis.
+This explains the need for a modular structure, where only those parts of the code are executed that are really necessary for the analysis.
 
-\item[Maintainability:]
+\item[Maintainability]
 Source code maintenance, i.e.\ to be up-to-date with the latest requirements while not losing backwards compatibility, is a challenge for each software project.
@@
 
-\artus has the built-in possibility to submit analysis jobs with grid-control, a job submission tool.
+%\artus has the built-in possibility to submit analysis jobs with grid-control, a job submission tool.
 
-\item[Reliability:]
+\item[Reliability]
 In most cases, analyses never leave prototype status.
@@
 
-\artus has no need to use multi-core techniques, since it can be parallelized trivially by splitting the input dataset and sending it to different computing instances.
-This is possible, because the processed events are know to be independent of each other.
+Multi-core techniques are not required since the processing can be trivially parallelized by splitting the input dataset and sending it to different computing instances.
+This is possible, because the processed events are known to be independent of each other.
 
@@
 
-\todo[inline]{I would not put the remaining part of this chapter here.
-It should be either part of the requirements or part of the summary what Artus does achieve; but in this technical part in between it feels misplaced
--> Should we put this part into a dedicated section directly after this one?
-I think the idea was to explain how certain design decisions, e.g.\ pipelines, achieve the \artus design goals.
-Therefore it should not be too far from the technical descriptions.
-}
 This structure extends the established concepts of existing frameworks~\cite{cmssw} to the following four main advantages:

### 2015-10-27 Core/doc/latex/paper.tex
Paper: Add ROOT reference
Paper: Different start of the end-user chapter

@@
 Consumers are executed after the chain of producers and filters.
-The output together with the complete configuration is written to a ROOT \todo[inline]{Referenz auf ROOT?} file.
+The output together with the complete configuration is written to a ROOT~\cite{root} file.
 These processors are created and managed by a dedicated factory according to the configuration.
@@
 \label{section_artus_analysis}
-\todo[inline]{If I would not know the structure already, the following part would not have helped my.
-Either we support it with a drawing and more detailed explanations or we just refer to a readme...
-Maybe rewrite parts of this section}
-In the \artus framework, each concrete analysis is defined by a set of object types.
-The analysis programmer must provide an implementation of the classes for settings, the event and the product class.
+In order to create a custom analysis, the analysis programmer can build his own code on the \artus classes by deriving from them.
+He must provide an implementation of the settings, the event and the product class.
 The settings class defines the tags that are read from the configuration file and the corresponding types of these values.
-The event class defines the event content which is read from the input and the product class contains members for new quantities calculated during the analysis stage.
+The \emph{event} class defines the event content which is read from the input and the product class contains members for new quantities calculated during the analysis stage.
 These three classes need to be derived from the base classes provided by the core of the \artus framework.
 
-An implementation of an event provider must be available.
+An implementation of an \emph{event provider} must be available.
 The event provider must know how to read event content from the input files and how to store them in the event object.
@@
 
-The most important part of an analysis are the processors.
+The most important part of an analysis are the \emph{processors}.
 The abstract processors of the \artus core need to be implemented to realize the physics needs of the analysis in the form of code.
@@
 Analyses that share the input file format can easily also share processors, that implement basic analysis steps in a general fashion.
-Analysis-specific parts can either derive from existing processor classer or be modeled in new processors.
+Analysis-specific parts can either derive from existing processor classes or be modeled in new processors.
 
@@
 These modules are then initialized and can define additional arguments needed for their configuration, such that every module can manage its own settings but can also access the settings of the entire program.
-After all arguments are defined, the configuration is parsed a second time providing the full settings for the HarryPlotter run.
-Then all processors are executed as described above.
 

### 2015-10-27 Core/doc/latex/paper.tex
Paper: Move table inside chapter
I think putting the table directly before the reference in the text
is acceptable, better than in the conclusion.
Paper: First figure caption

@@
 The data which are relevant for a specific analysis are selected in a step usually referred to as \textit{skimming}.
-The output of the skimming process is an analysis-dependent file, usually in an n-tuple format, and small enough to be stored on local file servers, often owned and operated by a single institute.
+The output of the skimming process is an analysis-dependent file\todo[inline]{better "format" instead of "file"?
+(needs restructuring of the sentence a bit}, usually in an n-tuple format, and small enough to be stored on local file servers, often owned and operated by a single institute.
 The size of these files ranges from several \SI{10}{GB} to few~TB.
@@
 \caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics, numbers taken from \cite{joram_phd}.
-Data size is reduced by six orders of magnitude, turnaround time by a factor of 4.
-I/O intensive operations are done in highly parallel in the WLCG.
-The data reduction is achieved by performing the data-intensive operations only rarely and applying sensible event selection steps as early as possible.}
+Data size is reduced by six orders of magnitude, the turnaround time by a factor of 10000.
+I/O intensive operations are done highly parallelized in the WLCG.
+The data reduction is achieved by performing the data-intensive operations only rarely and applying analysis specific event selection steps as early as possible.}
 \label{figure_analysis_steps}
@@
 \item[Performance]
-The main performance indicator is the \emph{turnaround time} which is the time needed to run the whole analysis in case new requirements arise.
+The main performance indicator is the \emph{turnaround time} which is the time needed to run the whole\todo[inline]{"entire" always better than "whole"?} analysis in case new requirements arise.
 Since the runtime is often limited by the transfer speed of the storage servers, the software should load each event only once and perform all necessary processing steps.
@@
 Source code maintenance, i.e.\ to be up-to-date with the latest requirements while not losing backwards compatibility, is a challenge for each software project.
-The first important step is to always have an updated recipe that works out of the box on each machine offering CVMFS.
+\todo[inline]{Didn't we agree to remove the following sentence?} The first important step is to always have an updated recipe that works out of the box on each machine offering CVMFS.
 To make the entry level as low as possible, beginners can start with an example analysis.
@@
 \artus respects the separation of code and configuration.
-Settings select what has to be done and with which parameters.
+Settings select\todo[inline]{better "specify" instead of "select"?} what has to be done and with which parameters.
 The code does perform these steps, ideally without the user being fully aware of implementation details.
@@
 First, a so-called global pipeline is run.
-Then, the execution is split up into multiple so-called local pipelines, that are also processed sequentially.
+Then,\todo[inline]{No comma here?} the execution is split up into multiple so-called local pipelines, that are also processed sequentially.
 The composition of a pipeline is illustrated in Figure~\ref{figure_artus_pipeline}.
@@
 He must provide an implementation of the settings, the event and the product class.
-The settings class defines the tags that are read from the configuration file and the corresponding types of these values.
+The settings class defines the tags that are read from the configuration file and the corresponding types of these values.\todo[inline]{better "and the types of the corresponding values"?}
 The \emph{event} class defines the event content which is read from the input and the product class contains members for new quantities calculated during the analysis stage.
@@
 
-Table~\ref{table_artus_runtime_comparison} shows a runtime measurement for the baseline part of the $\PH\to\Pgt\Pgt$ in the four main decay channels ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$ and $\Pgt\Pgt$).
-It illustrates the main advantage of the \artus structure: sub-analyses with different sets of configurations can be performed in the same run avoiding the multiple IO overhead when the configurations would be performed sequentially in different runs.
-
 %time HiggsToTauTauAnalysis.py @HiggsAnalysis/KITHiggsToTauTau/data/ArtusWrapperConfigs/Sync13TeV.cfg -i HiggsAnalysis/KITHiggsToTauTau/data/Samples/NAF_sample_DYJetsToLLM50_RunIISpring15DR74_Asympt25ns_13TeV_MINIAOD_amcatnloFXFX-pythia8_recent.txt -f 10
-\begin{table}[h!]
+\begin{table}[!ht]
 \centering
@@
 
+Table~\ref{table_artus_runtime_comparison} shows a runtime measurement for the baseline part of the $\PH\to\Pgt\Pgt$ in the four main decay channels ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$ and $\Pgt\Pgt$).
+It illustrates the main advantage of the \artus structure: sub-analyses with different sets of configurations can be performed in the same run avoiding the multiple IO overhead when the configurations would be performed sequentially in different runs.
+
 The outputs are flat n-tuples suitable for performing the background modeling step done in HarryPlotter.
@@
 
-Especially new students joining the analysis groups can contribute very quickly.
+Especially new students\todo[inline]{Das klingt ja schon fast, als st\"unden am Ende "echte" Menschen hinter den besprochenen Dingen.
+F\"ur Paper eher ungew\"ohnlich?} joining the analysis groups can contribute very quickly.
 Once they have understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.

### 2015-10-27 Core/doc/latex/paper.tex
Paper: Add flexibility goal and further remove details from goals

@@
 Source code maintenance, i.e.\ to be up-to-date with the latest requirements while not losing backwards compatibility, is a challenge for each software project.
-\todo[inline]{Didn't we agree to remove the following sentence?} The first important step is to always have an updated recipe that works out of the box on each machine offering CVMFS.
 To make the entry level as low as possible, beginners can start with an example analysis.
@@
 
-%\artus has the built-in possibility to submit analysis jobs with grid-control, a job submission tool.
+\item[Reliability]
+In most cases, analysis code is written from scratch for very specific tasks and it is used only by very small groups of analysts.
+This leads to frequent re-imple\-men\-ta\-tions and low trust in reliability.
+An ideal framework should allow to re-use analysis code due to its modular structure as well as sharing it between different analysis groups, and therefore improving code quality significantly.
 
-\item[Reliability]
-In most cases, analyses never leave prototype status.
-This leads to frequent re-imple\-men\-ta\-tions and low trust in reliability.
-\artus allows the re-use of analysis code due to its modular structure as well as sharing it between different analysis groups, and therefore improving code quality significantly.
-
-Source code and configuration files have become the most precise form of description.
+Source code and configuration files are the most precise form of describing the processes.
 Therefore, readability also for people who have not written the code is crucial.
 Also, if possible, existing and well-established libraries of the HEP community are interfaced.
+
+\item[Flexibility]
+While not aiming at feature-completeness, the software should make it easy to cover all analysis needs by being flexible and extendible.
+This comprises new data formats, physical quantites and analysis steps, for instance.
 \end{description}
@@
 The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.
-The complete structure is explained in the next section~\ref{section_artus_structure}.
+The complete structure is explained in the next section.
 
@@
 This is possible, because the processed events are known to be independent of each other.
+The framework comes with a built-in possibility to submit analysis jobs with the job submission tool grid-control.
 

### 2015-10-28 Core/doc/latex/paper.tex
paper.tex: minor comments

--- 2015-10-27 Core/doc/latex/paper.tex
@@
 \caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics, numbers taken from \cite{joram_phd}.
-Data size is reduced by six orders of magnitude, the turnaround time by a factor of 10000.
-I/O intensive operations are done highly parallelized in the WLCG.
-The data reduction is achieved by performing the data-intensive operations only rarely and applying analysis specific event selection steps as early as possible.}
+Data size is reduced by six orders of magnitude, turnaround time by a factor of 4.
+I/O intensive operations are done in highly parallel in the WLCG.
+The data reduction is achieved by performing the data-intensive operations only rarely and applying sensible event selection steps as early as possible.}
 \label{figure_analysis_steps}

### 2015-10-28 KappaAnalysis/scripts/puWeightCalc.py
puWeightCalc.py: now writing weight efficiency to STDOUT

@@ -129,6 +129,9 @@ def calcWeights(data, mc, verbose=False, warn=True, rebin=False, binning=(), wei
 		print >> sys.stderr, "WARNING: Bins truncated to lower limit (%f) in" % min_weight, format_bin_ranges([npu for npu in min_bins], bin_centers)
 	if max_bins:
 		print >> sys.stderr, "WARNING: Bins truncated to upper limit (%f) in" % max_weight, format_bin_ranges([npu for npu in max_bins], bin_centers)
+	# check efficiency of weights for matching MC to data
+	mc.Multiply(weights)
+	print "weight_efficiency =", mc.Integral()
 	return weights
 
 

### 2015-10-28 KappaAnalysis/scripts/puWeightCalc.py
puWeightCalc.py: updated help to match current interface

@@ -214,11 +214,14 @@ def format_bin_ranges(bins, all_bins=None, fmt_str="%.2f"):
 
 def options():
 	parser = argparse.ArgumentParser(
-		description="%(prog)s calculates the weights for MC reweighting "
-			"according to the number of pile-up interactions. Use cases: "
-			"%(prog)s /path/to/skim/*.root Cert_JSON.txt pileup_JSON.txt or"
-			"%(prog)s mcdist.root datadist.root")
-	parser.add_argument('files', metavar='input', type=str, nargs='*',
+		description="""
+%(prog)s calculates the weights for MC reweighting to match the number of
+pile-up interactions in data. Use cases:
+  %(prog)s Cert_JSON.txt /mc/skim/*.root -i pileup_JSON.txt [options]
+  %(prog)s datadist.root mcdist.root [options]
+		""".strip(),
+		formatter_class=argparse.RawDescriptionHelpFormatter)
+	parser.add_argument('files', metavar='input', type=str, nargs='+',
 		help="""
 		input files as [data] [mc, [mc, [...]]] - 'data' may be a root file
 		with the distribution of pile-up interactions in data or a run json file

### 2015-10-28 KappaAnalysis/scripts/puWeightCalc.py
puWeightCalc.py: added explicit emit_data for output

@@ -131,7 +131,7 @@ def calcWeights(data, mc, verbose=False, warn=True, rebin=False, binning=(), wei
 		print >> sys.stderr, "WARNING: Bins truncated to upper limit (%f) in" % max_weight, format_bin_ranges([npu for npu in max_bins], bin_centers)
 	# check efficiency of weights for matching MC to data
 	mc.Multiply(weights)
-	print "weight_efficiency =", mc.Integral()
+	emit_data("weight_efficiency", mc.Integral())
 	return weights
 
 
@@ -187,6 +187,12 @@ def getDistributionFromFile(filename, histoname="pileup"):
 		print >> sys.stderr, "The histogram %s could not be found in %s." % (histoname, filename)
 		sys.exit(1)
 	return copy.deepcopy(histo)
+
+
+# Formatting/Output
+def emit_data(key, value):
+	"""Write a key/value pair for machine processing"""
+	print >> sys.stdout, str(key) + " = " + repr(value)
 
 
 def format_bin_ranges(bins, all_bins=None, fmt_str="%.2f"):

### 2015-10-28 KappaAnalysis/scripts/puWeightCalc.py
puWeightCalc.py: expanded help on output

@@ -226,6 +226,13 @@ pile-up interactions in data. Use cases:
   %(prog)s Cert_JSON.txt /mc/skim/*.root -i pileup_JSON.txt [options]
   %(prog)s datadist.root mcdist.root [options]
 		""".strip(),
+		epilog="""
+%(prog)s may output warnings to stderr. These are for diagnostics only and
+formatted to be human readable.
+Additional data is written exclusively to stdout. These are machine readable
+key-value pairs separated by ' = ' using repr(value), e.g.
+foo_bar = "quax string value".
+		""".strip(),
 		formatter_class=argparse.RawDescriptionHelpFormatter)
 	parser.add_argument('files', metavar='input', type=str, nargs='+',
 		help="""

### 2015-10-28 Core/doc/latex/paper.tex
Paper: Further comments by Dominik

--- 2015-10-27 Core/doc/latex/paper.tex
@@
 \newcommand{\artus}{\software{Artus}}
+\newcommand{\kapa}{{\Large$\kappa$}\software{appa}}
+\newcommand{\harryplotter}{\software{HarryPlotter}}
 
@@
 \begin{frontmatter}
-\title{\artus{} -- Framework for Event-based Data Analysis in High Energy Physics}
+\title{\artus{} -- A Framework for Event-based Data Analysis in High Energy Physics}
 
@@
 
-Between the data taking at the detector or the generation of simulated events with the subsequent detector simulation and the presentation of the physical results, the following analysis steps have shown to be the best compromise in terms of turnaround time and efficiency as explained in Figure \ref{figure_analysis_steps}.
+Between the data taking at the detector or the generation of simulated events and the presentation of the physical results, the following analysis steps have shown to be the best compromise in terms of turnaround time and efficiency as explained in Figure \ref{figure_analysis_steps}.
 
@@
 Finally, the skimmed n-tuples are processed by user code running on local resources.
-This processing step includes further event selections, event categorization or high-level calculations based on the selected physics objects.
+This processing step includes further event selections, event categorization or high-level calculations based on the reconstructed physics objects.
 The events are usually processed with different configurations, depending on the specific analysis needs.
@@
 This leads to convoluted, tangled and unstructured code, which is difficult to understand and to maintain and also difficult to hand over to new people joining the analysis effort.
-Also, code is rarely shared among different groups, although the basic parts of an analysis, such as handling of input data having the same formats, their processing and the selection and identification of physics objects follow similar or equivalent specifications.
-Looking at the user side, an analysis group usually consists of several people having different academic levels and different programming skills, some of them joining the analysis effort only for a short period of time and with a well-defined task.
+Also, code is rarely shared among different groups, although the basic parts of an analysis, such as handling of input data in the same formats, their processing and the selection and identification of physics objects follow similar or equivalent specifications.
+Looking at the user side, an analysis group usually consists of several people having different academic levels and different programming skills, some of them joining the analysis effort only for a short period of time and limited to a well-defined task.
 
@@
 I/O intensive operations are done highly parallelized in the WLCG.
-The data reduction is achieved by performing the data-intensive operations only rarely and applying analysis specific event selection steps as early as possible.}
+The data reduction is achieved by applying analysis specific event selection steps as early as possible.
+Performing the data-intensive operations only in the first step of this sequence reduces the run time of the analysis.}
 \label{figure_analysis_steps}
@@
 To make the entry level as low as possible, beginners can start with an example analysis. 
-In \artus, everything is steered via JSON configuration files.
-The modules then implement what has to be done while the data is stored in desired data format.
+Up-to-date recipes should allow the installation and execution of the example analysis out-of-the box.
+Steering the analysis in detail with configuration files makes it possible to re-use the same code for differing analysis requirements.
+The modules should encapsulate the actual operations providing and enforcing a clear code structure while the data is stored in the desired data format.
 
@@
 The well-tested core is shared among various analyses, providing a reliable fundament for any new analysis.
-The highly modular structure guides the user to develop analysis software that is easily maintainable and constructively extensible.
+The highly modular structure guides the user to develop analysis software that is easily maintainable and extensible.
 Thus, the \artus framework avoids the aforementioned problems of separate user code for individual analyses.
@@
 Multi-core techniques are not required since the processing can be trivially parallelized by splitting the input dataset and sending it to different computing instances.
-This is possible, because the processed events are known to be independent of each other.
+This is possible because the processed events are known to be independent of each other.
 The framework comes with a built-in possibility to submit analysis jobs with the job submission tool grid-control.
@@
 
-The basic concept of the framework is taken from the code used for the $\PZ+\text{jet}$ analysis documented in reference~\cite{joram_phd}.
+The basic concept of the framework is taken from the code used for the $\PZ+\text{jet}$ analysis documented in~\cite{joram_phd}.
 It is generalized and extended to satisfy the needs of various analysis groups.
@@
 \artus respects the separation of code and configuration.
-Settings select\todo[inline]{better "specify" instead of "select"?} what has to be done and with which parameters.
-The code does perform these steps, ideally without the user being fully aware of implementation details.
-The single source of truth for an analysis is therefore a JSON file that completely defines the analysis.
+Settings specify what has to be done and with which parameters.
+The code performs the selected steps---ideally without requiring the user to be fully aware of implementation details.
+Hence, the JSON file completely defines the analysis.
 It contains information on the input data and settings for the pipelines and processors described in the following.
 Each of the modules described in the following has access to the settings read in from the configuration file.
-The \artus package comes with sophisticated tools written in python, that help in generating this JSON file.
+The \artus package comes with sophisticated tools written in Python which help in generating this JSON file.
 
 The input is handled by an event provider.
-Its purpose is to manage reading events contents from any kind of input into an event object and to provide information about the total number of events to be processed.
+Its purpose is to manage the import of event contents from any kind of input to the internal event object and to provide information about the total number of events to be processed.
 
@@
 First, a so-called global pipeline is run.
-Then,\todo[inline]{No comma here?} the execution is split up into multiple so-called local pipelines, that are also processed sequentially.
+Then the execution is split up into multiple so-called local pipelines which are also processed sequentially.
 The composition of a pipeline is illustrated in Figure~\ref{figure_artus_pipeline}.
@@
 \begin{description}
-\item[Producers] are meant to calculate new quantities based on the information in the event and the product and following the settings of the pipeline.
+\item[Producers] are meant to calculate new quantities based on the information in the event and the product according to the settings of the pipeline.
 \item[Filters] apply a selection based on event properties.
-In case an event does not fulfill a requirement defined by a filter, the processing of the subsequent producers and filters can be skipped.
+In case an event does not fulfill a requirement defined by a filter, the execution of the subsequent processors can be skipped.
 \item[Consumers] can be added to local pipelines.
@@
 The output together with the complete configuration is written to a ROOT~\cite{root} file.
-These processors are created and managed by a dedicated factory according to the configuration.
+These processors are created and managed by a dedicated factory class according to the configuration.
 
@@
 \label{section_artus_analysis}
-In order to create a custom analysis, the analysis programmer can build his own code on the \artus classes by deriving from them.
+In order to create a custom analysis, the user can build his own code on the \artus classes by deriving from them.
 He must provide an implementation of the settings, the event and the product class.
@@
 The event provider must know how to read event content from the input files and how to store them in the event object.
-Furthermore, a factory managing the creation of analysis-specific processors needs to exist.
+Furthermore, a factory class defining the creation of analysis-specific processors is required.
 These classes also have to be derived from the \artus base classes.
@@
 
-Analyses that share the input file format can easily also share processors, that implement basic analysis steps in a general fashion.
+Analyses shareing the input file format can easily also share processors which implement basic analysis steps in a general fashion.
 Analysis-specific parts can either derive from existing processor classes or be modeled in new processors.
 
-\section{HarryPlotter -- A Python Framework for Post-processing}
+\section{\harryplotter -- A Python Framework for Post-processing}
 \label{section_artus_harryplotter}
@@
 The inputs for this step are either histograms filled in the previous step or n-tuples whose entries can be filled into histograms with reasonable computing costs.
-For this reason, Python has been chosen as language for the HarryPlotter framework\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/HarryPlotter}}.
+For this reason, Python has been chosen as language for the \harryplotter framework\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/HarryPlotter}}.
 As the name implies, the main focus is on plotting of results.
@@
 \centering \input{figures/harry_plotter}
-\caption{Structure of the HarryPlotter framework.
+\caption{Structure of the \harryplotter framework.
 The processing of input modules is followed by the run of analysis modules and concluded by the execution of plot modules.
@@
 The configuration is provided by an argument parser that can handle both arguments from a command line interface and content from JSON configuration files or Python dictionaries.
-This makes it possible to use either the HarryPlotter executable configured via the command line or call the main function within another Python script.
+This makes it possible to use either the \harryplotter executable configured via the command line or call the main function within another Python script.
 The executable can perform one single plot per run.
@@
 
-Currently, the \artus framework is used for various user analyses of CMS data, ranging from jet energy calibration and QCD studies to analyses in the scope of Higgs boson measurements and searches for physics beyond the Standard Model.
+Currently, the \artus framework is used for various user analyses of CMS data, ranging from jet energy calibration and QCD studies to Higgs boson measurements and searches for physics beyond the Standard Model.
 As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis are explained in the following.
 
-The $\PH\to\Pgt\Pgt$ analysis makes use of skimmed data sets in the Kappa format.
-The Kappa framework\footnote{\url{https://github.com/KappaAnalysis/Kappa}} is designed for skimming CMS data into small n-tuples that can be analyzed independently of the CMSSW software.
+The $\PH\to\Pgt\Pgt$ analysis makes use of skimmed data sets in the \kapa format.
+The \kapa framework~\cite{kappa} is designed for skimming CMS data into small n-tuples that can be analyzed independently of the CMSSW software.
 The only dependence is the ROOT framework.
 The n-tuples store high-level information such as four-momentum vectors, collections of leptons and vertices.
-Similar as the \artus framework, Kappa aims to satisfy general analysis needs.
+Similar to the \artus framework, \kapa aims to satisfy general analysis needs.
 
-A large part of the \artus software is specialized on the analysis of Kappa n-tuples\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/KappaAnalysis}}.
-An event provider is available for reading Kappa n-tuples.
+A large part of the \artus software is specialized on the analysis of \kapa n-tuples\footnote{\url{https://github.com/artus-analysis/Artus/tree/master/KappaAnalysis}}.
+An event provider is available for reading \kapa n-tuples.
 The event class contains members for all important physics objects used in analyses.
-The branches of the n-tuples, that should be read in from the input files, are configurable and which reduces the amount of information transferred from the input files and therefore accelerates the analysis significantly.
+The branches of the n-tuples, that should be read in from the input files, are configurable.
+This reduces the amount of information transferred from the input files and therefore accelerates the analysis significantly.
 
-The structure of the pipelines is chosen such that, for each decay channel, a separate pipeline exists.
+The structure of the pipelines is chosen such that a separate pipeline exists for each decay channel.
 Each of the pipelines is duplicated and modified in order to implement the different settings for shifts of quantities affected by systematic uncertainties.
@@
 The global pipeline is used to perform actions that are common for all channels.
-This is for example the identification of jets and their corrections as well as the filtering of valid data events.
+This is for example the identification and correction of jets as well as the filtering of valid data events.
 
@@
 Table~\ref{table_artus_runtime_comparison} shows a runtime measurement for the baseline part of the $\PH\to\Pgt\Pgt$ in the four main decay channels ($\Pgm\Pgt$, $\Pe\Pgt$, $\Pe\Pgm$ and $\Pgt\Pgt$).
-It illustrates the main advantage of the \artus structure: sub-analyses with different sets of configurations can be performed in the same run avoiding the multiple IO overhead when the configurations would be performed sequentially in different runs.
+It illustrates the main advantage of the \artus structure: sub-analyses with different sets of configurations can be performed in the same run avoiding the multiple I/O overhead when the configurations would be executed sequentially in different runs.
 
-The outputs are flat n-tuples suitable for performing the background modeling step done in HarryPlotter.
-Histograms are read while cuts for the final event selection are applied.
-As an example, the cut on the transverse mass is applied on this level because events from control regions needed to be preserved for the background modeling step.
+The outputs are flat n-tuples suitable for performing the background modeling step which is done in \harryplotter.
+Histograms are read while the final event selection is applied.
+As an example, the selection on the transverse mass is applied on this level because events from control regions needed to be preserved for the background modeling step.
 For each background process, an analysis module has been developed performing the estimation of the samples.
@@
 The \artus analysis framework presented in this paper offers a comprehensive and well-integrated solution for event-based data analyses in the HEP domain.
-In conjunction with the post-processing toolkit HarryPlotter, all data analysis needs are covered.
+In conjunction with the post-processing toolkit \harryplotter, all data analysis needs are covered.
 
 The modular and structured manner, in which the processing required for an analysis, can be expressed within the \artus framework, allowed the involved research groups to share and re-use source code on a scale not possible before.
-The concept underlying the \artus framework also enabled us to share program code between analysis and even across different universities and research centers.
+The concept underlying the \artus framework also enabled sharing program code between analyses and even across different universities and research centers.
 
@@
 Once they have understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.
-In a similar manner, using the \artus framework, it is now much less work to set up a new analysis because a rich library of processors, filters and consumers exists and can be reused for new analysis.
+In a similar manner, using the \artus framework, it is now much less work to set up a new analysis because a rich library of processors, filters and consumers exists and can be reused for a new analysis.
 

### 2015-10-28 Core/doc/latex/paper.tex
Paper: Reorder citations

@@
 
-Following the structure of the CMSSW~\cite{cmssw} framework, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
+Following the structure of the CMS software framework~\cite{cms, cmssw}, the \artus framework\footnote{\url{https://github.com/artus-analysis/artus}} provides a front-to-end solution for the analysis of event-based data.
 The basic concept of modules processing events within an event loop is complemented by tools for the configuration of every step.
@@
 The \artus framework is written in C++.
-The core of the framework only depends on the boost library\footnote{\url{http://www.boost.org}}.
+The core of the framework only depends on the boost library~\cite{boost}.
 Further dependencies may be introduced by the actual analysis code.

### 2015-10-28 Core/doc/latex/paper.tex
Paper: Add commands for Kappa and HarryPlotter

--- 2015-10-28 Core/doc/latex/paper.tex
@@
 
-\section{HarryPlotter -- A Python Framework for Post-processing}
+\section{\harryplotter -- A Python Framework for Post-processing}
 \label{section_artus_harryplotter}
@@
 The \artus analysis framework presented in this paper offers a comprehensive and well-integrated solution for event-based data analyses in the HEP domain.
-In conjunction with the post-processing toolkit HarryPlotter, all data analysis needs are covered.
+In conjunction with the post-processing toolkit \harryplotter, all data analysis needs are covered.
 

### 2015-10-28 Core/doc/latex/paper.tex
Paper: Comments from Fabio

--- 2015-10-28 Core/doc/latex/paper.tex
@@
 \item[Re-utilization of code] Processors can be shared among different analysis groups.
-Every user contributes to the testing of existing code and improves the confidence in this code.
-\item[Configurability] Each module uses settings which are read from the the configuration.
+Every user contributes to the testing of existing code and improves the confidence in it.
+\item[Configurability] Each module uses settings which are read from the configuration.
 A separate sub-set of the configuration is created for each pipeline.
@@
 The settings class defines the tags that are read from the configuration file and the corresponding types of these values.\todo[inline]{better "and the types of the corresponding values"?}
-The \emph{event} class defines the event content which is read from the input and the product class contains members for new quantities calculated during the analysis stage.
-These three classes need to be derived from the base classes provided by the core of the \artus framework.
+The \emph{event} class defines the event content which is read from the input and the \emph{product} class contains members for new quantities calculated during the analysis stage.
+These classes need to be derived from the base classes provided by the core of the \artus framework.
 
@@
 %\em                                              & 6:27                             & 1181 \\
- 1 ($\Pe\Pe$)                                     & 6:31                             & 1174 \\
+ 1 ($\Pe\Pgm$)                                    & 6:31                             & 1174 \\
 %1 ($\Pe\Pgt$)                                    & 7:03                             & 1084 \\
@@
 The analysis is performed on 10 files with a total size of 6.1~GB containing 452229 simulated $\PZ+\text{jet}$ events.
-The measurement is performed with different numbers of pipelines, where each pipeline implements the analysis of one sub-channel of the analysis.
+The measurement is performed with different numbers of pipelines, where each pipeline implements the analysis of one sub-channel.
 The values are compared with the execution without any pipelines and without global processors.
@@
 Histograms are read while the final event selection is applied.
-As an example, the selection on the transverse mass is applied on this level because events from control regions needed to be preserved for the background modeling step.
+As an example, the selection on the transverse mass is applied on this level because events from control regions need to be preserved for the background modeling step.
 For each background process, an analysis module has been developed performing the estimation of the samples.
@@
 Once they have understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.
-In a similar manner, using the \artus framework, it is now much less work to set up a new analysis because a rich library of processors, filters and consumers exists and can be reused for a new analysis.
+In a similar manner, using the \artus framework, it is now much less work to set up a new analysis because a rich library of processors, filters and consumers exists and can be reused for new analyses.
 

### 2015-10-28 Core/doc/latex/paper.tex
Paper: Comments by Thomas

@@
 The data which are relevant for a specific analysis are selected in a step usually referred to as \textit{skimming}.
-The output of the skimming process is an analysis-dependent file\todo[inline]{better "format" instead of "file"?
-(needs restructuring of the sentence a bit}, usually in an n-tuple format, and small enough to be stored on local file servers, often owned and operated by a single institute.
+The output of the skimming process is stored in an n-tuple format on local file servers, often owned and operated by a single institute.
 The size of these files ranges from several \SI{10}{GB} to few~TB.
@@
 \item[Performance]
-The main performance indicator is the \emph{turnaround time} which is the time needed to run the whole\todo[inline]{"entire" always better than "whole"?} analysis in case new requirements arise.
+The main performance indicator is the \emph{turnaround time} which is the time needed to run the entire analysis in case new requirements arise.
 Since the runtime is often limited by the transfer speed of the storage servers, the software should load each event only once and perform all necessary processing steps.
@@
 He must provide an implementation of the settings, the event and the product class.
-The settings class defines the tags that are read from the configuration file and the corresponding types of these values.\todo[inline]{better "and the types of the corresponding values"?}
+The settings class defines the tags that are read from the configuration file and the types of the corresponding values.
 The \emph{event} class defines the event content which is read from the input and the \emph{product} class contains members for new quantities calculated during the analysis stage.
@@
 
-Especially new students\todo[inline]{Das klingt ja schon fast, als st\"unden am Ende "echte" Menschen hinter den besprochenen Dingen.
-F\"ur Paper eher ungew\"ohnlich?} joining the analysis groups can contribute very quickly.
-Once they have understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.
+Especially new students joining the analysis groups can contribute very quickly.
+Having understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.
 In a similar manner, using the \artus framework, it is now much less work to set up a new analysis because a rich library of processors, filters and consumers exists and can be reused for new analyses.

### 2015-10-28 HarryPlotter/python/analysis_modules/cutflow.py
harryplotter: cutflows properly set when no expansion is performed

@@ -144,7 +144,7 @@ class Cutflow(analysisbase.AnalysisBase):
 		_unique_cutflows = set(tuple(cutlabels) for cutlabels in filternames.values())
 		if not all_cuts and not cut_blacklist and len(_unique_cutflows) == 1:
 			# no modification required
-			return
+			return cutflow_histograms
 		if not all_cuts and len(_unique_cutflows) > 1:
 			log.warning("Cutflow histograms have different number of bins! New histograms containing all cuts will be constructed.")
 		# if we can merge desired cuts and individual cuts, subsequences don't have conflicting order

### 2015-11-02 Core/doc/latex/figures/analysis_steps.tex

@@
 
-\filldraw[KIT_gruen_1] (0.3,3.11) circle(.05cm) node[black,anchor=south west]{EDM};
-\filldraw[KIT_gruen_1] (3.3,2.269) circle(.05cm) node[black, anchor=west]{Kappa};
+\filldraw[KIT_gruen_1] (0.3,3.11) circle(.05cm) node[black,anchor=south west]{Full event data};
+\filldraw[KIT_gruen_1] (3.3,2.269) circle(.05cm) node[black, anchor=west]{Skim};
 \filldraw[KIT_gruen_1] (6.6,1.03) circle(.05cm) node[black, anchor=south west]{N-Tuple};
@@
 
-\draw[KIT_rot_1,->] (10,0) -- (10,4) node[anchor=south] {Turnarounds /h};
+\draw[KIT_rot_1,<-] (10,0) -- (10,4) node[anchor=south] {Run time / h};
 \foreach \y/\ytext in {1/-1,2/1, 3/3}
@@
 
-\filldraw[KIT_rot_1] (1.65,0.66) circle(.05cm) node[black, anchor=west]{Skim};
+\filldraw[KIT_rot_1] (1.65,0.66) circle(.05cm) node[black, anchor=west]{Skimming};
 \filldraw[KIT_rot_1] (5,1.65) circle(.05cm) node[black, anchor=north]{Analysis};

### 2015-11-17 HarryPlotter/scripts/ini_harry_cmssw.sh
one more ekplxplus machine

@@ -16,7 +16,7 @@ if [[ -z ${HARRY_SSHPC} ]]; then
 		export HARRY_SSHPC=$HARRY_USERPC
 	else
 		# find a reachable host - try ekplxs in different offices
-		for lxid in 26 30 69 77 14 17 21 25; do
+		for lxid in 55 26 30 69 77 14 17 21 25; do
 			if ping -c 1 ekplx${lxid}.physik.uni-karlsruhe.de 2>/dev/null 1>&2; then
 				export HARRY_SSHPC=ekplx${lxid}.physik.uni-karlsruhe.de
 				break

### 2015-11-17 Core/doc/latex/paper.tex

@@
 Having understood general concept and structure of an \artus analysis, they can contribute by writing their own producers or filters while the full complexity of the event-processing is taken care of by the \artus framework.
-In a similar manner, using the \artus framework, it is now much less work to set up a new analysis because a rich library of processors, filters and consumers exists and can be reused for new analyses.
+Using the \artus framework, it is much less work to set up a new analysis because a rich library of processors, filters and consumers already exists and can be reused for new analyses.
 

### 2015-11-17 Core/doc/latex/paper.tex

@@
 The events are usually processed with different configurations, depending on the specific analysis needs.
-The output is then used for post-processing steps, including plotting of the results and their statistical interpretation.
+The output is then used for post-processing steps, including the graphical representation of the results and their statistical interpretation.
 
@@
 Hence, the JSON file completely defines the analysis.
-It contains information on the input data and settings for the pipelines and processors described in the following.
-Each of the modules described in the following has access to the settings read in from the configuration file.
+It contains information on the input data and settings for the pipelines and processors described below.
+Each of the modules has access to the settings read in from the configuration file.
 The \artus package comes with sophisticated tools written in Python which help in generating this JSON file.
@@
 The most important part of an analysis are the \emph{processors}.
-The abstract processors of the \artus core need to be implemented to realize the physics needs of the analysis in the form of code.
+The abstract processors of the \artus core need to be implemented to realize the physics needs of the analysis.
 After the basic structure of an analysis is set up, most changes and additions are only related to the processors.
@@
 \begin{enumerate}
-\item One or, in special cases, more input modules are run to read in data from an input source.
+\item One or, in special cases, more input modules are run to read data from an input source.
 The input format is defined by the input module.
@@
 Their task is to output the processed data in the specified format.
-In most cases, the output is a plot but it is also possible to store the objects in new ROOT files.
+In most cases, the output is a plot, but it is also possible to store the objects in new ROOT files.
 \end{enumerate}
@@
 The configuration is provided by an argument parser that can handle both arguments from a command line interface and content from JSON configuration files or Python dictionaries.
-This makes it possible to use either the \harryplotter executable configured via the command line or call the main function within another Python script.
+This makes it possible to either use the \harryplotter executable configured via the command line or to call the main function within another Python script.
 The executable can perform one single plot per run.
@@
 Currently, the \artus framework is used for various user analyses of CMS data, ranging from jet energy calibration and QCD studies to Higgs boson measurements and searches for physics beyond the Standard Model.
-As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis are explained in the following.
+As an example, the technical aspects of the $\PH\to\Pgt\Pgt$ analysis are explained below.
 
@@
 The \artus analysis framework presented in this paper offers a comprehensive and well-integrated solution for event-based data analyses in the HEP domain.
-In conjunction with the post-processing toolkit \harryplotter, all data analysis needs are covered.
+In conjunction with the post-processing toolkit \harryplotter, all typical data analysis needs are covered.
 

### 2015-12-03 HarryPlotter/python/analysis_modules/tgraphfromhistograms.py
harryplotter: TGraphFromHistograms may now skip empty bins

@@ -1,6 +1,8 @@
 # -*- coding: utf-8 -*-
 
 import logging
+from collections import deque
+import sys
 import Artus.Utility.logger as logger
 log = logging.getLogger(__name__)
 
@@ -9,9 +11,80 @@ import ROOT
 import Artus.HarryPlotter.analysisbase as analysisbase
 
 
-class TGraphFromHistograms(analysisbase.AnalysisBase):
-	""" This module takes two (or more) histograms and uses their y-values (and errors) as x,y-pairs for a TGraphErrors."""
+class HistogramGroupIterator(object):
+	SKIP_ANY = 1
+	SKIP_LEADING = 2
+	SKIP_TRAILING = 4
+	SKIP_BORDERING = SKIP_LEADING | SKIP_TRAILING
+	def __init__(self, histograms, skip=False):
+		"""
+		Iterator for groups of histograms
 
+		This class iterates bin-wise in X over all its histograms. For each bin,
+		a list of `[(h1, h1err), (h2, h2err), ...]` is yielded.
+		"""
+		if len(set(histo.GetNbinsX() for histo in histograms)) > 1:
+			raise ValueError("Histograms must be of same bin count in X")
+		self.histograms = histograms
+		self.skip = skip
+
+	def _histo_group_iter(self):
+		"""
+		Actual iteration over histogram values without skipping
+
+		:returns: iterator of each histogram's content and error at each bin
+		:rtype: collections.Iterable[list[tuple(float, float)]]
+		"""
+		for i in range(1, self.histograms[0].GetNbinsX()+1):
+			yield [(histo.GetBinContent(i), histo.GetBinError(i)) for histo in self.histograms]
+
+	def __iter__(self):
+		raw_iter = self._histo_group_iter()
+		if self.skip == self.SKIP_ANY:
+			return self._iter_skip_any_(raw_iter)
+		if self.skip & self.SKIP_LEADING:
+			raw_iter = self._iter_skip_leading(raw_iter)
+		if self.skip & self.SKIP_TRAILING:
+			raw_iter = self._iter_skip_trailing(raw_iter)
+		return raw_iter
+
+	@staticmethod
+	def _iter_skip_any_(iterable):
+		"""Iterator skipping any bin that is empty in all histograms"""
+		for bin_contents in iterable:
+			# yield if any indivial histo has any non-empty content
+			if any(any(histo_content) for histo_content in bin_contents):
+				yield bin_contents
+
+	@staticmethod
[…]

### 2015-12-03 Utility/interface/easylogging++.h
Consider easy_logging a system header, AGAIN
This means no warnings are presented from easy logging code (this code
throws hundreds of warnings). See 43b75fa1f987

@@ -17,6 +17,7 @@
 #define EASYLOGGINGPP_H
 // Compilers and C++0x/C++11 Evaluation
 #if defined(__GNUC__)
+#pragma GCC system_header
 #   define ELPP_COMPILER_GCC 1
 #   define ELPP_GCC_VERSION (__GNUC__ * 10000 \
                                + __GNUC_MINOR__ * 100 \

### 2015-12-03 KappaAnalysis/interface/KappaProduct.h
Add ZProducer
This producer can produce Z candidates from valid leptons

@@ -147,7 +147,12 @@ public:
 	std::map<KElectron*, KGenJet*> m_genTauJetMatchedElectrons;
 	std::map<KMuon*, KGenJet*> m_genTauJetMatchedMuons;
 	std::map<KTau*, KGenJet*> m_genTauJetMatchedTaus;
-	
+
+	/// added by ZProducer
+	KLV m_z;
+	std::pair<KLepton*, KLepton*> m_zLeptons;
+	bool m_zValid;
+
 	// MVA outputs
 	std::vector<double> m_discriminators;
 

### 2015-12-03 KappaAnalysis/interface/KappaSettings.h

@@ -312,7 +312,7 @@ public:
 	IMPL_SETTING_STRINGLIST_DEFAULT(TmvaInputQuantities, {});
 	IMPL_SETTING_STRINGLIST_DEFAULT(TmvaMethods, {});
 	IMPL_SETTING_STRINGLIST_DEFAULT(TmvaWeights, {});
-	
+
 	// KappaCollectionsConsumer settings
 	IMPL_SETTING_DEFAULT(bool, BranchGenMatchedElectrons, false);
 	IMPL_SETTING_DEFAULT(bool, BranchGenMatchedMuons, false);
@@ -322,4 +322,8 @@ public:
 	IMPL_SETTING_DEFAULT(bool, AddGenMatchedParticles, true);
 	IMPL_SETTING_DEFAULT(bool, AddGenMatchedTaus, true);
 	IMPL_SETTING_DEFAULT(bool, AddGenMatchedTauJets, true);
+
+	// ZProducer
+	IMPL_SETTING_DEFAULT(float, ZMass, 91.1876f)
+	IMPL_SETTING(float, ZMassRange)
 };

### 2015-12-03 KappaAnalysis/src/KappaFactory.cc

@@ -33,6 +33,7 @@
 #include "Artus/KappaAnalysis/interface/Producers/GenTauMatchingProducers.h"
 #include "Artus/KappaAnalysis/interface/Producers/GenTauJetMatchingProducers.h"
 #include "Artus/KappaAnalysis/interface/Producers/GenMuonFSRProducer.h"
+#include "Artus/KappaAnalysis/interface/Producers/ZProducer.h"
 
 // filter
 #include "Artus/KappaAnalysis/interface/Filters/RunLumiEventFilter.h"
@@ -155,6 +156,12 @@ ProducerBaseUntemplated * KappaFactory::createProducer ( std::string const& id )
 		return new RecoMuonGenTauJetMatchingProducer();
 	else if(id == RecoTauGenTauJetMatchingProducer().GetProducerId())
 		return new RecoTauGenTauJetMatchingProducer();
+	else if(id == ZmmProducer().GetProducerId())
+		return new ZmmProducer();
+	else if(id == ZeeProducer().GetProducerId())
+		return new ZeeProducer();
+	else if(id == ZemProducer().GetProducerId())
+		return new ZemProducer();
 	else
 		return FactoryBase::createProducer( id );
 }

### 2015-12-03 KappaAnalysis/src/Filters/ZFilter.cc
Add ZFilter
This stops the processing if there is no valid Z in the event

@@ -1,0 +1,10 @@
+#include "Artus/KappaAnalysis/interface/Filters/ZFilter.h"
+
+std::string ZFilter::GetFilterId() const { return "ZFilter"; }
+
+bool ZFilter::DoesEventPass(KappaEvent const& event,
+                            KappaProduct const& product,
+                            KappaSettings const& settings) const
+{
+	return product.m_zValid;
+}

### 2015-12-03 KappaAnalysis/src/KappaFactory.cc

@@ -54,6 +54,7 @@
 #include "Artus/KappaAnalysis/interface/Filters/BeamScrapingFilter.h"
 #include "Artus/KappaAnalysis/interface/Filters/HCALNoiseFilter.h"
 #include "Artus/KappaAnalysis/interface/Filters/nPUFilter.h"
+#include "Artus/KappaAnalysis/interface/Filters/ZFilter.h"
 
 // consumer
 #include "Artus/KappaAnalysis/interface/Consumers/KappaCutFlowHistogramConsumer.h"
@@ -278,6 +279,8 @@ FilterBaseUntemplated * KappaFactory::createFilter ( std::string const& id )
 		return new BeamScrapingFilter();
 	else if(id == nPUFilter().GetFilterId())
 		return new nPUFilter();
+	else if(id == ZFilter().GetFilterId())
+		return new ZFilter();
 	else
 		return FactoryBase::createFilter( id );
 }

### 2015-12-04 HarryPlotter/python/analysis_modules/tgraphfromhistograms.py
HarryPlotter: disabled leftover debug code

@@ -12,6 +12,7 @@ import Artus.HarryPlotter.analysisbase as analysisbase
 
 
 class HistogramGroupIterator(object):
+	SKIP_NONE = 0
 	SKIP_ANY = 1
 	SKIP_LEADING = 2
 	SKIP_TRAILING = 4
@@ -105,16 +106,17 @@ class TGraphFromHistograms(analysisbase.AnalysisBase):
 		if plot_dict.get('tgraph_strip_empty'):
 			if plot_dict['tgraph_strip_empty'] == True:
 				plot_dict['tgraph_strip_empty'] = HistogramGroupIterator.SKIP_BORDERING
-			elif plot_dict['tgraph_strip_empty'].lower() == 'any':
-				plot_dict['tgraph_strip_empty'] = HistogramGroupIterator.SKIP_ANY
-			elif plot_dict['tgraph_strip_empty'].lower() == 'left':
-				plot_dict['tgraph_strip_empty'] = HistogramGroupIterator.SKIP_LEADING
-			elif plot_dict['tgraph_strip_empty'].lower() == 'right':
-				plot_dict['tgraph_strip_empty'] = HistogramGroupIterator.SKIP_TRAILING
-			else:
-				raise ValueError("Unrecognized option for 'tgraph_strip_empty': %s" % plotData['tgraph_strip_empty'])
+			elif isinstance(plot_dict['tgraph_strip_empty'], basestring):
+				if plot_dict['tgraph_strip_empty'].lower() == 'any':
+					plot_dict['tgraph_strip_empty'] = HistogramGroupIterator.SKIP_ANY
+				elif plot_dict['tgraph_strip_empty'].lower() == 'left':
+					plot_dict['tgraph_strip_empty'] = HistogramGroupIterator.SKIP_LEADING
+				elif plot_dict['tgraph_strip_empty'].lower() == 'right':
+					plot_dict['tgraph_strip_empty'] = HistogramGroupIterator.SKIP_TRAILING
+				else:
+					raise ValueError("Unrecognized option for 'tgraph_strip_empty': %s" % plotData['tgraph_strip_empty'])
 		else:
-			plot_dict['tgraph_strip_empty'] = 0
+			plot_dict['tgraph_strip_empty'] = HistogramGroupIterator.SKIP_NONE
 		self.prepare_list_args(plotData, ["tgraph_x_nicks", "tgraph_y_nicks", "tgraph_result_nicks"])
[…]

### 2015-12-04 Core/doc/latex/paper.tex

@@
 This processing step includes further event selections, event categorization or high-level calculations based on the reconstructed physics objects.
-The events are usually processed with different configurations, depending on the specific analysis needs.
+The data are usually processed with different configurations, depending on the specific analysis needs.
 The output is then used for post-processing steps, including the graphical representation of the results and their statistical interpretation.
@@
 This is possible because the processed events are known to be independent of each other.
-The framework comes with a built-in possibility to submit analysis jobs with the job submission tool grid-control.
+The framework comes with a built-in possibility to submit analysis jobs with the job submission tool \software{grid-control}.
 

### 2015-12-04 KappaAnalysis/interface/Filters/nPUFilter.h
Add forgotten change in KappaTools include

@@ -2,7 +2,7 @@
 #pragma once
 
 #include "Kappa/DataFormats/interface/Kappa.h"
-#include "KappaTools/RootTools/RunLumiReader.h"
+#include "KappaTools/RootTools/interface/RunLumiReader.h"
 
 #include "Artus/Core/interface/FilterBase.h"
 #include "Artus/KappaAnalysis/interface/KappaTypes.h"
@@ -31,6 +31,5 @@ public:
 
 
 private:
-	
 	//bool MatchWhiteBlackLists(uint64_t item, std::vector<uint64_t> const& whitelist, std::vector<uint64_t> const& blacklist) const;
 };
